### 2018-03-01 idetc2018.tex
Initial Commit

%%% use twocolumn and 10pt options with the asme2e format
\documentclass[twocolumn,10pt]{asme2ej}
\newcommand{\gbf}[1] {\mbox{\boldmath${#1}$\unboldmath}}
\newcommand{\R}{\hbox{I \kern -.5em R}}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{color}
\usepackage{wrapfig}
\usepackage[hidelinks]{hyperref}
\usepackage{subfigure}
\usepackage{amsmath}
\usepackage{url}
\urlstyle{same}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{caption}
\usepackage[font=small]{caption}
\usepackage{algorithmicx}

\hypersetup{
  colorlinks   = true, %Colours links instead of ugly boxes
  urlcolor     = blue, %Colour for external hyperlinks
  linkcolor    = blue, %Colour of internal links
  citecolor   = blue %Colour of citations
}

\newcommand{\nothing}{}
\newcommand{\req}[1]{(\ref{#1})}
\newcommand{\pos}[1]{\stackrel{+}{#1} \! }
\newcommand{\half}[1]{\frac{#1}{2}}
\newcommand{\nhalf}[1]{(\frac{#1}{2})}
\newcommand{\singleline}{\baselineskip 0pt}
\newcommand{\expo}[1]{exp$({\bf {#1}})$}

% for displaying argmin command
\DeclareMathOperator*{\argminA}{arg\,min}

\def \Pluckerian{Pl\"uckerian }
\def \Plucker{Pl\"ucker }
\def \plucker{Pl\"ucker}
\def \Bezier{B\'{e}zier }
\def \BEZIER{B\'{E}ZIER }
\def \Shrocker{Schr\ddot{o}cker}

%\title{Linkage Synthesis for defect free path and motion generation.}
\title{Data Driven Defect Free Synthesis of Planar Mechanisms for Path and Motion Generation}
%%% first author
\author{Shrinath Deshpande, Anurag Purwar\footnote{Corresponding Author}\\
    \affiliation{
    Computer-Aided Design and Innovation Lab \\
    Department of Mechanical Engineering\\
    Stony Brook University\\
    Stony Brook, New York, 11794-2300
    }
   }

\begin{document}
\maketitle

\begin{abstract}
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Classic mechanism synthesis problem deals with computing type and dimensions of linkage system for performing specific tasks, which are categorized as path, motion and function generation.
This problem has been dealt with many approaches with the aim of finding acceptable solutions for practical situations.
In spite of increasing applications of electronically controlled manipulators, single degree freedom mechanical linkages will still important.
This is justified by new areas of application opened by technologies like nanotechnology, bio-mechatronics.
Therefore mechanisms theory will retain its position in the research community.

The motion and path generation problems are exhaustively researched topics.
Several text books, such McCarthy and Soh \cite{sohmccarthy}, Sandor and Erdman~\cite{Sandor}, Hunt \cite{Hunt78}, Hartenberg and Denavit \cite{Hartenberg},  Suh and Radcliffe \cite{Suh78}, and Lohse \cite{lohse2013} cover the science and art of planar four-bar and higher-order linkages.
The majority of these theories dont account for circuit and branch defect in synthesized mechanisms, which can render these mechanisms useless for practical applications.
The defects in mechanisms are thoroghly discussed in Chase and Mirth\cite{chase}.
Few of the approaches have taken branching defect into account. Their literature goes here ->->

Original contribution of this paper is in 1) a data driven framework that solves this problem using database look up, followed fine tuning via local optimization,
2) objective function and a \emph{signature} of coupler curves invariant under similarity transformation.
The invariant signature of coupler curves reduces solution space by a major fraction, which is further subjected to dimensionality reduction using Auto-encoder Neural Networks.
Clustering is performed on compresed latent representation of encoder to create the database hierarchy.
When a inputs a motion or a path, a query representing invariant signature of the input is raised for k nearest neighbors among cluster centers in the database.
The neighbor is defined as trajectory whose part or whole has a similar signature to input. These k neighbors are then subjected to find fine tuning to obtain set of solutions.

\section{Invariant Representation of Coupler Motion}
A coupler motion is a continuous trajectory in SE2 space, for path generation problem we ignore the orientation aspect of it.
In order to farmulate signature of the coupler motion which is invariant under similarity transform, we detach orientation information from path at the first step.
This is done because orientation does not suffers from the similarity operations.
We use formulations developed by Cui et.al\cite{cui2009} for open 2D curve matching, and build the signature of planar rigid body motion.

\subsection{Cubic B-Spline Fitting}
The discrete version coupler path is fitted with cubic b-splines with a approximate curvature parameterization such that more points will be sampled at the locations where curvature changes are higher. BSpline knot vector parameterization is given by,
\begin{equation}\label{u_1}
  u_i = u_{(i-1)} + \sqrt{{(x-\bar{x})}^2 + {(y-\bar{y})}^2}
\end{equation}
 where $(\bar{x}$, $\bar{y})$ is center of the bounding box sample points. We further normalize knot-vector $u$ to keep it between 0 and 1.

Figure~\ref{bsplineFitting} presents a comparison of B-spline fittings to path given with different timing information. It can be seen that B-spline samples more points where radius of curvature is small.

\begin{figure}
\centering
\includegraphics[width=240pt]{figure/fig_bspline.eps}
\caption{Cubic B-spline with curvature parameterization on the same curve with two different sampling rates.}
\label{bsplineFitting}
\end{figure}

\subsection{Curvature and Integral of Curvature Computation}
The curvature ($k$) at arc length $s$ and its unsigned integral upto $s$ are respectively given by,
\begin{eqnarray}
  k(s) = {\ddot{\textbf{x}}}(s), \\
  K(s) = \int^{s}_0 |k(s)|, \\
\end{eqnarray}

where ${\textbf{x}}: (x(s), y(s)$.

Figure~\ref{curvatureK} shows computed curvatures and its unsinged integral of coupler trajectory shown in Fig.~\ref{bsplineFitting}.

\begin{figure}
\centering
\includegraphics[width=240pt]{figure/fig_curvatureK.eps}
  \caption{arc length parameterized Curvature and Integral of curvature for the path shown in Fig.~\ref{bsplineFitting} with timing 1.}
\label{curvatureK}
\end{figure}

\subsection{Signature}
Now we re-sample the curvature at equal intervals of $K(s)$.
This is done by fitting a BSpline curve through curvature plot, with choosing know vector $u_{2}$ as given by,
\begin{equation}\label{u_2}
  u_i = u_{(i-1)} + {(K_i-K_{(i-1)})}
\end{equation}

Now plotting re-sampled $k$ vs $K$ gives us the signature of the coupler path. This signature is invariant under similarity transformation; for proof see\cite{cui2009}.
Figure~\ref{signature} shows the path from Fig.~\ref{bsplineFitting} with two different timings and their corresponding signatures.
It can be seen that timing has a negligible effect on signatures.
The minor distortions is due to small difference in the shape of fitted B-Spline.

\begin{figure}
\centering
\includegraphics[width=240pt]{figure/fig_signatures.eps}
  \caption{Signatures of the path with two different timings from Fig.\ref{bsplineFitting}. It can be seen that signatures have minimal sensitivity towards change in timing of the input.}
\label{signature}
\end{figure}

\subsection{Partial Matching of Coupler Curves}\label{sec_ncc}
The signatures can be used for partial matching using normalized cross-correlation\cite{cui2009}.
Normalized cross-correlation function $(C_n)$ is a convolution operation between two signals (or curve signatures) $F(i)$ and $t(i)$ given by,

\begin{equation}
  Cn(j) = \sum_{i}^{t_{span}} \frac{(F(i+j) - \bar{F}_{t_{span}})(t(i) - \bar{t})}{\sqrt{\sum_{i}^{t_{span}}{(F(i+j) - \bar{F}_{t_{span}})}^2\sum_{i}^{t_{span}}{(t(i) - \bar{t})}^2}}
\end{equation}

Where $Cn(j)$ is the normalized cross-correlation value when template $t(i)$ is matched to $F$ at $j^{th}$ index. Here $t(i)$ acts as template that tries to find best match against $F(i)$ while sliding over it along j.
Domain of $Cn(j)$ is [-1, 1], where 1 represents the complete match.
Maximum score of the matching represents similarity of the template in F, and location at which maximum occurs is the start point.
Figure~\ref{ncc} depicts normalized cross correlation function over the sliding domain $j$ for two curves shown in Fig.~\ref{wholePart} where the second curve is a part of first curve modified by scaling and translation.

\begin{figure}
\centering
\includegraphics[width=240pt]{figure/fig_whole_part.eps}
  \caption{Part path is formed by trimming whole path followed by translation and scaling.}
\label{wholePart}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=240pt]{figure/fig_ncc.eps}
  \caption{Normalized cross correlation of the signatures is shown. It can be seen that exact match is found at $j=0$.}
\label{ncc}
\end{figure}

\subsection{Signature of coupler motion}\label{sec_sign}
Now that we have a invariant representation of path, we can formulate signature of coupler motion.
First we subtract initial angle from rest of the curve.
Next step is to fit a B-spline through coupler angles using the same knot vectors given in~\req{u_1}, followed by r-esampling at parameters given by~\req{u_2}.
The obtained orientation data plotted against $K$ results into motion signature of the trajectory as shown in fig.~\ref{motionSignature}

\begin{figure}
\centering
\includegraphics[width=240pt]{figure/fig_motion_signatures.eps}
  \caption{Motion Signatures of the trajectories shown in Fig.\ref{wholePart}. The same correlation function can be used to compute whole-to-part matching.}
\label{motionSignature}
\end{figure}

\subsection{Objective Function for Synthesis}
The Normalized Cross-Correlation function presented in the section~\ref{sec_ncc} can be used the criterion for motion (or path) synthesis of any planar linkage, where the objective is to find a linkage, that produces a motion whose part or whole corresponds to target motion (or path).
Thus we can formulate the optimization problem given by,

\begin{equation}\label{objectiveFun}
  \argminA_{\textbf{\emph{l}}} f_{obj}(\textbf{\emph{l}}) = 1 - \max\limits_{j}(Cn(j))
\end{equation}
where $\textbf{\emph{l}}$ is the vector of linkage parameters for perticular planar linkage.
In case of four-bar, $\textbf{\emph{l}}: l_1, l_2, l_3, l_4, l_5$, with $l_i$ is link ratio of $i^{th}$ link shown in Fig~\ref{fourbar}.

\begin{figure}
\centering
\includegraphics[width=240pt]{figure/fig_fourbar.eps}
  \caption{Parametric representation of four-bar linkage with all revolute joints.}
\label{fourbar}
\end{figure}

Objective function evaluation step consists of calculation of coupler motion and finding its best normalized cross-correlation score.
It is important to note that representation obtained in Section~\ref{sec_sign} reduces size of the linkage parameters in optimization.
This optimization problem can be solved using search methods which do not require gradient computation as algebraic representation of objective function in terms of linkage parameters is not possible.
We can employ global optimization methods such as differential evolution, simulated annealing at the start and local optimization methods link powell's method towards the end for faster convergence\cite{ullah1997}.
Section~\ref{examples} presents results for various optimization techniques used.

Considering highly non-linear nature of the problem, finding a good initial guess proves to be game changing.
Thus we exploit the advantages of data driven approach for finding many good initial guesses or if get lucky, the solution itself.

\section{Sensitivity Analysis of Signatures}
Owing to the complex relationship between parameter space and generated motion, small change in linkage parameters can produce large and discontinuous structural change in the generated motions.
For example small change in crank length can open a previously close loop.
Most of the analytical methods like Fourier analysis can not capture the continuity at such singular locations, which adversely affect the optimization process.
In contrast to this behavior, Signatures derived in Sec.~\ref{sec_sign} has smooth transition at these singular locations.
To make our point, we perform Sensitivity Analysis as follows:
A four-bar with link ratios ($l_1:0.3$, $l_2:1$, $l_3:1.5$, $l_4:1$, $l_5:1$) is subjected to gradual change in parameter $l_1$ in the range (0.3, 0.8) in steps of 0.1.
Figure~\ref{saCouplerCurves} shows coupler motion of the fourbars associated with change in $l_1$.
Although the close circuit breaks to form open curves, It is evident how smooth the shape changes in the process.
This smoothness is captured in the Heat Map shown in Fig.~\ref{saHeatmap} obtained by similarity evaluations via Normalized Cross-Correlation of corresponding signatures.
If we construct the graph (see Fig.~\ref{saGraph}) based on the adjacency matrix and igore the edges when distance is more than 0.2, we get a \emph{small world network}\cite{watts1998}.

\begin{figure}
\centering
\includegraphics[width=240pt]{figure/fig_sa_coupler_curves.eps}
  \caption{Hi}
\label{saCouplerCurves}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=240pt]{figure/fig_sa_heatmap.eps}
  \caption{Hi}
\label{saHeatmap}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=240pt]{figure/fig_sa_graph.eps}
  \caption{Hi}
\label{saGraph}
\end{figure}

\section{Clustered Database of Planar Linkages}
Having a invariant representation greatly reduces data required to sample all possible types shapes of coupler motion.
We have built a database of planar four-bar linkages with revolute joints as an example, but the approach is same for any planar motion generating machine.
We generate this database while taking following aspects into consideration.
\begin{enumerate}
  \item Sampling should maximize its distribution over possible four-bar coupler motions.
  \item Data generation can be parallelized.
  \item Approach scalable with linkages with more number of links.
\end{enumerate}
Figure~\ref{fourbar} represents parametric representation of four-bar linkage with parameters ($l_1,l_2,l_3,l_4,l_5$).
As mapping between four-bar linkage parameter space and coupler motion space is highly non-linear, uniform distribution over linkage parameter space doesn't necessarily mean uniform sampling over motion space.
Thus the efficient approach would be to sample more in the locations where sensitivity is maximum.
Our observational intuition tells that whenever the link ratios of four-bar linkage are close to 1, the sensitivity of the shape of a coupler motion is higher than otherwise.
Thus we chose Log-Normal Distribution ($\mu = 0,\sigma = 0.6 $) for the range of link ratios : $(l_1, l_2, l_3)$ as shown in Fig.~\ref{logNormal}, and Normal Distribution ($\mu = 0,\sigma = 2 $) for $(l_4, l_5)$.

\begin{figure}
\centering
\includegraphics[width=240pt]{figure/fig_logNormal.eps}
  \caption{Probability Distribution function used in random sampling for parameters $l_1$, $l_2$ and $l_3$.}
\label{logNormal}
\end{figure}

\subsection{Dimensionality Reduction using Auto-Encoders}
Each data point in database consists of discrite signature of motion, which is kept to be 100 float digits. In order to have efficient query operations we perform clustering, a method that summarizes and creates a hierarchy in the database.
Clustering in higher dimensions suffers from \emph{Curse of Dimensionality}, thus we first perform dimensionality reduction using Auto-encoder Neural Networks.
Auto-encoder is a powerful mapping model, which learns to encode the input data in very compact representation and can reconstruct the input with minimal error; performing much better than PCA\cite{hinton2006}.
This Non-linear mapping by auto-encoder can greatly improve the representation of data for clustering\cite{song2013}.
Figure~\ref{autoEncoder} shows an architecture similar to the Neural Network we designed for the task.
Number of neurons per layer are (100, 80, 50, 10, 50, 80, 100).
Each hidden layer is activate by Rectified Linear Unit (\emph{ReLU}) activation function.
In $i^{th}$ hidden layer, output of the previous layer $h_(i-1)$ is fed as input to produce output $h_i$ given by,

\begin{eqnarray}\label{nnlayer}
  h_i = ReLU(W_{i}h_{i-1} + b_{i}), \\
  ReLU(x) = max(0, x).
\end{eqnarray}

Where $W_i$ and $b_i$ are weights and bais of $i^{th}$ layer, which are computed in the process of training.
Auto-encoders are trained to reconstruct the input, in this way each layer encodes the input, which is sufficient for the next layers to reconstruct the output.
Objective of the training is to find out set of weights and biases that minimizes the error loss given by,

\begin{equation}\label{nnloss}
  E = \sum_{i=0}^{N} || X_i - \grave{X}_i ||^2
\end{equation}
where $X_i$ is input, $\grave{X}_i$ is reconstructed output and N is number of training examples.

Once a network is trained, Output of the bottle-neck layer $(h_{ib})$ represents the compressed feature space ($Z$).
It can be seen that input information is compressed by a factor of 10, while achieving $95\%$ reconstruction accuracy.
Standard clustering algorithms are performed on this latent space for better clustering\cite{song2013}.
We use Agglomeretive Clustering, a method of Hierarchical clustering, which is an approach to partitioning clustering for identifying groups in the dataset.
It does not require to pre-specify the number of clusters to be generated.
\emph{Ward}\cite{ward1963} Linkage criterion is used for clustering, which minimizes the variance of the clusters being merged.
The distance metric used is the euclidean distance in the latent space.
Although the more accurate distance metric is normalized cross correlation score, it is very expensive to calculate it for entire database.
Signatures with $\mathcal{O}(m)$ points, take $\mathcal{O}(m\log{}m)$ time for each comparisons and there are $\mathcal{O}(N^2)$ number of comparisons to be made for database of $N$ points.
Thus we pick one sample from each cluster and perform Agglomeretive Clustering on this set with normalized cross correlation as the distance metric to form a top cluster.
When user raises one such query, we first find k nearest neighbors in the top cluster, then descend into their neighbors.
Motion with highest similarity score is returned along with its corresponding linkage parameters which are further fine-tuned to match query using optimization.

\begin{figure}
\centering
\includegraphics[width=240pt]{figure/fig_auto_encoder.eps}
  \caption{A general architecture of Auto-Encoder. Actual implementation has five hidden layers where middle layer is the bottleneck.}
\label{autoEncoder}
\end{figure}

\section{Algorithm}
\begin{algorithm}[thb]
\caption{Algorithm for Optimal Four-bar Linkage Synthesis}\label{algorithm1}
\begin{algorithmic}[1]
\Procedure{Lagrange Multiplier Method}{}\\
linear constraints$ (n) \leq 5$
\For {each linear constraint}
\State{add constraint eq. to [A]}
\EndFor\label{}
\State{perform SVD and pick $n-8$ Singular Vectors}
\State $f = 0$
 \State{error function for each of the relaxed constraint $\rightarrow$ $f_i$}
 \For {each $f_i$}
\State{$f = f + {f_i}^2$}
\EndFor\label{}
\State{form $h_1$ and $h_2$ using Eq.~\ref{h1h2}}
\If{nonlinear constraints exist}
\State{number of non linear constraints =  $m$}
\For {each $m$}
\State{form $h_{(2+m)}$ using Eq.~\ref{nonlinEq} }
\EndFor\label{}
\EndIf\label{}
\State {{\bf Minimize} $f$ subjected to $h_1 = 0$,..,$h_{(2+m)} = 0$, $g \leq 0$ }
\State {Minimize $F$ by Lagrange Multipliers}
\State {$F = -f - \lambda_1h_1 -...-\lambda_{(m+2)}h_{(m+2)} - \mu g$}
\State {Take partial derivatives of $F$ w.r.t. $\alpha_2$,..,$\alpha_{(8-n)}$,$\lambda_1$,..,$\lambda_{(2+m)}$ to form a system of Equations along with Eq.\req{kkt1}},
\State {{\bf Solve} $(9 - n  + m) $ equations}
\State {{\bf Compute} dyad parameters}
\EndProcedure
\end{algorithmic}
\end{algorithm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Examples}\label{examples}

\begin{table}
\caption{Example~\ref{5pos}: Pose Data}
\centering
\label{5posMotion}
\begin{tabular}{cccc}
\hline
Poses & X & Y & $\phi$ (degree)\\
\hline
Pose 1 &  -5.74803 & -0.00787402 & 88.5679 \\
Pose 2 &  -4.12598 & 0.795276 & 2.16642 \\
Pose 3 &  -2.72441 & 1.67717 & 356.968 \\
Pose 4 &   -1.54331 & 0.433071 & 1.03102 \\
Pose 5 &   1.22835 & -0.590551 & 345.624 \\
\hline
\end{tabular}
\end{table}

\begin{table*}[thb]
  \caption{Example \ref{5pos}: Four singular vectors obtained after SVD of the matrix $[A]$ of size $4\times8$.}
  \centering
  \begin{tabular}{ccccccccc}
  \hline
  Dyad Vector &$p_1$&$p_2$&$p_3$&$p_4$&$p_5$&$p_6$&$p_7$&$p_8$\\
    \hline
   $\textbf{p}_1$& -0.01874 & -0.2516 & 0.5174 & -0.3985 & 0.02237 & 0.03616 & 0.4980 & 0.5097\\
$\textbf{p}_2$&0.007703 & 0.4284 & -0.3233 & 0.5047 & -0.02227 & -0.06264 & 0.4823 & 0.4688\\
$\textbf{p}_3$& 0.02871 & 0.08073 & 0.1114 & 0.1484 & -0.0120 & 0.9778 & -0.03979 & 0.01384\\
$\textbf{p}_4$& 0.07561 & -0.1628 & 0.02429 & 0.1901 & 0.9647 & -0.009039 & -0.007750 & 0.01223\\
    \hline
  \end{tabular}
  \label{svectors5pos}
\end{table*}

\begin{table*}[thb]
  \caption{Example \ref{5pos}: Two optimum dyad-vectors obtained as result of optimization}
  \centering
  \begin{tabular}{ccccccccc}
  \hline
  Vector &$p_1$&$p_2$&$p_3$&$p_4$&$p_5$&$p_6$&$p_7$&$p_8$\\
   \hline
$\textbf{s}_1$&0.4175 & 1.025 & 5.818 & 1.388 & 0.8691 & 17.21 & 7.760 & 8.773 \\
$\textbf{s}_2$&0.08080 & 0.007451 & 0.07404 & 0.3656 & 0.9573 & 0.2468 & 0.4554 & 0.4875\\
   \hline
  \end{tabular}
  \label{dyadvectors5pos}
\end{table*}

\begin{figure}
\centering
\includegraphics[width=200pt]{figure/fig1.eps}
\caption{Example \ref{5pos}: Optimal four-bar mechanism that minimizes algebraic fitting error for third pose. Although second pose lies on different circuit, this Grashof type four-bar produces desired continuous motion from first to last pose.}
\label{5posgg}
\end{figure}

\subsection{Optimal Linkage for Four Precision Poses with Region Constraint}\label{4pos1line1pose}
\begin{figure}
\centering
\includegraphics[width=230pt]{figure/fig2.eps}
\caption{Example \ref{4pos1line1pose}: Five landing gear positions are shown where the third position can be relaxed. Allowed region for fixed pivots of mechanism is also shown.}
\label{4posproblem}
\end{figure}

\begin{table}
\caption{Example~\ref{4pos1line1pose}: Pose Data}
\centering
\label{4posMotion}
\begin{tabular}{cccc}
\hline
Poses & X & Y & $\phi$ (degree)\\
\hline
Pose 1 &  -0.0125 & -0.0374 & 66.3 \\
Pose 2 &  0.303 & 0.634 & 35.5 \\
Pose 3 &  0.599 & 1.83 & 352. \\
Pose 4 &  0.268 & 2.30 & 331. \\
Pose 5 &  0.606 & 1.31 & 22.2 \\
\hline
\end{tabular}
\end{table}

\begin{table*}[thb]
  \caption{Example \ref{4pos1line1pose}: Four singular vectors obtained after SVD of the matrix $[A]$ of size $4\times8$. The vectors form basis for the null space}
  \centering
  \begin{tabular}{ccccccccc}
  \hline
  Vector &$p_1$&$p_2$&$p_3$&$p_4$&$p_5$&$p_6$&$p_7$&$p_8$\\
    \hline
   $\textbf{p}_1$& -0.585 & -0.0211 & -0.506 & 0.165 & 0.134 & -0.350 & 0.368 & 0.313 \\
   $\textbf{p}_2$& 0.0640 & -0.330 & 0.190 & -0.804 & 0.236 & -0.264 & 0.194 & 0.204 \\
   $\textbf{p}_3$& -0.280 & 0.0484 & -0.466 & -0.398 & 0.232 & 0.603 & -0.136 & -0.329 \\
   $\textbf{p}_4$& -0.137 & 0.145 & 0.469 & 0.250 & 0.747 & 0.229 & 0.259 & 0.0111 \\
    \hline
  \end{tabular}
  \label{svectors4pos}
\end{table*}

\begin{table*}[thb]
 \caption{Example \ref{4pos1line1pose}: Four optimum dyad-vectors obtained as result of optimization}
  \centering
  \begin{tabular}{ccccccccc}
  \hline
  Vector &$p_1$&$p_2$&$p_3$&$p_4$&$p_5$&$p_6$&$p_7$&$p_8$\\
    \hline
$\textbf{s}_1$&  0.0254 & 0.192 & -0.202 & -0.0965 & 0.00562 & 0.723 & -0.387 & -0.490 \\
$\textbf{s}_2$& 0.276 & -0.406 & 0.211 & -0.425 & -0.161 & -0.561 & 0.251 & 0.360 \\
$\textbf{s}_3$& 0.315 & -0.356 & 0.189 & -0.397 & -0.318 & -0.598 & 0.129 & 0.324 \\
$\textbf{s}_4$& 0.208 & -0.302 & 0.141 & -0.335 & -0.321 & -0.691 & 0.134 & 0.368 \\
    \hline
  \end{tabular}
  \label{dyadvectors4pos}
\end{table*}

Figure~\ref{4posproblem} shows five positions of a landing gear moving from the landing position to the retracted position. Table~\ref{4posMotion} contains position and orientation data for five poses. It is desirable that fixed pivots should lie inside the circle of radius 2.3 with center located at (3.33, 2.04). The task is to synthesize a mechanism which interpolates through precision poses (1,2,4,5) and minimizes the algebraic error for the third pose while keeping fixed pivot locations inside the allowed region as shown in the figure.

First step is to extract all four geometric constraints, i.e. four precision poses and form matrix $[A]$  using Eq.~\req{A8}. Here $n = 4$ which means solution space consists of 4 singular vectors which are obtained using SVD and tabulated in Table~\ref{svectors4pos}. Once this linear algebraic fitting is done, optimization problem can be formulated.

The error function is linear error function $f_1$ for third pose, which is evaluated using Eq.~\req{poseError}. Substituting singular vectors into dyad coefficients followed by substituting them in terms of $\alpha_i$ using Eq.~\req{solutionSpace}, we get final objective function given by
\begin{equation}
f = f_1^2,
\end{equation}
where $f_1 = -0.0598 {\alpha_2}+0.0294 {\alpha_3}-0.100 {\alpha_4}+0.0876$.
The circular region for fixed pivots is modeled as an inequality constraint using Eq.~\req{ellipseIneq} and~\req{g} given by,
\begin{equation}
\begin{array}{c}
g = 0.091 {\alpha_2}^2+(0.25 {\alpha_3}+0.11 {\alpha_4}+0.25) {\alpha_2}\\+0.35 {\alpha_3}^2+0.049 {\alpha_4}^2+{\alpha_3} (0.043 {\alpha_4}+1.0)\\-0.048 {\alpha_4}-0.19 \leq 0
\end{array}
\end{equation}
Objective function also has two quadratic equality constraints given by,
\begin{eqnarray}
& & h_1 = 0.058 {\alpha_2}^2+(-0.25 {\alpha_3}+0.17 {\alpha_4}-0.36) {\alpha_2} -0.34 {\alpha_3}^2  \nonumber \\
& & \ \ \ \ \ \ \ \ \  -0.041 {\alpha_4}^2+{\alpha_3} (0.23 {\alpha_4}-0.38)-0.033 {\alpha_4}+0.29, \nonumber \\
& & h_2  = -0.29 {\alpha_2}^2+{\alpha_2} (-0.15 {\alpha_3}-0.074 {\alpha_4}-0.048)+0.20 {\alpha_3}^2 \nonumber \\
& & \ \ \ \ \ \ \ \ \  +{\alpha_3} (0.18 {\alpha_4}+0.12)-0.46 {\alpha_4}^2-0.11 {\alpha_4}-0.36 \nonumber \\
\end{eqnarray}
We follow steps presented in section~\ref{lagrangeMultiplier} and form Lagrange objective function $F$ given by,
\begin{equation}
F = -{f_1}^2- \lambda_1h_1 -  \lambda_2h_2 - \mu g
\end{equation}
and obtain equations by partial differentiation as well as equation corresponding to Karush-Kuhn-Tucker condition as follow:

\begin{equation}
\begin{array}{c}
\frac{\partial}{\partial \alpha_2}(F) = 0 = (-0.12 {\alpha_2}+0.25 {\alpha_3}-0.17 {\alpha_4}+0.36) {\lambda_1}+(0.57 {\alpha_2}\\+0.15 {\alpha_3}+0.074 {\alpha_4}+0.048) {\lambda_2}-(0.18 {\alpha_2}) \mu \\-(0.25 {\alpha_3}) \mu -(0.11 {\alpha_4}) \mu -0.25 \mu +0.060
\end{array}
\end{equation}

\begin{equation}
\begin{array}{c}
\frac{\partial}{\partial \alpha_3}(F) = 0 = {\lambda_1} (0.25 {\alpha_2}+0.69 {\alpha_3}-0.23 {\alpha_4}+0.38)+{\lambda_2}\\ (0.15 {\alpha_2}-0.41 {\alpha_3}-0.18 {\alpha_4}-0.12)-0.25 {\alpha_2} \mu\\ -0.71 {\alpha_3} \mu -0.043 {\alpha_4} \mu -1.0 \mu -0.029
\end{array}
\end{equation}

\begin{equation}
\begin{array}{c}
\frac{\partial}{\partial \alpha_4}(F) = 0 = {\lambda_1} (-0.17 {\alpha_2}-0.23 {\alpha_3}+0.081 {\alpha_4}+0.033)\\+{\lambda_2} (0.074 {\alpha_2}-0.18 {\alpha_3}+0.92 {\alpha_4}+0.11)-0.11 {\alpha_2} \mu\\ -0.043 {\alpha_3} \mu -0.097 {\alpha_4} \mu +0.048 \mu +0.10
\end{array}
\end{equation}

\begin{equation}
\begin{array}{c}
\frac{\partial}{\partial \lambda_1}(F) = 0 =-0.058 \alpha_2^2+(0.25 \alpha_3-0.17 \alpha_4+0.36) \alpha_2\\+0.34 \alpha_3^2+0.041 \alpha_4^2+\alpha_3 (0.38-0.23 \alpha_4)+0.033 \alpha_4-0.29
\end{array}
\end{equation}

\begin{equation}
\begin{array}{c}
\frac{\partial}{\partial \lambda_2}(F) = 0 =0.29 \alpha_2^2+(0.15 \alpha_3+0.074 \alpha_4+0.048) \alpha_2\\-0.20 \alpha_3^2+0.46 \alpha_4^2+\alpha_3 (-0.18 \alpha_4-0.12)+0.11 \alpha_4+0.36
\end{array}
\end{equation}

\begin{equation}
\begin{array}{c}
\mu\frac{\partial}{\partial \mu}(F) = 0 =\mu(-0.091 \alpha_2^2+(-0.25 \alpha_3-0.11 \alpha_4-0.25) \alpha_2\\-0.35 \alpha_3^2-0.049 \alpha_4^2+\alpha_3 (-0.043 \alpha_4-1.0)+0.048 \alpha_4+0.19)
\end{array}
\end{equation}

Solving these equations followed by filtering on the basis of feasibility using Eq.~\ref{kkt2} yields four unique and feasible solutions tabulated in Table~\ref{alphasol}. All of these solutions satisfy Karush-Kuhn-Tucker Condition for optimality given by Eq.~\req{kkt3}. Dyad vectors are calculated by substituting these solutions into \req{solutionSpace} and are given in Table ~\ref{dyadvectors4pos}. Any of these four dyad-vectors when substituted in Eq.~\req{general} forms a quartic equation, which when projected on hyperplane $Z_4 = 1$ represents a quadric surface. Fig.~\ref{4posmanifolds} shows intersection of hyperboloid and hyperbolic paraboloid  formed from first and second dyad-vectors. The intersection curve represents workspace of the corresponding four-bar linkage. Table~\ref{error4pos} contains the minimized algebraic fitting error of objective function. From this table, we can see that dyad $\textbf{s}_4$ has least pose fitting error. All dyads except $\textbf{s}_1$ are of RR type dyads while $\textbf{s}_1$ is an RP dyad. Figure~\ref{4posRRRP} shows a branch defect free four-bar mechanism formed by combining $\textbf{s}_1$ and $\textbf{s}_2$.

\begin{table}
\caption{Real Solutions for $\alpha_i$, $\lambda_i$ and $\mu$}
\centering
\label{alphasol}
\begin{tabular}{cccccccc}
\hline
Dyad &$\alpha_1$&$\alpha_2$ & $\alpha_3$& $\alpha_4$& $\lambda_1$& $\lambda_2$& $\mu$\\
\hline
$\textbf{s}_1$  & 1 & -0.40 & -0.027 & 1.09 & 0.0 & 0.0 & 0.0 \\
$\textbf{s}_2$ & 1 &  -2.04 & -1.81 & 2.06 & 0.0 & 0.0 & 0.0 \\
$\textbf{s}_3$ & 1 &-3.64 & -4.24 & 5.37 & 0.0 & 0.0 & 0.0 \\
$\textbf{s}_4$ & 1 & 5.08 & -2.58 & -2.94  & 0.0 & 0.0 & 0.0 \\
\hline
\end{tabular}
\end{table}

\begin{table}
\caption{Optimality Evaluations for Dyads}
\centering
\label{error4pos}
\begin{tabular}{ccc}
\hline
Dyad & $3^{rd}$Pose-Fitting Error & Inequality Constraint \\
\hline
$\textbf{s}_1$ &  0.0102 & -0.000650 \\
$\textbf{s}_2$ &  0.0415 & -0.00126 \\
$\textbf{s}_3$ &  0.0212 & -0.000424 \\
$\textbf{s}_4$ & -1.8$\times10^{-8}$ &  -0.396 \\
\hline
\end{tabular}
\end{table}

\begin{figure}
\centering
\includegraphics[width=230pt]{figure/fig3.eps}
\caption{Example \ref{4pos1line1pose}: First and second dyad in Table ~\ref{dyadvectors4pos} are combined to form the linkage shown. It can be clearly seen that coupler curve fairly approximates the third pose while fixed pivots are inside the allowed region.}
\label{4posRRRP}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=250pt]{figure/fig4.eps}
\caption{Example \ref{4pos1line1pose}: Image-Space representation of intersection of third and fourth optimal constraint manifolds from Table.~\ref{dyadvectors4pos}. Also shown are five image points as dark spheres representing the five poses; four of them lie exactly on the intersection of the two surfaces, while one is closest possible.}
\label{4posmanifolds}
\end{figure}

\section*{Conclusion}
In this paper, we presented a task-driven approach to unified and optimal synthesis of planar four-bar linkages for extended Burmester problem. In this formulation, various geometric constraints are treated equivalently, which in turn leads to a much simpler two-step based algorithm for computing planar dyads of four-bar linkages. Original contributions of this paper have been into reforming a mixed exact-approximate algebraic fitting problem into problem of task oriented optimal fitting of algebraic manifold. The framework presented here can accommodate linear as well as non-linear equality and inequality geometric constraints and minimize objective functions that can be expressed in terms of dyadic parameters. Although adding non-linear geometric constraints increase computational complexity, computer algebra software like Mathematica could be used to compute solutions of quadratic system of equations in a reasonable amount of time. Experimentations show that Mathematica takes less than 3 seconds on a MacBook Pro with 2.4GHz Intel core i5 processor and 8GB RAM for computing solutions for the system of seven quadratic equations. The framework also preserves previously achieved real-time solutions for linear geometric constraints with no optimality criterion. Two examples demonstrating computation of optimal type and dimensions of dyads that minimize task oriented objective function are presented.

\begin{acknowledgment}
This work has been financially supported by National Science Foundation under a research grant to Stony Brook University (A. Purwar and Q.J. Ge, grant CMMI-1563413). All findings and results presented in this paper are those of the authors and do not represent those of the funding agencies.
\end{acknowledgment}

\bibliographystyle{purwar}
\bibliography{References}
\newpage
\clearpage
\listoftables
\listoffigures

\end{document}

### 2018-03-01 intro.tex
Initial Commit

\section{Intoduction}
In this paper, we present 1) a unified approach for solving the extended Burmester problem by showing that all linear- and non-linear constraints can be handled in a unified way without resorting to special cases, 2) in the event of no or unsatisfactory solutions to the synthesis problem certain constraints can be relaxed, and 3) such constraints can be approximately satisfied by minimizing the algebraic fitting error using Lagrange Multiplier method. We present a new algorithm, which solves new problems including optimal approximate synthesis of Burmester problem with no exact solutions.

### 2018-03-07 idetc2018.tex
version 2.0

@@
 %%% use twocolumn and 10pt options with the asme2e format
-\documentclass[twocolumn,10pt]{asme2ej}
+\documentclass[twocolumn,10pt]{asme2e}
 \newcommand{\gbf}[1] {\mbox{\boldmath${#1}$\unboldmath}}
@@
 \usepackage{subfigure}
-\usepackage{amsmath}
 \usepackage{url}
 \urlstyle{same}
-\usepackage{algorithm}
-\usepackage[noend]{algpseudocode}
 \usepackage{caption}
@@
 \usepackage{algorithmicx}
+%\usepackage{algorithm}
+\usepackage{amsmath}
+\usepackage[linesnumbered,ruled]{algorithm2e}
 
@@
 
-%\title{Linkage Synthesis for defect free path and motion generation.}
-\title{Data Driven Defect Free Synthesis of Planar Mechanisms for Path and Motion Generation}
+%%% Replace here with information related to your conference
+\confshortname{IDETC/CIE 2017}
+\conffullname{the ASME 2017 International Design Engineering Technical Conferences \&\\
+              Computers and Information in Engineering Conference}
+
+%%%%% for date in a single month, use
+\confdate{26-29}
+\confmonth{August}
+%%%%% for date across two months, use
+\confyear{2017}
+\confcity{Quebec City}
+\confcountry{Canada}
+
+%%% Replace DETC2009/MESA-12345 with the number supplied to you
+%%% by ASME for your paper.
+\papernum{DRAFT: DETC2017-TBD}
+
+\title{Framework for Unified Optimal Synthesis of Planar Mechanisms for Motion and Path Generation using Shape Optimization}
 %%% first author
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{abstract}
+% Mechanisms design is generally the earliest phase in a machines design stages.
+
+Success in Synthesis of mechanisms for motion generation refers to computing linkage type and dimensions to perform the task without disassembly.
+However, majority of the methods formulate it as Precision Position problem (or Classical Burmester Problem) which inherently ignores the continuity information.
+Which, in turn results into solution linkages with branch and circuit defects.
+In this paper, we present a novel approach that addresses this issue into problem formulation and returns solutions free from defects.
+At the heart of this approach lies an objective function that compares the motion as a whole; thus, capturing designer's intent.
+In contrast to widely used structural error or loop closer equation based error functions which convolute the optimization by considering shape, size, position and orientation simultaneously, this objective function computes motion difference in the form that is invariant to similarity transformations.
+Actual scale, position and orientation of linkage components are obtained by subsequent trivial fitting.
+
+The approach starts with creating database of invariant motions of known linkages.
+The query is raised in the database for k nearest neighbors, which are either solutions or good initial conditions for fast local optimization techniques.
+We also employ global optimizing techniques without any initial guess.
+In spite of highly non-linear parameters space our approach discovers a wide pool of defect free solutions.
 \end{abstract}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}
-Classic mechanism synthesis problem deals with computing type and dimensions of linkage system for performing specific tasks, which are categorized as path, motion and function generation.
-This problem has been dealt with many approaches with the aim of finding acceptable solutions for practical situations.
 In spite of increasing applications of electronically controlled manipulators, single degree freedom mechanical linkages will still important.
@@
 Therefore mechanisms theory will retain its position in the research community.
+Classic mechanism synthesis problem deals with computing type and dimensions of linkage system for performing specific tasks, which are categorized as path, motion and function generation.
+This problem has been dealt with many approaches with the aim of finding acceptable solutions for practical situations.
 
@@
 Several text books, such McCarthy and Soh \cite{sohmccarthy}, Sandor and Erdman~\cite{Sandor}, Hunt \cite{Hunt78}, Hartenberg and Denavit \cite{Hartenberg},  Suh and Radcliffe \cite{Suh78}, and Lohse \cite{lohse2013} cover the science and art of planar four-bar and higher-order linkages.
-The majority of these theories dont account for circuit and branch defect in synthesized mechanisms, which can render these mechanisms useless for practical applications.
-The defects in mechanisms are thoroghly discussed in Chase and Mirth\cite{chase}.
-Few of the approaches have taken branching defect into account. Their literature goes here ->->
+The majority of these theories don't account for circuit and branch defect in the synthesis process, which can render the solution useless for practical applications.
+These defects in single DOF mechanisms are thoroughly discussed in Chase and Mirth\cite{chasemirth}.
 
-Original contribution of this paper is in 1) a data driven framework that solves this problem using database look up, followed fine tuning via local optimization,
-2) objective function and a \emph{signature} of coupler curves invariant under similarity transformation.
-The invariant signature of coupler curves reduces solution space by a major fraction, which is further subjected to dimensionality reduction using Auto-encoder Neural Networks.
-Clustering is performed on compresed latent representation of encoder to create the database hierarchy.
-When a inputs a motion or a path, a query representing invariant signature of the input is raised for k nearest neighbors among cluster centers in the database.
-The neighbor is defined as trajectory whose part or whole has a similar signature to input. These k neighbors are then subjected to find fine tuning to obtain set of solutions.
+Original contribution of this paper are in 1) a novel objective function for defect-free motion generation problem, 2) discovering a representation of coupler motion and path which is invariant under similarity transformations (henceforth termed as motion signature and path signature respectively.), 3) novel algorithm for partial matching of motions , 3) optimal storage by means of auto-encoder neural network and efficient neighbor search in the clustered database.
+The objective function that drives the synthesis process computes a distance measure of dissimilarity between the task motion and the coupler motion generated by current linkage parameters.
+In contrast to precision point method where distance measure is in terms of interpolation error, the distance measure of dissimilarity is valid between two planar curves or motions.
+Which inherently requires the continuity of output; ensuring the output mechanism defect free throughout the task.
 
-\section{Invariant Representation of Coupler Motion}
-A coupler motion is a continuous trajectory in SE2 space, for path generation problem we ignore the orientation aspect of it.
-In order to farmulate signature of the coupler motion which is invariant under similarity transform, we detach orientation information from path at the first step.
-This is done because orientation does not suffers from the similarity operations.
-We use formulations developed by Cui et.al\cite{cui2009} for open 2D curve matching, and build the signature of planar rigid body motion.
+Path synthesis methods based on Fourier analysis do take the continuity information of the coupler path into account, however majority of them are only defined on closed loop curves.
+Ullah and Kota\cite{ullah1997} have presented an invariant approach towards representation and synthesis of closed paths through shape optimization.
+They use combination of global and local search methods by optimizing Fourier Deviant function to compute the dimensions of planar fourbar linkage without any initial guesses.
+Wu et al.\cite{wu2011} presented a synthesis method for path generation based on finite Fourier series for synthesis of open and closed paths.
+In the case of motion generation, methods that take the branching defect into consideration limit their search into configuration space where Grashof condition holds true.
+To the authors' best knowledge, None of the method truly take motion continuity into account.
 
-\subsection{Cubic B-Spline Fitting}
-The discrete version coupler path is fitted with cubic b-splines with a approximate curvature parameterization such that more points will be sampled at the locations where curvature changes are higher.
-BSpline knot vector parameterization is given by,
-\begin{equation}\label{u_1}
-  u_i = u_{(i-1)} + \sqrt{{(x-\bar{x})}^2 + {(y-\bar{y})}^2}
-\end{equation}
- where $(\bar{x}$, $\bar{y})$ is center of the bounding box sample points. We further normalize knot-vector $u$ to keep it between 0 and 1.
+Owing to the highly nonlinear nature of the problem, most of the optimization based methods require good initial condition to start.
+Thus, an atlas or a design library is used to provide good initial conditions.
+McGarva\cite{mcgarva1994} have taken the earliest approach towards creating a library for coupler trajectories based on harmonic analysis.
+Wandling\cite{wandling2000} has presented an atlas based approach where, coupler paths and motions are stored in terms of Fourier Transforms.
+Input motion is searched for neighbors based on euclidean distances of Fourier Transforms.
+Yue et al.\cite{yue-pathgen2011} presented a similar approach of path generation using P-Type Fourier Descriptor applicable for open curves.
+In their approach, a task curve is transformed into normalized Fourier coefficients and queried for nearest neighbor search.
+The best match is returned as solution to input.
+Chu et al.\cite{chu2010} showcase an atlas based method of synthesizing spatial fourbar linkage for function generation problem where orientation data is stored in terms of Fourier harmonics.
 
-Figure~\ref{bsplineFitting} presents a comparison of B-spline fittings to path given with different timing information.
-It can be seen that B-spline samples more points where radius of curvature is small.
+The above methods generate data based on uniform sampling in the linkage parameter space.
+Given the highly nonlinear mapping between linkage parameters and coupler trajectory, this way of sampling leads to highly non-uniform sampling of trajectory space resulting in to data misrepresentation.
+We try to address this issue by employing log normal distribution in the linkage parameter space and clustering the generated data.
+The above methods have their library consists of all possible coupler curves, where one curve is broken down into many segments for creating data for partial curves.
+In contrast to this, we need store only one curve because our curve representation facilitates partial matching.
+Neither of the methods facilitate this partial matching of open motion curve into another open or closed curve.
+Thus reducing the data requirement even further.
+
+A Hierarchy is created in the database by means of clustering, where top level comprises of few data points called cluster centers which are representative of the cluster points in the lower levels.
+When a inputs a motion or a path, a query representing invariant signature \footnote{path or motion signature} of the input is raised for k nearest neighbors among cluster centers in the database.
+The neighbor is defined as motion or path whose part has a similar signature to the input.
+These k neighbors if needed, are subjected to fine tuning by local optimization to obtain set of solutions.
+Overall method is presented in algorithm~\ref{alg_overall}.
+
+Organization of the paper is as follows. Section~\ref{sec_sign} presents the computation of motion and path signatures.
+Section~\ref{sec_distanceMetric} is comprised of evaluation criterion for two signatures based on the shape similarity, which leads to form the error function for optimization.
+Section~\ref{sec_SA} discusses the nature of objective function via sensitivity analysis at a singular point.
+Section~\ref{sec_db_ae} explains the database generation and clustering using auto-encoders for efficient sampling and query operations.
+Finally, an case study is presented~\ref{sec_example} to showcase the efficacy of the method.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{algorithm}
+    \SetKwInOut{Input}{Input}
+    \SetKwInOut{Output}{Output}
+    \Input{Task Motion $\{x_i,y_i,\theta_i\}_{i=1}^{N}$ or Path$\{x_i,y_i\}_{i=1}^{N}$ }
+    \Output{Linkage Parameters \emph{\textbf{l}: $l_1$, $l_2$, ...}}
+    signature = calculateSignature(Input); \\
+    distances = [];\\
+    \For{centerPoint \textbf{in} clusterCenters}
+    {
+      distances.push(getDistance(signature, centerPoint))
+    }
+    kNeighbors = getNeighbors(distances, k)
+    \For{neighbor \textbf{in} kNeighbors}
+    {
+      \eIf{threshold $<$ neighbor.distance}
+      {
+        \textbf{return} $neighbor.LinkParameters$
+      }
+      {
+        \textbf{return} Optimize$(neighbor.LinkParameters)$
+      }
+    }
+    \caption{Planar Linkage Synthesis}
+    \label{alg_overall}
+\end{algorithm}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Signatures of Coupler Path and Motion}\label{sec_sign}
+The main focus of the paper is a novel method for motion generation that takes a continuous task motion as the input and returns defect free linkages producing similar motion.
+The objective function evaluation requires the input motion to be transformed into a specific form, which we call the signature of input motion.
+This signature representation is invariant to similarity operations which are reflection, rotation, translation and scaling.
+Signature for path and motion are termed as path signature and motion signature respectively.
+For calculating path signature we use formulations developed by Cui et.al\cite{cui2009}.
+For this task, our approach requires the input in terms of a parametric motion $(x:x(t), y:y(t), \theta:\theta(t))$.
+This section explains the procedure of signature calculation given in Algorithm ~\ref{alg_signature}.
+
+\begin{algorithm}
+    \SetKwInOut{Input}{Input}
+    \SetKwInOut{Output}{Output}
+    \Input{Twice Differentiable Parametric Representation of Motion $(x:x(t), y:y(t), \theta:\theta(t))$}
+    \Output{signature //discretized signal in form of an array}
+    k(t) = ComputeCurvature(x, y) using eq.~\ref{computeCurvature} \\
+    K(t) = IntergrateCumulatively(k) using eq.~\ref{kInt} \\
+    motionSignature = [] \\
+    pathSignature = [] \\
+    \For{$i = 0 \to max(K)$}
+    {
+      tmp = (value of t corresponding to which K has value i) \\
+      $i = i + 0.1$ \\
+      motionSignature.push(k(tmp)) \\
+      pathSignature.push(k(tmp))
+    }
+    \Return{PathSignature, MotionSignature}
+    \caption{Calculate Invariant Signatures}
+    \label{alg_signature}
+\end{algorithm}
+
+Curvature of the path of a parametric motion $(x:x(t), y:y(t), \theta:\theta(t))$ given by,
+\begin{eqnarray}
+  k(t) = \frac{\ddot{y}(t)\dot{x}(t) - \ddot{x}(t)\dot{y}(t)}{{(\dot{x}^2(t) + \dot{y}^2(t))}^{(\frac 32)}} \label{curvature}\\
+  K(t) = \int^{t}_0 |k(t)| \label{kInt},
+\end{eqnarray}
+where $\dot{x}$, $\ddot{x}(t)$ are first and second order derivative w.r.t. parameter t.
+For an example, parametric motion could be a B-spline motion as shown in fig~\ref{bsplineFitting}.
+We compute the curvature of path along the direction of t, using eq.~\ref{curvature} and the cumulative integral by eq.~\ref{kInt}.
+For implementation purposes, we use scipy\cite{scipy} module for computations of B-splines and their derivatives.
+Figure~\ref{curvatureK} shows computed curvatures and its unsigned integral of coupler path shown in Fig.~\ref{bsplineFitting}.
+It can be seen that curvature is very low at start, increases as the curve bends along the path and drops once again as the path straightens out.
+It is obvious that curvature plot will reverse if the direction of parameterization reverses.
 
@@
 \includegraphics[width=240pt]{figure/fig_bspline.eps}
-\caption{Cubic B-spline with curvature parameterization on the same curve with two different sampling rates.}
+  \caption{a) The path of the input motion along with direction of parameterization. b) Motion components $x(t), y(t), \theta(t)$ are plotted against parameter t.}
 \label{bsplineFitting}
 \end{figure}
-
-\subsection{Curvature and Integral of Curvature Computation}
-The curvature ($k$) at arc length $s$ and its unsigned integral upto $s$ are respectively given by,
-\begin{eqnarray}
-  k(s) = {\ddot{\textbf{x}}}(s), \\
-  K(s) = \int^{s}_0 |k(s)|, \\
-\end{eqnarray}
-
-where ${\textbf{x}}: (x(s), y(s)$.
-
-Figure~\ref{curvatureK} shows computed curvatures and its unsinged integral of coupler trajectory shown in Fig.~\ref{bsplineFitting}.
 
@@
 \includegraphics[width=240pt]{figure/fig_curvatureK.eps}
-  \caption{arc length parameterized Curvature and Integral of curvature for the path shown in Fig.~\ref{bsplineFitting} with timing 1.}
+  \caption{Curvature and its unsigned integral for the path shown in Fig.~\ref{bsplineFitting}}
 \label{curvatureK}
@@
 
-\subsection{Signature}
-Now we re-sample the curvature at equal intervals of $K(s)$.
-This is done by fitting a BSpline curve through curvature plot, with choosing know vector $u_{2}$ as given by,
-\begin{equation}\label{u_2}
-  u_i = u_{(i-1)} + {(K_i-K_{(i-1)})}
-\end{equation}
+Now we re-sample the curvature at equal intervals of $K(t)$, which is equivalent to plotting $k$ vs $K$ in Fig~\ref{signature}(a).
+This is done by finding the parameter values of t where $K$ changes in the steps of some step size. For practical purposes we find array of parameter t such that $K$ increments by 0.1.
+For each value of t in such array, we compute $k(t)$ and $\theta(t)$ and store it as the path and motion signatures respectively.
 
-Now plotting re-sampled $k$ vs $K$ gives us the signature of the coupler path. This signature is invariant under similarity transformation; for proof see\cite{cui2009}.
-Figure~\ref{signature} shows the path from Fig.~\ref{bsplineFitting} with two different timings and their corresponding signatures.
-It can be seen that timing has a negligible effect on signatures.
-The minor distortions is due to small difference in the shape of fitted B-Spline.
+These signatures are invariant under similarity transformations; for proof see\cite{cui2009}.
+Since we know that curvature changes inversely to the scale of the curve, when integrate along the scaled curve the scale factor cancels itself out.
+Reflection operation on the motion or the path, produces flipped path signature, but motion signature remains invariant.
+
+Figure~\ref{signature} shows path and motion signature obtained for the motion depicted in Fig.~\ref{bsplineFitting}
+It is important to note that signature depends on the direction along which we compute the curvature $k(t)$ as well as re-sample $\theta(t)$.
 
@@
 \includegraphics[width=240pt]{figure/fig_signatures.eps}
-  \caption{Signatures of the path with two different timings from Fig.\ref{bsplineFitting}. It can be seen that signatures have minimal sensitivity towards change in timing of the input.}
+  \caption{Path and motion signatures of the motion shown in Fig.~\ref{bsplineFitting}}
 \label{signature}
@@
 
-\subsection{Partial Matching of Coupler Curves}\label{sec_ncc}
-The signatures can be used for partial matching using normalized cross-correlation\cite{cui2009}.
-Normalized cross-correlation function $(C_n)$ is a convolution operation between two signals (or curve signatures) $F(i)$ and $t(i)$ given by,
+\section{Signature Matching and Error Function}\label{sec_distanceMetric}
+The signatures obtained in the previous steps contain important information about shape of the trajectory.
+In this section we formulate functions that evaluate the similarity (or distance) between two trajectories based on their signatures.
+These distance functions can be used as error metric which can be minimize using optimization methods.
 
-\begin{equation}
-  Cn(j) = \sum_{i}^{t_{span}} \frac{(F(i+j) - \bar{F}_{t_{span}})(t(i) - \bar{t})}{\sqrt{\sum_{i}^{t_{span}}{(F(i+j) - \bar{F}_{t_{span}})}^2\sum_{i}^{t_{span}}{(t(i) - \bar{t})}^2}}
+\subsection{Partial Matching of Path Signatures}\label{sec_ncc}
+When a path query is raised, it can be very useful to know whether this path already exists as a part in some other path present in the database.
+This subsection presents a method for determining this partial similarity.
+Let $p$ be motion signature of such a part path which acts as template while $W$ is the motion signature corresponding to a path (Whole) that can completely embed the template as shown in Fig.~\ref{wholePart}.
+The orientation information shown in Fig.~\ref{wholePart} is ignored for path matching.
+It will be used later for matching of motion signature.
+The way this partial matching works is as follows:
+
+\begin{enumerate}
+  \item As $p$ and $W$ are expressed in terms of arrays where each $i^{th}$ entry in the array corresponds to $K = 0.01\times i$, $W$ must contain more points than $p$.
+  \item The template $p$ is slid with offset index $j$ along with $W$.
+  \item For each offset $j$, we compute normalized cross-correlation function given by,
+\end{enumerate}
+\vspace{-0.6cm}
+\begin{equation}\label{nccEq}
+  Cn(j, p, W) = |\sum_{i}^{p_{span}} \frac{(W(i+j) - \bar{W}(j\to j + p_{span}))(p(i) - \bar{p})}{\sqrt{\sum_{i}^{p_{span}}{(W(i+j) - \bar{W}_{p_{span}})}^2\sum_{i}^{p_{span}}{(p(i) - \bar{p})}^2}} |,
 \end{equation}
+where $Cn(j, p, W)$ is the normalized cross-correlation value when template $p$ is matched to $W$ at $j^{th}$ index, $p_{span}$ is the length of the array $p$ and $\bar{W}(j\to j + p_{span})$ is the mean for the values of array $W$ between index range of ($j, j+p_{span}$)
 
-Where $Cn(j)$ is the normalized cross-correlation value when template $t(i)$ is matched to $F$ at $j^{th}$ index.
-Here $t(i)$ acts as template that tries to find best match against $F(i)$ while sliding over it along j.
-Domain of $Cn(j)$ is [-1, 1], where 1 represents the complete match.
-Maximum score of the matching represents similarity of the template in F, and location at which maximum occurs is the start point.
+Here $p$ acts as template that tries to find best match against $W$ while sliding over it along j.
+Domain of $Cn(j, p, W)$ is [0, 1], where 1 represents the complete embedment.
+
+Maximum score of the matching ($Cn_{max}(p, W)$) represents similarity of the template in $W$, and offset index $j$ at which maximum occurs is the start point for matching.
+As the signature reverses with reversal of the direction of sampling, we compute the correlation once in a normal way and again after reversing $p$ and select the best matching score, offset index and the matching direction of sampling.
 Figure~\ref{ncc} depicts normalized cross correlation function over the sliding domain $j$ for two curves shown in Fig.~\ref{wholePart} where the second curve is a part of first curve modified by scaling and translation.
@@
 \centering
+\includegraphics[width=240pt]{figure/fig_path_signatures.eps}
+  \caption{The domain of path signature is scale invariant but the range still has a scaling factor, which is taken by normalized cross-correlation.}
+\label{pathSignature}
+\end{figure}
+
+\begin{figure}
+\centering
 \includegraphics[width=240pt]{figure/fig_ncc.eps}
-  \caption{Normalized cross correlation of the signatures is shown. It can be seen that exact match is found at $j=0$.}
+  \caption{Normalized cross correlation of the signatures computed along each direction is shown. It can be seen that exact match is found at $j=0$.}
 \label{ncc}
@@
 
-\subsection{Signature of coupler motion}\label{sec_sign}
-Now that we have a invariant representation of path, we can formulate signature of coupler motion.
-First we subtract initial angle from rest of the curve.
-Next step is to fit a B-spline through coupler angles using the same knot vectors given in~\req{u_1}, followed by r-esampling at parameters given by~\req{u_2}.
-The obtained orientation data plotted against $K$ results into motion signature of the trajectory as shown in fig.~\ref{motionSignature}
+\subsection{Partial Matching of Motion Signatures}\label{sec_mcc}
+This section presents how a template $p$ motion can be checked against motion with signature $W$ for potential matching.
+All the steps are same as done for partial matching of path signature except the cross-correlation function which is given by,
+
+\begin{equation}\label{mccEq}
+  E(j, p, W) = \sum_{i}^{p_{span}} {((W(i+j) - \bar{W}(j\to j + p_{span})) - (p(i) - \bar{p}))}^2,
+\end{equation}
+where $E(j, p, W)$ is the dissimilarity value when template $p$ is matched to $W$ at $j^{th}$ index. Here $p$ tries to find best match against $W(i)$ while sliding over it.
+Similar to path signature, motion signature is dependent on the sampling direction along the motion.
+Thus we compute the dissimilarity for both direction and the take whichever is the least i.e.
+$E_{min}(p, W)$.
+Figure~\ref{mcc} depicts dissimilarity function over the sliding domain $j$ for two curves shown in Fig.~\ref{wholePart}.
+In the case shown in example~\ref{mcc}, we find that first point itself is start point where the perfect match is occurred which is consistent with the fact that we slice the motion in similar manner.
 
@@
 \includegraphics[width=240pt]{figure/fig_motion_signatures.eps}
-  \caption{Motion Signatures of the trajectories shown in Fig.\ref{wholePart}. The same correlation function can be used to compute whole-to-part matching.}
+  \caption{Motion Signatures of the trajectories shown in Fig.\ref{wholePart}. The domain as well as range of motion signature is invariant to similarity transformation.}
 \label{motionSignature}
@@
 
+\begin{figure}
+\centering
+\includegraphics[width=240pt]{figure/fig_mcc.eps}
+  \caption{Dissimilarity function of two motion signatures along both directions. It can be seen that exact match is found at $j=0$, where template is fully embedded inside the other motion.}
+\label{mcc}
+\end{figure}
+
 \subsection{Objective Function for Synthesis}
-The Normalized Cross-Correlation function presented in the section~\ref{sec_ncc} can be used the criterion for motion (or path) synthesis of any planar linkage, where the objective is to find a linkage, that produces a motion whose part or whole corresponds to target motion (or path).
-Thus we can formulate the optimization problem given by,
+The functions in Eq.~\req{nccEq} or ~\req{mccEq} presented in the sections \ref{sec_ncc}, \ref{sec_mcc} can be used as the error measure for path or motion synthesis of any planar linkage, where the objective is to find a linkage, that produces a motion whose part or whole corresponds to target motion (or path).
+Thus we can formulate the path synthesis problem as,
 
-\begin{equation}\label{objectiveFun}
-  \argminA_{\textbf{\emph{l}}} f_{obj}(\textbf{\emph{l}}) = 1 - \max\limits_{j}(Cn(j))
+\begin{equation}\label{objectiveFunPath}
+  \argminA_{\textbf{\emph{l}}, W_i} (1 - Cn_{max}(p, W_i)
 \end{equation}
-where $\textbf{\emph{l}}$ is the vector of linkage parameters for perticular planar linkage.
+where $\textbf{\emph{l}}$ is the vector of linkage parameters for particular planar linkage, p is the task curve taken as template for Normalized Cross-Correlation and ${\{W_i\}}_{i=0}^{s}$ is the signature set of all coupler paths generated by the linkage.
 In case of four-bar, $\textbf{\emph{l}}: l_1, l_2, l_3, l_4, l_5$, with $l_i$ is link ratio of $i^{th}$ link shown in Fig~\ref{fourbar}.
+
+Similarly, we can formulate motion synthesis as,
+\begin{equation}\label{objectiveFunMotion}
+  \argminA_{\textbf{\emph{l}}, W_i} (E_{min}(p, W_i)
+\end{equation}
+Here, E is the Dissimilarity function from eq.~\req{mccEq} while p and ${\{W_i\}}_{i=0}^{s}$ are motion signatures instead of path signatures.
 
@@
 \includegraphics[width=240pt]{figure/fig_fourbar.eps}
-  \caption{Parametric representation of four-bar linkage with all revolute joints.}
+  \caption{Parametric representation of four-bar linkage with all revolute joints.
+We set $l_0 = 1$ and one fixed joint at origin of the global frame along with making fixed length of the fourbar parallel to x axis.}
 \label{fourbar}
@@
 
-Objective function evaluation step consists of calculation of coupler motion and finding its best normalized cross-correlation score.
+Objective function evaluation step consists of calculation of coupler motion or path and finding its dissimilarity score.
 It is important to note that representation obtained in Section~\ref{sec_sign} reduces size of the linkage parameters in optimization.
-This optimization problem can be solved using search methods which do not require gradient computation as algebraic representation of objective function in terms of linkage parameters is not possible.
-We can employ global optimization methods such as differential evolution, simulated annealing at the start and local optimization methods link powell's method towards the end for faster convergence\cite{ullah1997}.
-Section~\ref{examples} presents results for various optimization techniques used.
+This optimization problem can be solved using search methods which do not require gradient computation.
+We can employ global optimization methods such as differential evolution at the start and local optimization methods link Powell's method towards the end for faster convergence\cite{ullah1997}.
+Section~\ref{examples} presents results for the optimization technique used.
 
@@
 
-\section{Sensitivity Analysis of Signatures}
+\section{Sensitivity Analysis of Signatures}\label{sec_SA}
 Owing to the complex relationship between parameter space and generated motion, small change in linkage parameters can produce large and discontinuous structural change in the generated motions.
-For example small change in crank length can open a previously close loop.
-Most of the analytical methods like Fourier analysis can not capture the continuity at such singular locations, which adversely affect the optimization process.
-In contrast to this behavior, Signatures derived in Sec.~\ref{sec_sign} has smooth transition at these singular locations.
-To make our point, we perform Sensitivity Analysis as follows:
-A four-bar with link ratios ($l_1:0.3$, $l_2:1$, $l_3:1.5$, $l_4:1$, $l_5:1$) is subjected to gradual change in parameter $l_1$ in the range (0.3, 0.8) in steps of 0.1.
-Figure~\ref{saCouplerCurves} shows coupler motion of the fourbars associated with change in $l_1$.
-Although the close circuit breaks to form open curves, It is evident how smooth the shape changes in the process.
-This smoothness is captured in the Heat Map shown in Fig.~\ref{saHeatmap} obtained by similarity evaluations via Normalized Cross-Correlation of corresponding signatures.
-If we construct the graph (see Fig.~\ref{saGraph}) based on the adjacency matrix and igore the edges when distance is more than 0.2, we get a \emph{small world network}\cite{watts1998}.
+For example small change in crank length ($l_1$) can open a previously close loop.
+Most of the methods based on Fourier descriptors are if defined, can not capture the continuity at such singular locations, which adversely affect the optimization process.
+In contrast to this behavior, the signatures derived in Sec.~\ref{sec_sign} have smooth transition at these singular locations due to shape similarity between a closed and just opened curve or motion.
+To make our point, we perform sensitivity analysis as follows:
+A four-bar with link ratios ($l_1:0.55$, $l_2:1$, $l_3:1.5$, $l_4:1$, $l_5:1$) is subjected to gradual change in parameters $l_1$ and $l_3$ by the amount (-0.2, 0.2) in steps of 0.01.
+Error functions for motion using eq.~\req{objectiveFunMotion} are calculated between new and initial fourbar.
+Figure~\ref{saCouplerCurves} shows coupler motion of some of the four-bars while Fig.~\ref{saMotionSignatures} depicts their motion signatures.
+It can be seen from Fig.~\ref{saCouplerCurves} that there exists a discontinuity in topology of the coupler curves even though their shapes have a continuous shift.
+Our method captures this continuity, which is shown by error function evaluations depicted in Fig.~\ref{saErrorFunction}.
 
@@
 \includegraphics[width=240pt]{figure/fig_sa_coupler_curves.eps}
-  \caption{Hi}
+  \caption{Coupler Motions of the fourbar linkage with variation of parameters $l_1$ and $l_2$. It can be seen that motion topology changes from close-loop Grashof to open loop Triple-Rocker.}
 \label{saCouplerCurves}
@@
 \centering
-\includegraphics[width=240pt]{figure/fig_sa_heatmap.eps}
-  \caption{Hi}
-\label{saHeatmap}
+\includegraphics[width=240pt]{figure/fig_sa_distance_function.eps}
+  \caption{Distance ($E_{min}$) from eq.~\req{mccEq} as the parameters $l_1$ and $l_2$ are varied.
+Although open loop breaks between $l_1$:(0.5, 0.6), $l_3$:1.5 parameter values, there are no spikes in the error function as the shape is very similar between the two topologies.}
+\label{saErrorFunction}
 \end{figure}
@@
 \centering
-\includegraphics[width=240pt]{figure/fig_sa_graph.eps}
-  \caption{Hi}
-\label{saGraph}
+\includegraphics[width=240pt]{figure/fig_sa_motion_signatures.eps}
+  \caption{Motion signatures obtained by steps given in~\ref{sec_sign}.
+Although topology difference is even more evident in this representation, it also signifies the similarity pattern between them.}
+\label{saMotionSignatures}
 \end{figure}
 
-\section{Clustered Database of Planar Linkages}
-Having a invariant representation greatly reduces data required to sample all possible types shapes of coupler motion.
+\section{Clustered Database of Planar Linkages}\label{sec_db_ae}
+Having a invariant representation facilitating partial matching greatly reduces data required to sample all possible types shapes of coupler motion.
 We have built a database of planar four-bar linkages with revolute joints as an example, but the approach is same for any planar motion generating machine.
-We generate this database while taking following aspects into consideration.
+We generate this database comprising of $40,000$ linkages, while taking following aspects into consideration.
 \begin{enumerate}
-  \item Sampling should maximize its distribution over possible four-bar coupler motions.
+  \item Sampling should maximize the uniformity of its distribution over the space of four-bar coupler motions.
   \item Data generation can be parallelized.
-  \item Approach scalable with linkages with more number of links.
+  \item Scalable with linkages with more number of links.
 \end{enumerate}
@@
 \subsection{Dimensionality Reduction using Auto-Encoders}
-Each data point in database consists of discrite signature of motion, which is kept to be 100 float digits.
-In order to have efficient query operations we perform clustering, a method that summarizes and creates a hierarchy in the database.
-Clustering in higher dimensions suffers from \emph{Curse of Dimensionality}, thus we first perform dimensionality reduction using Auto-encoder Neural Networks.
-Auto-encoder is a powerful mapping model, which learns to encode the input data in very compact representation and can reconstruct the input with minimal error; performing much better than PCA\cite{hinton2006}.
-This Non-linear mapping by auto-encoder can greatly improve the representation of data for clustering\cite{song2013}.
+Each data point in database consists of discrete signature of motion, which is kept to be of 100 float digits.
+In order to have efficient query operations, we perform Hierarchical Clustering; a method that summarizes and creates a hierarchy in the database.
+Clustering in higher dimensions suffers from \emph{Curse of Dimensionality}\cite{marimont1979}, thus we first perform dimensionality reduction using Auto-encoder Neural Networks.
+Auto-encoder is a powerful mapping model, which learns to encode the input data in very compact representation and can reconstruct the input with minimal error; performing much better than Principal Component Analysis\cite{hinton2006}.
+This Non-linear mapping by auto-encoder can greatly improve the representation of data for clustering (For details refer \cite{song2013}).
 Figure~\ref{autoEncoder} shows an architecture similar to the Neural Network we designed for the task.
 Number of neurons per layer are (100, 80, 50, 10, 50, 80, 100).
-Each hidden layer is activate by Rectified Linear Unit (\emph{ReLU}) activation function.
-In $i^{th}$ hidden layer, output of the previous layer $h_(i-1)$ is fed as input to produce output $h_i$ given by,
+Each neuron in the hidden layer is activated by Rectified Linear Unit (\emph{ReLU}) activation function.
+In $i^{th}$ hidden layer, $d^{(i-1)}$ dimensional vector output of the previous layer $h_(i-1)$ is fed as input to produce $d^{(i)}$ dimensional output $h_i$.
+Input-output relationship of a layer is given by,
 
@@
 
-Where $W_i$ and $b_i$ are weights and bais of $i^{th}$ layer, which are computed in the process of training.
+Where $W_i$ is weight matrix with dimensions $(d^{i}, d^{(i-1)})$ and $b_i$ is $d^{(i)}$ dimensional bias vector of $i^{th}$ layer, which are computed in the process of training.
 Auto-encoders are trained to reconstruct the input, in this way each layer encodes the input, which is sufficient for the next layers to reconstruct the output.
@@
 \begin{equation}\label{nnloss}
-  E = \sum_{i=0}^{N} || X_i - \grave{X}_i ||^2
+  \argminA_{W, b} \sum_{i=0}^{N} || X_i - \tilde{X}_i ||^2
 \end{equation}
-where $X_i$ is input, $\grave{X}_i$ is reconstructed output and N is number of training examples.
+where $X_i$ is input, $\tilde{X}_i$ is reconstructed output and N is number of training examples.
 
@@
 Standard clustering algorithms are performed on this latent space for better clustering\cite{song2013}.
-We use Agglomeretive Clustering, a method of Hierarchical clustering, which is an approach to partitioning clustering for identifying groups in the dataset.
-It does not require to pre-specify the number of clusters to be generated.
+We use Agglomerative Clustering, a method of Hierarchical clustering, which is an approach to partitioning clustering for identifying groups in the dataset.
 \emph{Ward}\cite{ward1963} Linkage criterion is used for clustering, which minimizes the variance of the clusters being merged.
 The distance metric used is the euclidean distance in the latent space.
-Although the more accurate distance metric is normalized cross correlation score, it is very expensive to calculate it for entire database.
-Signatures with $\mathcal{O}(m)$ points, take $\mathcal{O}(m\log{}m)$ time for each comparisons and there are $\mathcal{O}(N^2)$ number of comparisons to be made for database of $N$ points.
-Thus we pick one sample from each cluster and perform Agglomeretive Clustering on this set with normalized cross correlation as the distance metric to form a top cluster.
-When user raises one such query, we first find k nearest neighbors in the top cluster, then descend into their neighbors.
-Motion with highest similarity score is returned along with its corresponding linkage parameters which are further fine-tuned to match query using optimization.
+Although the more accurate distance metric is distance function discussed in sec.~\ref{sec_distanceMetric}, it is very expensive to calculate it for entire database.
+Signatures with ${O}(m)$ points, take ${O}(m\log{}m)$ time for each comparisons and there are ${O}(N^2)$ number of comparisons to be made for database of $N$ points.
+When user raises one such query, we first find k nearest neighbors among $1500$ cluster centers, then descend into their clusters if needed.
+Motion with highest similarity score is returned along with its corresponding linkage parameters which if required, are further fine-tuned to match the query using local optimization.
 
@@
 \includegraphics[width=240pt]{figure/fig_auto_encoder.eps}
-  \caption{A general architecture of Auto-Encoder. Actual implementation has five hidden layers where middle layer is the bottleneck.}
+  \caption{A small scale version of the Auto-Encoder.
+This network takes 5 dimensional input in the input layer.
+At each encoder layer, input is compressed into vector of lesser dimensions, lowest at the bottleneck layer.}
 \label{autoEncoder}
@@
 
-\section{Algorithm}
-\begin{algorithm}[thb]
-\caption{Algorithm for Optimal Four-bar Linkage Synthesis}\label{algorithm1}
-\begin{algorithmic}[1]
-\Procedure{Lagrange Multiplier Method}{}\\
-linear constraints$ (n) \leq 5$
-\For {each linear constraint}
-\State{add constraint eq. to [A]}
-\EndFor\label{}
-\State{perform SVD and pick $n-8$ Singular Vectors}
-\State $f = 0$
- \State{error function for each of the relaxed constraint $\rightarrow$ $f_i$}
- \For {each $f_i$}
-\State{$f = f + {f_i}^2$}
-\EndFor\label{}
-\State{form $h_1$ and $h_2$ using Eq.~\ref{h1h2}}
-\If{nonlinear constraints exist}
-\State{number of non linear constraints =  $m$}
-\For {each $m$}
-\State{form $h_{(2+m)}$ using Eq.~\ref{nonlinEq} }
-\EndFor\label{}
-\EndIf\label{}
-\State {{\bf Minimize} $f$ subjected to $h_1 = 0$,..,$h_{(2+m)} = 0$, $g \leq 0$ }
-\State {Minimize $F$ by Lagrange Multipliers}
-\State {$F = -f - \lambda_1h_1 -...-\lambda_{(m+2)}h_{(m+2)} - \mu g$}
-\State {Take partial derivatives of $F$ w.r.t. $\alpha_2$,..,$\alpha_{(8-n)}$,$\lambda_1$,..,$\lambda_{(2+m)}$ to form a system of Equations along with Eq.\req{kkt1}},
-\State {{\bf Solve} $(9 - n  + m) $ equations}
-\State {{\bf Compute} dyad parameters}
-\EndProcedure
-\end{algorithmic}
-\end{algorithm}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Examples}\label{examples}
-
-\begin{table}
-\caption{Example~\ref{5pos}: Pose Data}
-\centering
-\label{5posMotion}
-\begin{tabular}{cccc}
-\hline
-Poses & X & Y & $\phi$ (degree)\\
-\hline
-Pose 1 &  -5.74803 & -0.00787402 & 88.5679 \\
-Pose 2 &  -4.12598 & 0.795276 & 2.16642 \\
-Pose 3 &  -2.72441 & 1.67717 & 356.968 \\
-Pose 4 &   -1.54331 & 0.433071 & 1.03102 \\
-Pose 5 &   1.22835 & -0.590551 & 345.624 \\
-\hline
-\end{tabular}
-\end{table}
-
-\begin{table*}[thb]
-  \caption{Example \ref{5pos}: Four singular vectors obtained after SVD of the matrix $[A]$ of size $4\times8$.}
-  \centering
-  \begin{tabular}{ccccccccc}
-  \hline
-  Dyad Vector &$p_1$&$p_2$&$p_3$&$p_4$&$p_5$&$p_6$&$p_7$&$p_8$\\
-    \hline
-   $\textbf{p}_1$& -0.01874 & -0.2516 & 0.5174 & -0.3985 & 0.02237 & 0.03616 & 0.4980 & 0.5097\\
-$\textbf{p}_2$&0.007703 & 0.4284 & -0.3233 & 0.5047 & -0.02227 & -0.06264 & 0.4823 & 0.4688\\
-$\textbf{p}_3$& 0.02871 & 0.08073 & 0.1114 & 0.1484 & -0.0120 & 0.9778 & -0.03979 & 0.01384\\
-$\textbf{p}_4$& 0.07561 & -0.1628 & 0.02429 & 0.1901 & 0.9647 & -0.009039 & -0.007750 & 0.01223\\
-    \hline
-  \end{tabular}
-  \label{svectors5pos}
-\end{table*}
-
-\begin{table*}[thb]
-  \caption{Example \ref{5pos}: Two optimum dyad-vectors obtained as result of optimization}
-  \centering
-  \begin{tabular}{ccccccccc}
-  \hline
-  Vector &$p_1$&$p_2$&$p_3$&$p_4$&$p_5$&$p_6$&$p_7$&$p_8$\\
-   \hline
-$\textbf{s}_1$&0.4175 & 1.025 & 5.818 & 1.388 & 0.8691 & 17.21 & 7.760 & 8.773 \\
-$\textbf{s}_2$&0.08080 & 0.007451 & 0.07404 & 0.3656 & 0.9573 & 0.2468 & 0.4554 & 0.4875\\
-   \hline
-  \end{tabular}
-  \label{dyadvectors5pos}
-\end{table*}
+\section{Examples}\label{sec_example}
+This sections presents a case study presenting the effectiveness of our approach.
+The task is to find a pool of linkage systems that can perform snow-shoveling with a motion shown in Fig.~\ref{motionQuery}.
+The motion data is tabulated in Table ~\ref{poseData} which we fit into a B-spline with arc-length parameterization.
+The task can be treated as a finite position motion generation and solved for valid solutions.
+We try with our real time computational methods of algebraic fitting\cite{generalfitting-JCISE},\cite{deshpande2017} but the solutions obtained suffer from circuit defect.
+Now we employ the approach presented in this paper.
+First step is to calculate motion signature of the task motion.
+For that we follow the steps given in section~\ref{sec_sign} to obtain the motion signature depicted in Fig.~\ref{queryResult}.
+Next we raise the signature query for nearest signatures among the cluster centers of the database.
+Fig.\ref{queryResult} shows nine nearest neighbor signatures along with task signature.
+Table ~\ref{knnLinkageData} presents the linkage parameters corresponding to the nearest neighbors along with their distance score from the task.
+Coupler motions of these linkages have a part which matches with the shape of input motion query.
+Actual scaling and orientation of the linkage can be found out easily by comparing analogous points which are given by the offset index $j$ that corresponds to minimum distance$(E_min)$ in eq.~\req{mccEq}.
+Figures~\ref{knnSol1} to \ref{knnSol7} depict the solutions obtained after scaling and orienting the linkage to match required motion.
+Although all of these linkages satisfactorily perform the input task with any defect, linkages in Fig.~\ref{knnsol1}, \ref{knnsol2}, \ref{knnsol3}, \ref{knnsol7} are suitable for the task considering the pivot locations.
+Nevertheless this approach produces a large variety of solutions which otherwise would have been very hard to found using precision point approach.
 
@@
 \centering
-\includegraphics[width=200pt]{figure/fig1.eps}
-\caption{Example \ref{5pos}: Optimal four-bar mechanism that minimizes algebraic fitting error for third pose.
-Although second pose lies on different circuit, this Grashof type four-bar produces desired continuous motion from first to last pose.}
-\label{5posgg}
+\includegraphics[width=240pt]{figure/fig_motion_query.eps}
+  \caption{Motion Query : Task Motion drawn specified by user.}
+\label{motionQuery}
 \end{figure}
 
-\subsection{Optimal Linkage for Four Precision Poses with Region Constraint}\label{4pos1line1pose}
 \begin{figure}
 \centering
-\includegraphics[width=230pt]{figure/fig2.eps}
-\caption{Example \ref{4pos1line1pose}: Five landing gear positions are shown where the third position can be relaxed. Allowed region for fixed pivots of mechanism is also shown.}
-\label{4posproblem}
+\includegraphics[width=240pt]{figure/fig_ex_motion_signatures.eps}
+  \caption{Query Result: Motion signatures in the dataset with highest similarity.}
+\label{queryResult}
 \end{figure}
@@
 \begin{table}
-\caption{Example~\ref{4pos1line1pose}: Pose Data}
+\caption{Example : Pose Data}
 \centering
-\label{4posMotion}
+\label{poseData}
 \begin{tabular}{cccc}
 \hline
-Poses & X & Y & $\phi$ (degree)\\
+Pose & x & y & $\theta$ \\
 \hline
-Pose 1 &  -0.0125 & -0.0374 & 66.3 \\
-Pose 2 &  0.303 & 0.634 & 35.5 \\
-Pose 3 &  0.599 & 1.83 & 352. \\
-Pose 4 &  0.268 & 2.30 & 331. \\
-Pose 5 &  0.606 & 1.31 & 22.2 \\
-\hline
-\end{tabular}
-\end{table}
-
-\begin{table*}[thb]
-  \caption{Example \ref{4pos1line1pose}: Four singular vectors obtained after SVD of the matrix $[A]$ of size $4\times8$. The vectors form basis for the null space}
-  \centering
-  \begin{tabular}{ccccccccc}
-  \hline
-  Vector &$p_1$&$p_2$&$p_3$&$p_4$&$p_5$&$p_6$&$p_7$&$p_8$\\
-    \hline
-   $\textbf{p}_1$& -0.585 & -0.0211 & -0.506 & 0.165 & 0.134 & -0.350 & 0.368 & 0.313 \\
-   $\textbf{p}_2$& 0.0640 & -0.330 & 0.190 & -0.804 & 0.236 & -0.264 & 0.194 & 0.204 \\
-   $\textbf{p}_3$& -0.280 & 0.0484 & -0.466 & -0.398 & 0.232 & 0.603 & -0.136 & -0.329 \\
-   $\textbf{p}_4$& -0.137 & 0.145 & 0.469 & 0.250 & 0.747 & 0.229 & 0.259 & 0.0111 \\
-    \hline
-  \end{tabular}
-  \label{svectors4pos}
-\end{table*}
-
-\begin{table*}[thb]
- \caption{Example \ref{4pos1line1pose}: Four optimum dyad-vectors obtained as result of optimization}
-  \centering
-  \begin{tabular}{ccccccccc}
-  \hline
-  Vector &$p_1$&$p_2$&$p_3$&$p_4$&$p_5$&$p_6$&$p_7$&$p_8$\\
-    \hline
-$\textbf{s}_1$&  0.0254 & 0.192 & -0.202 & -0.0965 & 0.00562 & 0.723 & -0.387 & -0.490 \\
-$\textbf{s}_2$& 0.276 & -0.406 & 0.211 & -0.425 & -0.161 & -0.561 & 0.251 & 0.360 \\
-$\textbf{s}_3$& 0.315 & -0.356 & 0.189 & -0.397 & -0.318 & -0.598 & 0.129 & 0.324 \\
-$\textbf{s}_4$& 0.208 & -0.302 & 0.141 & -0.335 & -0.321 & -0.691 & 0.134 & 0.368 \\
-    \hline
-  \end{tabular}
-  \label{dyadvectors4pos}
-\end{table*}
-
-Figure~\ref{4posproblem} shows five positions of a landing gear moving from the landing position to the retracted position.
-Table~\ref{4posMotion} contains position and orientation data for five poses.
-It is desirable that fixed pivots should lie inside the circle of radius 2.3 with center located at (3.33, 2.04).
-The task is to synthesize a mechanism which interpolates through precision poses (1,2,4,5) and minimizes the algebraic error for the third pose while keeping fixed pivot locations inside the allowed region as shown in the figure.
-
-First step is to extract all four geometric constraints, i.e.
-four precision poses and form matrix $[A]$  using Eq.~\req{A8}.
-Here $n = 4$ which means solution space consists of 4 singular vectors which are obtained using SVD and tabulated in Table~\ref{svectors4pos}.
-Once this linear algebraic fitting is done, optimization problem can be formulated.
-
-The error function is linear error function $f_1$ for third pose, which is evaluated using Eq.~\req{poseError}.
-Substituting singular vectors into dyad coefficients followed by substituting them in terms of $\alpha_i$ using Eq.~\req{solutionSpace}, we get final objective function given by
-\begin{equation}
-f = f_1^2,
-\end{equation}
-where $f_1 = -0.0598 {\alpha_2}+0.0294 {\alpha_3}-0.100 {\alpha_4}+0.0876$.
-The circular region for fixed pivots is modeled as an inequality constraint using Eq.~\req{ellipseIneq} and~\req{g} given by,
-\begin{equation}
-\begin{array}{c}
-g = 0.091 {\alpha_2}^2+(0.25 {\alpha_3}+0.11 {\alpha_4}+0.25) {\alpha_2}\\+0.35 {\alpha_3}^2+0.049 {\alpha_4}^2+{\alpha_3} (0.043 {\alpha_4}+1.0)\\-0.048 {\alpha_4}-0.19 \leq 0
-\end{array}
-\end{equation}
-Objective function also has two quadratic equality constraints given by,
-\begin{eqnarray}
-& & h_1 = 0.058 {\alpha_2}^2+(-0.25 {\alpha_3}+0.17 {\alpha_4}-0.36) {\alpha_2} -0.34 {\alpha_3}^2  \nonumber \\
-& & \ \ \ \ \ \ \ \ \  -0.041 {\alpha_4}^2+{\alpha_3} (0.23 {\alpha_4}-0.38)-0.033 {\alpha_4}+0.29, \nonumber \\
-& & h_2  = -0.29 {\alpha_2}^2+{\alpha_2} (-0.15 {\alpha_3}-0.074 {\alpha_4}-0.048)+0.20 {\alpha_3}^2 \nonumber \\
-& & \ \ \ \ \ \ \ \ \  +{\alpha_3} (0.18 {\alpha_4}+0.12)-0.46 {\alpha_4}^2-0.11 {\alpha_4}-0.36 \nonumber \\
-\end{eqnarray}
-We follow steps presented in section~\ref{lagrangeMultiplier} and form Lagrange objective function $F$ given by,
-\begin{equation}
-F = -{f_1}^2- \lambda_1h_1 -  \lambda_2h_2 - \mu g
-\end{equation}
-and obtain equations by partial differentiation as well as equation corresponding to Karush-Kuhn-Tucker condition as follow:
-
-\begin{equation}
-\begin{array}{c}
-\frac{\partial}{\partial \alpha_2}(F) = 0 = (-0.12 {\alpha_2}+0.25 {\alpha_3}-0.17 {\alpha_4}+0.36) {\lambda_1}+(0.57 {\alpha_2}\\+0.15 {\alpha_3}+0.074 {\alpha_4}+0.048) {\lambda_2}-(0.18 {\alpha_2}) \mu \\-(0.25 {\alpha_3}) \mu -(0.11 {\alpha_4}) \mu -0.25 \mu +0.060
-\end{array}
-\end{equation}
-
-\begin{equation}
-\begin{array}{c}
-\frac{\partial}{\partial \alpha_3}(F) = 0 = {\lambda_1} (0.25 {\alpha_2}+0.69 {\alpha_3}-0.23 {\alpha_4}+0.38)+{\lambda_2}\\ (0.15 {\alpha_2}-0.41 {\alpha_3}-0.18 {\alpha_4}-0.12)-0.25 {\alpha_2} \mu\\ -0.71 {\alpha_3} \mu -0.043 {\alpha_4} \mu -1.0 \mu -0.029
-\end{array}
-\end{equation}
-
-\begin{equation}
-\begin{array}{c}
-\frac{\partial}{\partial \alpha_4}(F) = 0 = {\lambda_1} (-0.17 {\alpha_2}-0.23 {\alpha_3}+0.081 {\alpha_4}+0.033)\\+{\lambda_2} (0.074 {\alpha_2}-0.18 {\alpha_3}+0.92 {\alpha_4}+0.11)-0.11 {\alpha_2} \mu\\ -0.043 {\alpha_3} \mu -0.097 {\alpha_4} \mu +0.048 \mu +0.10
-\end{array}
-\end{equation}
-
-\begin{equation}
-\begin{array}{c}
-\frac{\partial}{\partial \lambda_1}(F) = 0 =-0.058 \alpha_2^2+(0.25 \alpha_3-0.17 \alpha_4+0.36) \alpha_2\\+0.34 \alpha_3^2+0.041 \alpha_4^2+\alpha_3 (0.38-0.23 \alpha_4)+0.033 \alpha_4-0.29
-\end{array}
-\end{equation}
-
-\begin{equation}
-\begin{array}{c}
-\frac{\partial}{\partial \lambda_2}(F) = 0 =0.29 \alpha_2^2+(0.15 \alpha_3+0.074 \alpha_4+0.048) \alpha_2\\-0.20 \alpha_3^2+0.46 \alpha_4^2+\alpha_3 (-0.18 \alpha_4-0.12)+0.11 \alpha_4+0.36
-\end{array}
-\end{equation}
-
-\begin{equation}
-\begin{array}{c}
-\mu\frac{\partial}{\partial \mu}(F) = 0 =\mu(-0.091 \alpha_2^2+(-0.25 \alpha_3-0.11 \alpha_4-0.25) \alpha_2\\-0.35 \alpha_3^2-0.049 \alpha_4^2+\alpha_3 (-0.043 \alpha_4-1.0)+0.048 \alpha_4+0.19)
-\end{array}
-\end{equation}
-
-Solving these equations followed by filtering on the basis of feasibility using Eq.~\ref{kkt2} yields four unique and feasible solutions tabulated in Table~\ref{alphasol}.
-All of these solutions satisfy Karush-Kuhn-Tucker Condition for optimality given by Eq.~\req{kkt3}.
-Dyad vectors are calculated by substituting these solutions into \req{solutionSpace} and are given in Table ~\ref{dyadvectors4pos}.
-Any of these four dyad-vectors when substituted in Eq.~\req{general} forms a quartic equation, which when projected on hyperplane $Z_4 = 1$ represents a quadric surface.
-Fig.~\ref{4posmanifolds} shows intersection of hyperboloid and hyperbolic paraboloid  formed from first and second dyad-vectors.
-The intersection curve represents workspace of the corresponding four-bar linkage.
-Table~\ref{error4pos} contains the minimized algebraic fitting error of objective function.
-From this table, we can see that dyad $\textbf{s}_4$ has least pose fitting error.
-All dyads except $\textbf{s}_1$ are of RR type dyads while $\textbf{s}_1$ is an RP dyad.
-Figure~\ref{4posRRRP} shows a branch defect free four-bar mechanism formed by combining $\textbf{s}_1$ and $\textbf{s}_2$.
-
-\begin{table}
-\caption{Real Solutions for $\alpha_i$, $\lambda_i$ and $\mu$}
-\centering
-\label{alphasol}
-\begin{tabular}{cccccccc}
-\hline
-Dyad &$\alpha_1$&$\alpha_2$ & $\alpha_3$& $\alpha_4$& $\lambda_1$& $\lambda_2$& $\mu$\\
-\hline
-$\textbf{s}_1$  & 1 & -0.40 & -0.027 & 1.09 & 0.0 & 0.0 & 0.0 \\
-$\textbf{s}_2$ & 1 &  -2.04 & -1.81 & 2.06 & 0.0 & 0.0 & 0.0 \\
-$\textbf{s}_3$ & 1 &-3.64 & -4.24 & 5.37 & 0.0 & 0.0 & 0.0 \\
-$\textbf{s}_4$ & 1 & 5.08 & -2.58 & -2.94  & 0.0 & 0.0 & 0.0 \\
-\hline
+1 & 0.03 & 0.07 & 6.06 \\
+2 & 0.38 & 0.01 & 6.18 \\
+3 & 0.71 &-0.00 & 0.04 \\
+4 & 1.02 & 0.06 & 0.22 \\
+5 & 1.26 & 0.22 & 0.46 \\
+6 & 1.39 & 0.47 & 0.73 \\
+7 & 1.36 & 0.77 & 1.03 \\
+8 & 1.18 & 1.06 & 1.36 \\
+9 & 0.88 & 1.27 & 1.74 \\
 \end{tabular}
@@
 \begin{table}
-\caption{Optimality Evaluations for Dyads}
+\caption{Linkage Parameters of Five Nearest Neighbor Motions}
 \centering
-\label{error4pos}
-\begin{tabular}{ccc}
+\label{knnLinkageData}
+\begin{tabular}{ccccccc}
 \hline
-Dyad & $3^{rd}$Pose-Fitting Error & Inequality Constraint \\
+  linkage & $l_1$ & $l_2$ & $l_3$ & $l_4$ & $l_5$ & $f_{obj}$ \\
 \hline
-$\textbf{s}_1$ &  0.0102 & -0.000650 \\
-$\textbf{s}_2$ &  0.0415 & -0.00126 \\
-$\textbf{s}_3$ &  0.0212 & -0.000424 \\
-$\textbf{s}_4$ & -1.8$\times10^{-8}$ &  -0.396 \\
-\hline
+ 1 & 1.28 & 0.88 & 1.77 & -1.32 & 1.79 & 0.0186   \\
+ 2 & 1.05 & 1.14 & 1.09 & 0.35 & -0.60 & 0.0362   \\
+ 3 & 2.06 & 2.28 & 1.84 & -1.71 & 0.51 & 0.0378   \\
+ 4 & 1.52 & 1.22 & 1.46 & 0.05 & 0.12 & 0.0402    \\
+ 5 & 1.12 & 0.99 & 0.57 & 0.05 & 0.68 & 0.0467    \\
+ 6 & 1.58 & 0.88 & 1.17 & 0.08 & -0.22 & 0.0481   \\
+ 7 & 2.17 & 0.38 & 2.87 & -3.51 & 1.39 & 0.0578   \\
+ 8 & 1.55 & 0.79 & 0.85 & -0.80 & -0.52 & 0.0585  \\
+ 9 & 0.91 & 1.40 & 1.93 & -0.93 & -0.83 & 0.0605
 \end{tabular}
@@
 \centering
-\includegraphics[width=230pt]{figure/fig3.eps}
-\caption{Example \ref{4pos1line1pose}: First and second dyad in Table ~\ref{dyadvectors4pos} are combined to form the linkage shown.
-It can be clearly seen that coupler curve fairly approximates the third pose while fixed pivots are inside the allowed region.}
-\label{4posRRRP}
+\includegraphics[width=240pt]{figure/sol1.eps}
+  \caption{First Linkage in the table~\ref{knnLinkageData} and its resultant motion.}
+\label{knnSol1}
 \end{figure}
@@
 \centering
-\includegraphics[width=250pt]{figure/fig4.eps}
-\caption{Example \ref{4pos1line1pose}: Image-Space representation of intersection of third and fourth optimal constraint manifolds from Table.~\ref{dyadvectors4pos}.
-Also shown are five image points as dark spheres representing the five poses; four of them lie exactly on the intersection of the two surfaces, while one is closest possible.}
-\label{4posmanifolds}
+\includegraphics[width=240pt]{figure/sol2.eps}
+  \caption{Second Linkage in the table~\ref{knnLinkageData} and its resultant motion.}
+\label{knnSol2}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=240pt]{figure/sol3.eps}
+  \caption{Third Linkage in the table~\ref{knnLinkageData} and its resultant motion.}
+\label{knnSol3}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=240pt]{figure/sol4.eps}
+  \caption{Fourth Linkage in the table~\ref{knnLinkageData} and its resultant motion.}
+\label{knnSol4}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=200pt]{figure/sol5.eps}
+  \caption{Fifth Linkage in the table~\ref{knnLinkageData} and its resultant motion.}
+\label{knnSol5}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=240pt]{figure/sol6.eps}
+  \caption{Sixth Linkage in the table~\ref{knnLinkageData} and its resultant motion.}
+\label{knnSol6}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=240pt]{figure/sol7.eps}
+  \caption{Seventh Linkage in the table~\ref{knnLinkageData} and its resultant motion.}
+\label{knnSol7}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=240pt]{figure/sol7.eps}
+  \caption{Eighth Linkage in the table~\ref{knnLinkageData} and its resultant motion.}
+\label{knnSol8}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=240pt]{figure/sol7.eps}
+  \caption{Eighth Linkage in the table~\ref{knnLinkageData} and its resultant motion.}
+\label{knnSol9}
 \end{figure}
@@
 \section*{Conclusion}
-In this paper, we presented a task-driven approach to unified and optimal synthesis of planar four-bar linkages for extended Burmester problem.
-In this formulation, various geometric constraints are treated equivalently, which in turn leads to a much simpler two-step based algorithm for computing planar dyads of four-bar linkages.
-Original contributions of this paper have been into reforming a mixed exact-approximate algebraic fitting problem into problem of task oriented optimal fitting of algebraic manifold.
-The framework presented here can accommodate linear as well as non-linear equality and inequality geometric constraints and minimize objective functions that can be expressed in terms of dyadic parameters.
-Although adding non-linear geometric constraints increase computational complexity, computer algebra software like Mathematica could be used to compute solutions of quadratic system of equations in a reasonable amount of time.
-Experimentations show that Mathematica takes less than 3 seconds on a MacBook Pro with 2.4GHz Intel core i5 processor and 8GB RAM for computing solutions for the system of seven quadratic equations.
-The framework also preserves previously achieved real-time solutions for linear geometric constraints with no optimality criterion.
-Two examples demonstrating computation of optimal type and dimensions of dyads that minimize task oriented objective function are presented.
+This approach presents a novel optimization approach towards defect free linkage synthesis.
+The framework is highly data efficient due to similarity invariant representation of paths and motion which also facilitates partial matching.
+The method always returns defect free solutions as it is inherently taken care of.
+Sensitivity analysis indicates that complexity of the objective function, although obviously multimodal and nonlinear, is not overly complex and certainly well behaved in the singular spaces.
+Hierarchically cluster database provides efficient query search.
+Finally effectiveness of the method is showcased by a case study for which nine defect free solutions were found in contrast to zero solutions by our algebraic fitting based precision point method.
+Although our method can provide highly accurate results, our focus is to generate high number of defect free solutions for the task in more or less similar fashion.
+Because more often than not, linkage synthesis algorithms are desired to be prolific in terms of concept generation than to produce highly accurate very few solutions.
 

### 2018-03-07 idetc2018.tex
Bug fixes

@@
 
-Original contribution of this paper are in 1) a novel objective function for defect-free motion generation problem, 2) discovering a representation of coupler motion and path which is invariant under similarity transformations (henceforth termed as motion signature and path signature respectively.), 3) novel algorithm for partial matching of motions , 3) optimal storage by means of auto-encoder neural network and efficient neighbor search in the clustered database.
+Original contribution of this paper are in 1) a novel objective function for defect-free motion generation problem, 2) discovering a representation of coupler motion and path which is invariant under similarity transformations (henceforth termed as motion signature and path signature respectively.), 3) novel algorithm for partial matching of motions , 4) optimal storage by means of auto-encoder neural network and efficient neighbor search in the clustered database.
 The objective function that drives the synthesis process computes a distance measure of dissimilarity between the task motion and the coupler motion generated by current linkage parameters.
@@
 \begin{equation}\label{objectiveFunMotion}
-  \argminA_{\textbf{\emph{l}}, W_i} (E_{min}(p, W_i)
+  \argminA_{\textbf{\emph{l}}, W_i} (E_{min}(p, W_i))
 \end{equation}
@@
 We can employ global optimization methods such as differential evolution at the start and local optimization methods link Powell's method towards the end for faster convergence\cite{ullah1997}.
-Section~\ref{examples} presents results for the optimization technique used.
+%Section~\ref{examples} presents results for the optimization technique used.
 
@@
 Once a network is trained, Output of the bottle-neck layer $(h_{ib})$ represents the compressed feature space ($Z$).
-It can be seen that input information is compressed by a factor of 10, while achieving $95\%$ reconstruction accuracy.
-Standard clustering algorithms are performed on this latent space for better clustering\cite{song2013}.
+As the bottleneck layer has 10 neurons and input is 100 dimensional vector, it is evident that information is compressed by a factor of 10, while achieving $95\%$ reconstruction accuracy.
+Standard clustering algorithms are performed on this latent\footnote{compressed output of bottleneck layer.} space for better clustering\cite{song2013}.
 We use Agglomerative Clustering, a method of Hierarchical clustering, which is an approach to partitioning clustering for identifying groups in the dataset.
@@
 Figures~\ref{knnSol1} to \ref{knnSol7} depict the solutions obtained after scaling and orienting the linkage to match required motion.
-Although all of these linkages satisfactorily perform the input task with any defect, linkages in Fig.~\ref{knnsol1}, \ref{knnsol2}, \ref{knnsol3}, \ref{knnsol7} are suitable for the task considering the pivot locations.
+Although all of these linkages satisfactorily perform the input task with any defect, linkages except Fig.~\ref{knnSol4}, \ref{knnSol5}, \ref{knnSol6} are suitable for the task considering the pivot locations.
 Nevertheless this approach produces a large variety of solutions which otherwise would have been very hard to found using precision point approach.
@@
 \centering
-\includegraphics[width=240pt]{figure/sol7.eps}
+\includegraphics[width=240pt]{figure/sol8.eps}
   \caption{Eighth Linkage in the table~\ref{knnLinkageData} and its resultant motion.}
@@
 \centering
-\includegraphics[width=240pt]{figure/sol7.eps}
-  \caption{Eighth Linkage in the table~\ref{knnLinkageData} and its resultant motion.}
+\includegraphics[width=240pt]{figure/sol9.eps}
+  \caption{Ninth Linkage in the table~\ref{knnLinkageData} and its resultant motion.}
 \label{knnSol9}

### 2018-03-10 idetc2018.tex
Added second example

@@
 \newcommand{\expo}[1]{exp$({\bf {#1}})$}
+
+% Subfigure plot
+\makeatletter
+\newcommand{\putindeepbox}[2][0.7\baselineskip]{{%
+    \setbox0=\hbox{#2}%
+    \setbox0=\vbox{\noindent\hsize=\wd0\unhbox0}
+    \@tempdima=\dp0
+    \advance\@tempdima by \ht0
+    \advance\@tempdima by -#1\relax
+    \dp0=\@tempdima
+    \ht0=#1\relax
+    \box0
+}}
+\makeatother
 
@@
 
-\section{Examples}\label{sec_example}
-This sections presents a case study presenting the effectiveness of our approach.
+\section{Case Studies}\label{sec_example}
+This sections presents two case studies presenting the effectiveness of our approach in path and motion synthesis respectively.
+\subsection{Path Generation}
+In the design phase of a rehabilitation device that assists people during sit-to-stand motion, it is required to generate linkages that can execute a sit-to-stand (STS) trajectory of hip as shown in Fig.~\ref{ex1_path}.
+Table~\ref{hipPathTab} presents the discretized path data.
+As our approach requires parametric representation of path, we first fit a cubic B-Spline with cord length parameterization through path data points to generate parametric curve shown in Fig.~\ref{ex1_path}.
+We compute its path signature by the steps mentioned in Algorithm ~\ref{alg_signature} and raise the query for nearest neighbors among 1500 cluster centers of our database.
+The distance metric for finding neighbors is $1-Cn_{max}$ in ~\req{objectiveFunPath}.
+Table~\ref{ex1_knnLinkageData} tabulates the link ratios corresponding to obtained nine nearest neighbors.
+Next step is compute actual parameters according to position, scale and orientation of the path.
+It is done by comparing analogous points found by offset index $j$ in eq.~\ref{nccEq}.
+Figure ~\ref{ex1_solns} shows first eight fourbar mechanisms corresponding to nearest signatures to path signature of input.
+As it can be clearly seen these linkages generate highly accurate paths without any defects throughout sit to stand activity.
+
+\begin{table}
+\caption{Case Study 1 : Path Data}
+\centering
+\label{hipPathTab}
+\begin{tabular}{cccccc}
+\hline
+Point & x & y & Point & x & y \\
+\hline
+1 & -7.81 & -9.65 & 10 & 0.28 & -1.31 \\
+2 & -6.42 & -9.81 & 11 & 0.64 & 1.07 \\
+3 & -5.14 & -9.62 & 12 & 0.98 & 2.73 \\
+4 & -3.72 & -8.99 & 13 & 1.47 & 4.30 \\
+5 & -2.62 & -8.14 & 14 & 2.73 & 6.58 \\
+6 & -1.75 & -7.13 & 15 & 3.46 & 7.41 \\
+7 & -0.91 & -5.67 & 16 & 4.07 & 7.95 \\
+8 & -0.32 & -4.10 & 17 & 4.70 & 8.41 \\
+9 & -0.02 & -2.92 & 18 & 5.32 & 8.76 \\
+\end{tabular}
+\end{table}
+
+\begin{table}
+\caption{Linkage Parameters of Nine Nearest Neighbor Paths}
+\centering
+\label{ex1_knnLinkageData}
+\begin{tabular}{ccccccc}
+\hline
+  linkage & $l_1$ & $l_2$ & $l_3$ & $l_4$ & $l_5$ & $1 - Cn_{max}$ \\
+\hline
+ 1 & 0.79 & 2.78 & 1.70 & 1.35 & -0.71 & 0.0011 \\
+ 2 & 1.59 & 1.28 & 0.96 & -1.74 & -1.13 & 0.0015\\
+ 3 & 0.99 & 0.71 & 1.66 & -1.07 & -0.85 & 0.0016\\
+ 4 & 0.51 & 0.48 & 1.11 & -0.02 & -0.15 & 0.0017\\
+ 5 & 0.93 & 0.75 & 2.18 & -1.65 & 0.96 & 0.0018 \\
+ 6 & 1.29 & 1.98 & 1.02 & -1.83 & -1.33 & 0.0019\\
+ 7 & 0.63 & 1.42 & 1.03 & -1.90 & -0.38 & 0.0020\\
+ 8 & 0.66 & 0.85 & 0.84 & -1.40 & -0.13 & 0.0021\\
+ 9 & 1.81 & 0.55 & 1.08 & 0.14 & -0.04 & 0.0022
+\end{tabular}
+\end{table}
+
+\begin{figure}
+\centering
+\includegraphics[width=240pt]{figure/path_solutions/hip_path.eps}
+  \caption{Case Study 1: Path traced by hip joint during Sit-to-Stand Motion.}
+\label{ex1_path}
+\end{figure}
+
+\begin{figure}
+\begin{tabular}{cc}
+  1)\putindeepbox[7pt]{\includegraphics[width=100pt]{figure/path_solutions/path_sol1.eps}}
+    & 2)\putindeepbox[7pt]{\includegraphics[width=60pt]{figure/path_solutions/path_sol2.eps}} \\
+  3)\putindeepbox[7pt]{\includegraphics[width=120pt]{figure/path_solutions/path_sol3.eps}}
+    & 4)\putindeepbox[7pt]{\includegraphics[width=120pt]{figure/path_solutions/path_sol4.eps}}\\
+  5)\putindeepbox[7pt]{\includegraphics[width=120pt]{figure/path_solutions/path_sol5.eps}}
+    & 6)\putindeepbox[7pt]{\includegraphics[width=120pt]{figure/path_solutions/path_sol6.eps}} \\
+  7)\putindeepbox[7pt]{\includegraphics[width=120pt]{figure/path_solutions/path_sol7.eps}}
+    & 8)\putindeepbox[7pt]{\includegraphics[width=120pt]{figure/path_solutions/path_sol8.eps}}\\
+\end{tabular}
+\caption{First 8 Linkages in the table~\ref{knnLinkageData} and their resultant coupler motions.}
+\label{ex1_solns}
+\end{figure}
+
+\subsection{Motion Generation}
 The task is to find a pool of linkage systems that can perform snow-shoveling with a motion shown in Fig.~\ref{motionQuery}.
-The motion data is tabulated in Table ~\ref{poseData} which we fit into a B-spline with arc-length parameterization.
+The motion data is tabulated in Table ~\ref{poseData} which we fit into a B-spline with cord length parameterization.
 The task can be treated as a finite position motion generation and solved for valid solutions.
-We try with our real time computational methods of algebraic fitting\cite{generalfitting-JCISE},\cite{deshpande2017} but the solutions obtained suffer from circuit defect.
+We try with our real time computational methods of algebraic fitting\cite{generalfitting-JCISE},\cite{deshpande2017} but obtained solutions suffer from circuit defect, which is not a surprise as those methods do not account for continuity of the input positions.
+
 Now we employ the approach presented in this paper.
-First step is to calculate motion signature of the task motion.
+First step is to calculate motion signature of the task motion using steps mentioned in Algorithm ~\ref{alg_signature}.
 For that we follow the steps given in section~\ref{sec_sign} to obtain the motion signature depicted in Fig.~\ref{queryResult}.
@@
 Actual scaling and orientation of the linkage can be found out easily by comparing analogous points which are given by the offset index $j$ that corresponds to minimum distance$(E_min)$ in eq.~\req{mccEq}.
-Figures~\ref{knnSol1} to \ref{knnSol7} depict the solutions obtained after scaling and orienting the linkage to match required motion.
-Although all of these linkages satisfactorily perform the input task with any defect, linkages except Fig.~\ref{knnSol4}, \ref{knnSol5}, \ref{knnSol6} are suitable for the task considering the pivot locations.
+Figure~\ref{ex2_solns} depict the solutions obtained after scaling and orienting the linkage to match required motion.
+Although all of these linkages satisfactorily perform the input task with any defect, linkages except Fig.~\ref{knnSol4} are suitable for the task considering the pivot locations.
 Nevertheless this approach produces a large variety of solutions which otherwise would have been very hard to found using precision point approach.
@@
 \includegraphics[width=240pt]{figure/fig_motion_query.eps}
-  \caption{Motion Query : Task Motion drawn specified by user.}
+  \caption{Case Study 2: Task Motion drawn specified by user.}
 \label{motionQuery}
@@
 \includegraphics[width=240pt]{figure/fig_ex_motion_signatures.eps}
-  \caption{Query Result: Motion signatures in the dataset with highest similarity.}
+  \caption{Case Study 2 - Query Result: Motion signatures in the dataset with highest similarity.}
 \label{queryResult}
@@
 \begin{table}
-\caption{Example : Pose Data}
+\caption{Case Study 2: Pose Data}
 \centering
 \label{poseData}
-\begin{tabular}{cccc}
+\begin{tabular}{cccccccc}
 \hline
-Pose & x & y & $\theta$ \\
+%Pose & x & y & $\theta$ \\
+Pose & x & y & $\theta$ & Pose & x & y & $\theta$ \\
 \hline
-1 & 0.03 & 0.07 & 6.06 \\
-2 & 0.38 & 0.01 & 6.18 \\
-3 & 0.71 &-0.00 & 0.04 \\
-4 & 1.02 & 0.06 & 0.22 \\
-5 & 1.26 & 0.22 & 0.46 \\
-6 & 1.39 & 0.47 & 0.73 \\
-7 & 1.36 & 0.77 & 1.03 \\
-8 & 1.18 & 1.06 & 1.36 \\
-9 & 0.88 & 1.27 & 1.74 \\
+1 & 0.03 & 0.07 & 6.06 & 6 & 1.39 & 0.47 & 0.73 \\
+2 & 0.38 & 0.01 & 6.18 & 7 & 1.36 & 0.77 & 1.03 \\
+3 & 0.71 &-0.00 & 0.04 & 8 & 1.18 & 1.06 & 1.36 \\
+4 & 1.02 & 0.06 & 0.22 & 9 & 0.88 & 1.27 & 1.74 \\
+5 & 1.26 & 0.22 & 0.46 & \\
 \end{tabular}
@@
 \begin{table}
-\caption{Linkage Parameters of Five Nearest Neighbor Motions}
+\caption{Case Study 2: Linkage Parameters corresponding to Nine Nearest Neighbor Motions}
 \centering
-\label{knnLinkageData}
+\label{ex2_knnLinkageData}
 \begin{tabular}{ccccccc}
 \hline
-  linkage & $l_1$ & $l_2$ & $l_3$ & $l_4$ & $l_5$ & $f_{obj}$ \\
+  linkage & $l_1$ & $l_2$ & $l_3$ & $l_4$ & $l_5$ & $E_{min}$ \\
 \hline
@@
 \begin{figure}
-\centering
-\includegraphics[width=240pt]{figure/sol1.eps}
-  \caption{First Linkage in the table~\ref{knnLinkageData} and its resultant motion.}
-\label{knnSol1}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=240pt]{figure/sol2.eps}
-  \caption{Second Linkage in the table~\ref{knnLinkageData} and its resultant motion.}
-\label{knnSol2}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=240pt]{figure/sol3.eps}
-  \caption{Third Linkage in the table~\ref{knnLinkageData} and its resultant motion.}
-\label{knnSol3}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=240pt]{figure/sol4.eps}
-  \caption{Fourth Linkage in the table~\ref{knnLinkageData} and its resultant motion.}
-\label{knnSol4}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=200pt]{figure/sol5.eps}
-  \caption{Fifth Linkage in the table~\ref{knnLinkageData} and its resultant motion.}
-\label{knnSol5}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=240pt]{figure/sol6.eps}
-  \caption{Sixth Linkage in the table~\ref{knnLinkageData} and its resultant motion.}
-\label{knnSol6}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=240pt]{figure/sol7.eps}
-  \caption{Seventh Linkage in the table~\ref{knnLinkageData} and its resultant motion.}
-\label{knnSol7}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=240pt]{figure/sol8.eps}
-  \caption{Eighth Linkage in the table~\ref{knnLinkageData} and its resultant motion.}
-\label{knnSol8}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=240pt]{figure/sol9.eps}
-  \caption{Ninth Linkage in the table~\ref{knnLinkageData} and its resultant motion.}
-\label{knnSol9}
+\begin{tabular}{cc}
+  1)\putindeepbox[2pt]{\includegraphics[width=120pt]{figure/sol1.eps}}
+    & 2)\putindeepbox[2pt]{\includegraphics[width=120pt]{figure/sol2.eps}} \\
+  3)\putindeepbox[2pt]{\includegraphics[width=120pt]{figure/sol3.eps}}
+    & 4)\putindeepbox[2pt]{\includegraphics[width=120pt]{figure/sol4.eps}}\\
+  5)\putindeepbox[2pt]{\includegraphics[width=120pt]{figure/sol6.eps}}
+    & 6)\putindeepbox[2pt]{\includegraphics[width=120pt]{figure/sol7.eps}} \\
+  7)\putindeepbox[2pt]{\includegraphics[width=120pt]{figure/sol8.eps}}
+    & 8)\putindeepbox[2pt]{\includegraphics[width=120pt]{figure/sol9.eps}}\\
+\end{tabular}
+\caption{Case Study 2: First 8 Linkages in the table~\ref{ex2_knnLinkageData} and their resultant coupler motions.}
+\label{ex2_solns}
 \end{figure}

### 2018-03-10 idetc2018.tex
added overall layout figure

@@
 %%% Replace here with information related to your conference
-\confshortname{IDETC/CIE 2017}
-\conffullname{the ASME 2017 International Design Engineering Technical Conferences \&\\
+\confshortname{IDETC/CIE 2018}
+\conffullname{the ASME 2018 International Design Engineering Technical Conferences \&\\
               Computers and Information in Engineering Conference}
@@
 %%%%% for date across two months, use
-\confyear{2017}
+\confyear{2018}
 \confcity{Quebec City}
@@
 %%% by ASME for your paper.
-\papernum{DRAFT: DETC2017-TBD}
+\papernum{DRAFT: DETC2018-TBD}
 
@@
 
+\begin{figure*}
+\centering
+\includegraphics[width=\textwidth]{figure/overall_approach.eps}
+  \caption{General Layout of the approach.}
+\label{overallMethod}
+\end{figure*}
+
 The motion and path generation problems are exhaustively researched topics.
@@
 
-Original contribution of this paper are in 1) a novel objective function for defect-free motion generation problem, 2) discovering a representation of coupler motion and path which is invariant under similarity transformations (henceforth termed as motion signature and path signature respectively.), 3) novel algorithm for partial matching of motions , 4) optimal storage by means of auto-encoder neural network and efficient neighbor search in the clustered database.
+Original contribution of this paper are in 1) a novel objective function for defect-free motion generation problem, 2) discovering a representation of coupler motion and path which is invariant under similarity transformations (henceforth termed as motion signature and path signature respectively), 3) novel algorithm for partial matching of motions , 4) optimal storage by means of auto-encoder neural network and efficient neighbor search in the clustered database.
 The objective function that drives the synthesis process computes a distance measure of dissimilarity between the task motion and the coupler motion generated by current linkage parameters.
@@
 These k neighbors if needed, are subjected to fine tuning by local optimization to obtain set of solutions.
-Overall method is presented in algorithm~\ref{alg_overall}.
+Overall method is given in algorithm~\ref{alg_overall} and depicted in Fig.~\ref{overallMethod}.
 
@@
     \Output{signature //discretized signal in form of an array}
-    k(t) = ComputeCurvature(x, y) using eq.~\ref{computeCurvature} \\
+    k(t) = ComputeCurvature(x, y) using eq.~\ref{curvatureEq} \\
     K(t) = IntergrateCumulatively(k) using eq.~\ref{kInt} \\
@@
 \begin{eqnarray}
-  k(t) = \frac{\ddot{y}(t)\dot{x}(t) - \ddot{x}(t)\dot{y}(t)}{{(\dot{x}^2(t) + \dot{y}^2(t))}^{(\frac 32)}} \label{curvature}\\
+  k(t) = \frac{\ddot{y}(t)\dot{x}(t) - \ddot{x}(t)\dot{y}(t)}{{(\dot{x}^2(t) + \dot{y}^2(t))}^{(\frac 32)}} \label{curvatureEq}\\
   K(t) = \int^{t}_0 |k(t)| \label{kInt},
@@
 This subsection presents a method for determining this partial similarity.
-Let $p$ be motion signature of such a part path which acts as template while $W$ is the motion signature corresponding to a path (Whole) that can completely embed the template as shown in Fig.~\ref{wholePart}.
+Lets consider two coupler paths as shown in~\ref{wholePart}.
+Let $p$ be path signature of such a part path which acts as template while $W$ is the path signature corresponding to a path (Whole) that can completely embed the template as shown in Fig.~\ref{pathSignature}.
 The orientation information shown in Fig.~\ref{wholePart} is ignored for path matching.
@@
 \includegraphics[width=240pt]{figure/fig_path_signatures.eps}
-  \caption{The domain of path signature is scale invariant but the range still has a scaling factor, which is taken by normalized cross-correlation.}
+  \caption{Path Signatures of part $p$ and whole $W$ from Fig.~\ref{wholePart}.The domain of path signature is scale invariant but the range still has a scaling factor, which is taken care by normalized cross-correlation.}
 \label{pathSignature}

### 2018-03-10 idetc2018.tex
full Read 1, bug fixes

@@
 However, majority of the methods formulate it as Precision Position problem (or Classical Burmester Problem) which inherently ignores the continuity information.
-Which, in turn results into solution linkages with branch and circuit defects.
+Which, in turn results into solution linkages with branch, circuit and order defects.
 In this paper, we present a novel approach that addresses this issue into problem formulation and returns solutions free from defects.
 At the heart of this approach lies an objective function that compares the motion as a whole; thus, capturing designer's intent.
-In contrast to widely used structural error or loop closer equation based error functions which convolute the optimization by considering shape, size, position and orientation simultaneously, this objective function computes motion difference in the form that is invariant to similarity transformations.
+In contrast to widely used structural error or loop-closer equation based error functions which convolute the optimization by considering shape, size, position and orientation simultaneously, this objective function computes motion difference in a form invariant to similarity transformations.
 Actual scale, position and orientation of linkage components are obtained by subsequent trivial fitting.
@@
   The query is raised in the database for k nearest neighbors, which are either solutions or good initial conditions for fast local optimization techniques.
-We also employ global optimizing techniques without any initial guess.
-In spite of highly non-linear parameters space our approach discovers a wide pool of defect free solutions.
+In spite of highly non-linear parameters space, our approach discovers a wide pool of defect free solutions.
 \end{abstract}
@@
 \section{Introduction}
-In spite of increasing applications of electronically controlled manipulators, single degree freedom mechanical linkages will still important.
-This is justified by new areas of application opened by technologies like nanotechnology, bio-mechatronics.
-Therefore mechanisms theory will retain its position in the research community.
 Classic mechanism synthesis problem deals with computing type and dimensions of linkage system for performing specific tasks, which are categorized as path, motion and function generation.
@@
 The majority of these theories don't account for circuit and branch defect in the synthesis process, which can render the solution useless for practical applications.
-These defects in single DOF mechanisms are thoroughly discussed in Chase and Mirth\cite{chasemirth}.
+These defects in single DOF mechanisms are thoroughly discussed by Chase and Mirth\cite{chasemirth}.
 
@@
 The objective function that drives the synthesis process computes a distance measure of dissimilarity between the task motion and the coupler motion generated by current linkage parameters.
-In contrast to precision point method where distance measure is in terms of interpolation error, the distance measure of dissimilarity is valid between two planar curves or motions.
-Which inherently requires the continuity of output; ensuring the output mechanism defect free throughout the task.
+The distance measure of dissimilarity inherently requires continuity of motion; ensuring the output mechanism is defect free throughout the task.
 
@@
 In the case of motion generation, methods that take the branching defect into consideration limit their search into configuration space where Grashof condition holds true.
-To the authors' best knowledge, None of the method truly take motion continuity into account.
+To the authors' best knowledge, no other method truly take the motion continuity into account.
 
-Owing to the highly nonlinear nature of the problem, most of the optimization based methods require good initial condition to start.
+Owing to the highly nonlinear nature of the problem, most optimization based methods require good initial condition to start.
 Thus, an atlas or a design library is used to provide good initial conditions.
-McGarva\cite{mcgarva1994} have taken the earliest approach towards creating a library for coupler trajectories based on harmonic analysis.
+McGarva\cite{mcgarva1994} has taken the earliest approach towards creating a library for coupler trajectories based on harmonic analysis.
 Wandling\cite{wandling2000} has presented an atlas based approach where, coupler paths and motions are stored in terms of Fourier Transforms.
@@
 The best match is returned as solution to input.
-Chu et al.\cite{chu2010} showcase an atlas based method of synthesizing spatial fourbar linkage for function generation problem where orientation data is stored in terms of Fourier harmonics.
+Chu et al.\cite{chu2010} have showcased an atlas based method of synthesizing spatial fourbar linkage for function generation problem where orientation data is stored in terms of Fourier harmonics.
 
 The above methods generate data based on uniform sampling in the linkage parameter space.
-Given the highly nonlinear mapping between linkage parameters and coupler trajectory, this way of sampling leads to highly non-uniform sampling of trajectory space resulting in to data misrepresentation.
+Given the highly nonlinear mapping between linkage parameters and coupler trajectory, this way of sampling leads into non-uniform sampling of trajectory space which causes under-representation of possible motions.
 We try to address this issue by employing log normal distribution in the linkage parameter space and clustering the generated data.
-The above methods have their library consists of all possible coupler curves, where one curve is broken down into many segments for creating data for partial curves.
-In contrast to this, we need store only one curve because our curve representation facilitates partial matching.
-Neither of the methods facilitate this partial matching of open motion curve into another open or closed curve.
+Also other methods have their library consists of all possible coupler curves, where one curve is broken down into many segments for creating data for partial curves.
+In contrast to this, we need to store only one curve because our curve representation facilitates partial matching.
+No other previous method facilitates this partial matching of open motion curve into another open or closed curve.
 Thus reducing the data requirement even further.
@@
 A Hierarchy is created in the database by means of clustering, where top level comprises of few data points called cluster centers which are representative of the cluster points in the lower levels.
-When a inputs a motion or a path, a query representing invariant signature \footnote{path or motion signature} of the input is raised for k nearest neighbors among cluster centers in the database.
+When a user inputs a motion or a path, a query representing invariant signature \footnote{path or motion signature} of the input is raised for k nearest neighbors among cluster centers in the database.
 The neighbor is defined as motion or path whose part has a similar signature to the input.
@@
 Section~\ref{sec_distanceMetric} is comprised of evaluation criterion for two signatures based on the shape similarity, which leads to form the error function for optimization.
-Section~\ref{sec_SA} discusses the nature of objective function via sensitivity analysis at a singular point.
+Section~\ref{sec_SA} discusses the nature of objective function via sensitivity analysis at a singularity.
 Section~\ref{sec_db_ae} explains the database generation and clustering using auto-encoders for efficient sampling and query operations.
-Finally, an case study is presented~\ref{sec_example} to showcase the efficacy of the method.
+Finally, a case study is presented~\ref{sec_example} to showcase the efficacy of the method.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-Curvature of the path of a parametric motion $(x:x(t), y:y(t), \theta:\theta(t))$ given by,
+Curvature $k(t)$ of the path of a parametric motion $(x:x(t), y:y(t), \theta:\theta(t))$ and its integral $K(t)$ is given by,
 \begin{eqnarray}
   k(t) = \frac{\ddot{y}(t)\dot{x}(t) - \ddot{x}(t)\dot{y}(t)}{{(\dot{x}^2(t) + \dot{y}^2(t))}^{(\frac 32)}} \label{curvatureEq}\\
-  K(t) = \int^{t}_0 |k(t)| \label{kInt},
+  K(t) = \int^{t}_0 |k(t)|dt \label{kInt},
 \end{eqnarray}
@@
 For an example, parametric motion could be a B-spline motion as shown in fig~\ref{bsplineFitting}.
-We compute the curvature of path along the direction of t, using eq.~\ref{curvature} and the cumulative integral by eq.~\ref{kInt}.
+We compute the curvature of path along the direction of t, using eq.~\ref{curvatureEq} and the cumulative integral by eq.~\ref{kInt}.
 For implementation purposes, we use scipy\cite{scipy} module for computations of B-splines and their derivatives.
@@
 These signatures are invariant under similarity transformations; for proof see\cite{cui2009}.
-Since we know that curvature changes inversely to the scale of the curve, when integrate along the scaled curve the scale factor cancels itself out.
+The general intuition is as follows:
+we know that curvature changes inversely to the scale of the curve, so when it is integrated along the scaled curve the scale factor cancels itself out.
 Reflection operation on the motion or the path, produces flipped path signature, but motion signature remains invariant.
@@
 This subsection presents a method for determining this partial similarity.
-Lets consider two coupler paths as shown in~\ref{wholePart}.
-Let $p$ be path signature of such a part path which acts as template while $W$ is the path signature corresponding to a path (Whole) that can completely embed the template as shown in Fig.~\ref{pathSignature}.
-The orientation information shown in Fig.~\ref{wholePart} is ignored for path matching.
+
+Lets consider two coupler paths; namely part and whole as shown in~\ref{wholePart}.
+Let $p$ be path signature of the part path which acts as template, while $W$ is path signature of the whole path that can completely embed the template as shown in Fig.~\ref{pathSignature}.
+The orientation information shown in Fig.~\ref{wholePart}, is ignored for path matching.
 It will be used later for matching of motion signature.
@@
 \begin{enumerate}
-  \item As $p$ and $W$ are expressed in terms of arrays where each $i^{th}$ entry in the array corresponds to $K = 0.01\times i$, $W$ must contain more points than $p$.
-  \item The template $p$ is slid with offset index $j$ along with $W$.
+  \item $p$ and $W$ are expressed in terms of arrays and $W$ must contain more points than $p$.
+  \item The template $p$ is slid with offset index $j$ along $W$.
   \item For each offset $j$, we compute normalized cross-correlation function given by,
@@
 As the signature reverses with reversal of the direction of sampling, we compute the correlation once in a normal way and again after reversing $p$ and select the best matching score, offset index and the matching direction of sampling.
-Figure~\ref{ncc} depicts normalized cross correlation function over the sliding domain $j$ for two curves shown in Fig.~\ref{wholePart} where the second curve is a part of first curve modified by scaling and translation.
+Figure~\ref{ncc} depicts normalized cross correlation function over the sliding domain $j$ for part and whole curves.
 
@@
 \subsection{Partial Matching of Motion Signatures}\label{sec_mcc}
-This section presents how a template $p$ motion can be checked against motion with signature $W$ for potential matching.
+This section presents how a template motion can be checked against other motion for potential matching.
+Consider part and whole motions shown in Fig.~\ref{wholePart}.
+Let $p$ and $W$ be the motion signatures of part and whole motions respectively.
 All the steps are same as done for partial matching of path signature except the cross-correlation function which is given by,
@@
 $E_{min}(p, W)$.
-Figure~\ref{mcc} depicts dissimilarity function over the sliding domain $j$ for two curves shown in Fig.~\ref{wholePart}.
-In the case shown in example~\ref{mcc}, we find that first point itself is start point where the perfect match is occurred which is consistent with the fact that we slice the motion in similar manner.
+Figure~\ref{mcc} depicts dissimilarity function over the sliding domain $j$.
+In this case as shown in Fig.~\ref{mcc}, we find that the first point itself is a point where the perfect match is occurred which is consistent with the fact that we slice the motion in similar manner.
 
@@
 
-Similarly, we can formulate motion synthesis as,
+Similarly, we can formulate motion synthesis problem as,
 \begin{equation}\label{objectiveFunMotion}
@@
 Considering highly non-linear nature of the problem, finding a good initial guess proves to be game changing.
-Thus we exploit the advantages of data driven approach for finding many good initial guesses or if get lucky, the solution itself.
+Thus we exploit the advantages of data driven approach for finding many good initial guesses or the solution itself.
 
@@
 A four-bar with link ratios ($l_1:0.55$, $l_2:1$, $l_3:1.5$, $l_4:1$, $l_5:1$) is subjected to gradual change in parameters $l_1$ and $l_3$ by the amount (-0.2, 0.2) in steps of 0.01.
-Error functions for motion using eq.~\req{objectiveFunMotion} are calculated between new and initial fourbar.
+Error function between motions of new and initial fourbar are calculated using eq.~\req{objectiveFunMotion} .
 Figure~\ref{saCouplerCurves} shows coupler motion of some of the four-bars while Fig.~\ref{saMotionSignatures} depicts their motion signatures.
@@
   \caption{Distance ($E_{min}$) from eq.~\req{mccEq} as the parameters $l_1$ and $l_2$ are varied.
-Although open loop breaks between $l_1$:(0.5, 0.6), $l_3$:1.5 parameter values, there are no spikes in the error function as the shape is very similar between the two topologies.}
+Although open loop breaks at $l_1$:0.55, $l_3$:1.5, there are no spikes of error function in the region near singularity, as the shape is very similar between the two topologies.}
 \label{saErrorFunction}
@@
 As mapping between four-bar linkage parameter space and coupler motion space is highly non-linear, uniform distribution over linkage parameter space doesn't necessarily mean uniform sampling over motion space.
-Thus the efficient approach would be to sample more in the locations where sensitivity is maximum.
+Thus the efficient approach would be to sample more in the regions where sensitivity is maximum.
 Our observational intuition tells that whenever the link ratios of four-bar linkage are close to 1, the sensitivity of the shape of a coupler motion is higher than otherwise.
-Thus we chose Log-Normal Distribution ($\mu = 0,\sigma = 0.6 $) for the range of link ratios : $(l_1, l_2, l_3)$ as shown in Fig.~\ref{logNormal}, and Normal Distribution ($\mu = 0,\sigma = 2 $) for $(l_4, l_5)$.
+Thus we have chosen Log-Normal probalitiy distribution ($\mu = 0,\sigma = 0.6 $) for selecting the link ratios : $(l_1, l_2, l_3)$ as shown in Fig.~\ref{logNormal}, and Normal Distribution ($\mu = 0,\sigma = 2 $) for $(l_4, l_5)$.
 
@@
 This Non-linear mapping by auto-encoder can greatly improve the representation of data for clustering (For details refer \cite{song2013}).
-Figure~\ref{autoEncoder} shows an architecture similar to the Neural Network we designed for the task.
-Number of neurons per layer are (100, 80, 50, 10, 50, 80, 100).
+Figure~\ref{autoEncoder} shows a Neural Network architecture similar to the one we designed for the task.
+Our architecture consists of 100 neurons in input and output layer, while five hidden layers have (80, 50, 10, 50, 80) neurons respectively.
 Each neuron in the hidden layer is activated by Rectified Linear Unit (\emph{ReLU}) activation function.
@@
 Once a network is trained, Output of the bottle-neck layer $(h_{ib})$ represents the compressed feature space ($Z$).
-As the bottleneck layer has 10 neurons and input is 100 dimensional vector, it is evident that information is compressed by a factor of 10, while achieving $95\%$ reconstruction accuracy.
+As the bottleneck layer has 10 neurons and input is 100 dimensional vector, it is evident that information is compressed by a factor of 10, while achieving $95\%$ reconstruction accuracy as a result of training.
 Standard clustering algorithms are performed on this latent\footnote{compressed output of bottleneck layer.} space for better clustering\cite{song2013}.
@@
 \section{Case Studies}\label{sec_example}
-This sections presents two case studies presenting the effectiveness of our approach in path and motion synthesis respectively.
+This sections presents two case studies presenting the effectiveness of our approach for path and motion synthesis applications.
 \subsection{Path Generation}
-In the design phase of a rehabilitation device that assists people during sit-to-stand motion, it is required to generate linkages that can execute a sit-to-stand (STS) trajectory of hip as shown in Fig.~\ref{ex1_path}.
+In the design phase of a rehabilitation device that assists people stand from sitting position, it is required to generate linkages that can execute a sit-to-stand (STS) trajectory of hip as shown in Fig.~\ref{ex1_path}.
 Table~\ref{hipPathTab} presents the discretized path data.
@@
 \end{tabular}
-\caption{First 8 Linkages in the table~\ref{knnLinkageData} and their resultant coupler motions.}
+\caption{First 8 Linkages in the table~\ref{ex1_knnLinkageData} and their resultant coupler paths.}
 \label{ex1_solns}
@@
 The task is to find a pool of linkage systems that can perform snow-shoveling with a motion shown in Fig.~\ref{motionQuery}.
-The motion data is tabulated in Table ~\ref{poseData} which we fit into a B-spline with cord length parameterization.
-The task can be treated as a finite position motion generation and solved for valid solutions.
+The motion data is tabulated in Table ~\ref{poseData} to which we fit into a B-spline with cord length parameterization in order to get parametric representation of motion.
+The task can also be treated as a finite position motion generation and solved for valid solutions.
 We try with our real time computational methods of algebraic fitting\cite{generalfitting-JCISE},\cite{deshpande2017} but obtained solutions suffer from circuit defect, which is not a surprise as those methods do not account for continuity of the input positions.
@@
 Next we raise the signature query for nearest signatures among the cluster centers of the database.
-Fig.\ref{queryResult} shows nine nearest neighbor signatures along with task signature.
-Table ~\ref{knnLinkageData} presents the linkage parameters corresponding to the nearest neighbors along with their distance score from the task.
+Fig.\ref{queryResult} shows nine nearest neighbor signatures along with the task signature.
+Table ~\ref{ex2_knnLinkageData} presents the linkage parameters corresponding to the nearest neighbors along with their distance score from the task.
 Coupler motions of these linkages have a part which matches with the shape of input motion query.
@@
 Figure~\ref{ex2_solns} depict the solutions obtained after scaling and orienting the linkage to match required motion.
-Although all of these linkages satisfactorily perform the input task with any defect, linkages except Fig.~\ref{knnSol4} are suitable for the task considering the pivot locations.
-Nevertheless this approach produces a large variety of solutions which otherwise would have been very hard to found using precision point approach.
+All of these linkages satisfactorily perform the input task without any defect.
+As ground or fixed pivot locations should lie above the ground, all solutions except the $4^{th}$ solution are suitable for the task.
+In light of these results, we can say that this approach produces a large variety of solutions which otherwise would be very hard to find using precision point approach.
 
@@
 \includegraphics[width=240pt]{figure/fig_motion_query.eps}
-  \caption{Case Study 2: Task Motion drawn specified by user.}
+  \caption{Case Study 2: User specified motion necessary for the snow shoveling task.}
 \label{motionQuery}
@@
 Sensitivity analysis indicates that complexity of the objective function, although obviously multimodal and nonlinear, is not overly complex and certainly well behaved in the singular spaces.
-Hierarchically cluster database provides efficient query search.
-Finally effectiveness of the method is showcased by a case study for which nine defect free solutions were found in contrast to zero solutions by our algebraic fitting based precision point method.
-Although our method can provide highly accurate results, our focus is to generate high number of defect free solutions for the task in more or less similar fashion.
+Hierarchically clustered database provides efficient query search.
+Finally, the effectiveness of presented approach is showcased by two case studies for each of which nine defect free solutions were found in contrast to one and zero solutions respectively by our algebraic fitting based precision point method.
+Although our method can provide highly accurate results, our focus here is to generate high number of defect free solutions that can perform the task in more or less similar fashion.
 Because more often than not, linkage synthesis algorithms are desired to be prolific in terms of concept generation than to produce highly accurate very few solutions.

### 2018-03-12 idetc2018.tex
Second Read Bug Fixes

@@
 
-\title{Framework for Unified Optimal Synthesis of Planar Mechanisms for Motion and Path Generation using Shape Optimization}
+\title{Machine Learning-Driven Kinematic Synthesis of Defect-Free Planar Four-Bar Linkages for Motion and Path Generation using Shape Optimization}
 %%% first author
@@
 \begin{abstract}
-% Mechanisms design is generally the earliest phase in a machines design stages.
-
 Success in Synthesis of mechanisms for motion generation refers to computing linkage type and dimensions to perform the task without disassembly.
-However, majority of the methods formulate it as Precision Position problem (or Classical Burmester Problem) which inherently ignores the continuity information.
-Which, in turn results into solution linkages with branch, circuit and order defects.
-In this paper, we present a novel approach that addresses this issue into problem formulation and returns solutions free from defects.
-At the heart of this approach lies an objective function that compares the motion as a whole; thus, capturing designer's intent.
+Majority of the methods formulate it as Precision Position problem (or Classical Burmester Problem) which inherently ignores the continuity information,
+resulting into solution linkages with branch, circuit and order defects.
+In this paper, we present a novel approach that addresses this issue into problem formulation and returns the solutions free from defects.
+At the heart of this approach lies an objective function that compares the motion as a whole, capturing designer's intent.
 In contrast to widely used structural error or loop-closer equation based error functions which convolute the optimization by considering shape, size, position and orientation simultaneously, this objective function computes motion difference in a form invariant to similarity transformations.
@@
 
-The approach starts with creating database of invariant motions of known linkages.
+We employ auto-encoder neural networks to create a compact and clustered database of invariant motions of known linkages.
 The query is raised in the database for k nearest neighbors, which are either solutions or good initial conditions for fast local optimization techniques.
@@
 \section{Introduction}
-Classic mechanism synthesis problem deals with computing type and dimensions of linkage system for performing specific tasks, which are categorized as path, motion and function generation.
-This problem has been dealt with many approaches with the aim of finding acceptable solutions for practical situations.
+Classical mechanism synthesis problem deals with computing type and dimensions of linkage system for performing specific tasks, which are categorized as path, motion and function generation.
+These problems have been dealt with by many approaches with the aim of finding acceptable solutions for practical situations.
+Several text books, such McCarthy and Soh \cite{sohmccarthy}, Sandor and Erdman~\cite{Sandor}, Hunt \cite{Hunt78}, Hartenberg and Denavit \cite{Hartenberg},  Suh and Radcliffe \cite{Suh78}, and Lohse \cite{lohse2013} cover the science and art of planar four-bar and higher-order linkages.
+The majority of these theories don't account for circuit and branch defect in the synthesis process, which can render the solution useless for practical applications.
+These defects in single DOF mechanisms are thoroughly discussed by Chase and Mirth\cite{chasemirth}.
 
@@
 
-The motion and path generation problems are exhaustively researched topics.
-Several text books, such McCarthy and Soh \cite{sohmccarthy}, Sandor and Erdman~\cite{Sandor}, Hunt \cite{Hunt78}, Hartenberg and Denavit \cite{Hartenberg},  Suh and Radcliffe \cite{Suh78}, and Lohse \cite{lohse2013} cover the science and art of planar four-bar and higher-order linkages.
-The majority of these theories don't account for circuit and branch defect in the synthesis process, which can render the solution useless for practical applications.
-These defects in single DOF mechanisms are thoroughly discussed by Chase and Mirth\cite{chasemirth}.
-
-Original contribution of this paper are in 1) a novel objective function for defect-free motion generation problem, 2) discovering a representation of coupler motion and path which is invariant under similarity transformations (henceforth termed as motion signature and path signature respectively), 3) novel algorithm for partial matching of motions , 4) optimal storage by means of auto-encoder neural network and efficient neighbor search in the clustered database.
-The objective function that drives the synthesis process computes a distance measure of dissimilarity between the task motion and the coupler motion generated by current linkage parameters.
-The distance measure of dissimilarity inherently requires continuity of motion; ensuring the output mechanism is defect free throughout the task.
+Original contribution of this paper are in 1) a novel objective function for defect-free motion generation problem, 2) discovering a representation of coupler motion and path which is invariant under similarity transformations (henceforth termed as motion signature and path signature respectively), 3) novel algorithm for partial matching of motions , 4) optimal storage data by means of auto-encoder neural network and efficient neighbor search in the clustered database.
+The objective function that drives the synthesis process, computes a distance measure of dissimilarity between the task motion and the coupler motion generated by current linkage parameters.
+This distance measure of dissimilarity inherently requires continuity of motion; ensuring the output mechanism is defect free throughout the task.
 
@@
 Wu et al.\cite{wu2011} presented a synthesis method for path generation based on finite Fourier series for synthesis of open and closed paths.
-In the case of motion generation, methods that take the branching defect into consideration limit their search into configuration space where Grashof condition holds true.
-To the authors' best knowledge, no other method truly take the motion continuity into account.
+In the case of motion generation, methods that take the branching defect into consideration, limit their search in the configuration space where Grashof condition holds true.
+To our best knowledge, no other motion generation method truly takes the motion continuity into account.
 
@@
 McGarva\cite{mcgarva1994} has taken the earliest approach towards creating a library for coupler trajectories based on harmonic analysis.
-Wandling\cite{wandling2000} has presented an atlas based approach where, coupler paths and motions are stored in terms of Fourier Transforms.
+Wandling\cite{wandling2000} has presented an atlas based approach, where coupler paths and motions are stored in terms of Fourier Transforms.
 Input motion is searched for neighbors based on euclidean distances of Fourier Transforms.
@@
 The above methods generate data based on uniform sampling in the linkage parameter space.
-Given the highly nonlinear mapping between linkage parameters and coupler trajectory, this way of sampling leads into non-uniform sampling of trajectory space which causes under-representation of possible motions.
-We try to address this issue by employing log normal distribution in the linkage parameter space and clustering the generated data.
-Also other methods have their library consists of all possible coupler curves, where one curve is broken down into many segments for creating data for partial curves.
-In contrast to this, we need to store only one curve because our curve representation facilitates partial matching.
+Given the highly nonlinear mapping between linkage parameters and coupler trajectory, this way of sampling leads into non-uniform sampling of trajectory space causing under-representation of possible motions.
+We try to address this issue by employing log normal distribution in the linkage parameter space to generate data and perform compact clustering of the data using machine learning techniques.
+A Hierarchy is created in the database by means of clustering, where the top level comprises of few data points called cluster centers which are representative of the cluster points in the lower levels.
+Also the methods\cite{wandling2000},\cite{yue-pathgen2011} have built the library with all possible coupler curves, where one curve is broken down into many segments for creating data for partial curves.
+In contrast to this, we need to store only one curve representing all the segments in it as our representation facilitates partial matching.
 No other previous method facilitates this partial matching of open motion curve into another open or closed curve.
@@
 
-A Hierarchy is created in the database by means of clustering, where top level comprises of few data points called cluster centers which are representative of the cluster points in the lower levels.
 When a user inputs a motion or a path, a query representing invariant signature \footnote{path or motion signature} of the input is raised for k nearest neighbors among cluster centers in the database.
-The neighbor is defined as motion or path whose part has a similar signature to the input.
-These k neighbors if needed, are subjected to fine tuning by local optimization to obtain set of solutions.
-Overall method is given in algorithm~\ref{alg_overall} and depicted in Fig.~\ref{overallMethod}.
+The neighbor is defined as motion or path whose part has a similar signature to the input. These k neighbors if needed, are subjected to fine tuning by local optimization to obtain set of solutions.
+Overall method depicted in Fig.~\ref{overallMethod} is codified in Algorithm ~\ref{alg_overall}.
 
@@
 Section~\ref{sec_db_ae} explains the database generation and clustering using auto-encoders for efficient sampling and query operations.
-Finally, a case study is presented~\ref{sec_example} to showcase the efficacy of the method.
+Finally, two case studies are presented~\ref{sec_example} to showcase efficacy of the method.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{Signatures of Coupler Path and Motion}\label{sec_sign}
-The main focus of the paper is a novel method for motion generation that takes a continuous task motion as the input and returns defect free linkages producing similar motion.
+The main focus of the paper is a novel method for motion generation that takes a continuous task motion or path as the input and returns defect-free linkages producing similar motion or path.
 The objective function evaluation requires the input motion to be transformed into a specific form, which we call the signature of input motion.
-This signature representation is invariant to similarity operations which are reflection, rotation, translation and scaling.
+This signature representation is invariant to similarity operations, which are reflection, rotation, translation and scaling.
 Signature for path and motion are termed as path signature and motion signature respectively.
@@
     \Output{signature //discretized signal in form of an array}
-    k(t) = ComputeCurvature(x, y) using eq.~\ref{curvatureEq} \\
-    K(t) = IntergrateCumulatively(k) using eq.~\ref{kInt} \\
+    k(t) = ComputeCurvature(x, y) using Eq.~\ref{curvatureEq} \\
+    K(t) = IntergrateCumulatively(k(t)) using Eq.~\ref{kInt} \\
     motionSignature = [] \\
@@
 \begin{eqnarray}
-  k(t) = \frac{\ddot{y}(t)\dot{x}(t) - \ddot{x}(t)\dot{y}(t)}{{(\dot{x}^2(t) + \dot{y}^2(t))}^{(\frac 32)}} \label{curvatureEq}\\
+  k(t) = \frac{\ddot{y}(t)\dot{x}(t) - \ddot{x}(t)\dot{y}(t)}{{(\dot{x}^2(t) + \dot{y}^2(t))}^{(\frac 32)}}, \label{curvatureEq}\\
   K(t) = \int^{t}_0 |k(t)|dt \label{kInt},
@@
 For an example, parametric motion could be a B-spline motion as shown in fig~\ref{bsplineFitting}.
-We compute the curvature of path along the direction of t, using eq.~\ref{curvatureEq} and the cumulative integral by eq.~\ref{kInt}.
+We compute the curvature of path along the direction of t, using Eq.~\ref{curvatureEq} and the cumulative integral by Eq.~\ref{kInt}.
 For implementation purposes, we use scipy\cite{scipy} module for computations of B-splines and their derivatives.
@@
 The general intuition is as follows:
-we know that curvature changes inversely to the scale of the curve, so when it is integrated along the scaled curve the scale factor cancels itself out.
+we know that curvature changes inversely to the scale of the curve, so when it is integrated along the scaled curve, the scale factor cancels itself out.
 Reflection operation on the motion or the path, produces flipped path signature, but motion signature remains invariant.
@@
 \end{equation}
-where $Cn(j, p, W)$ is the normalized cross-correlation value when template $p$ is matched to $W$ at $j^{th}$ index, $p_{span}$ is the length of the array $p$ and $\bar{W}(j\to j + p_{span})$ is the mean for the values of array $W$ between index range of ($j, j+p_{span}$)
+where $Cn(j, p, W)$ is the normalized cross-correlation value when template $p$ is matched against $W$ at $j^{th}$ index, $p_{span}$ is the length of the array $p$ and $\bar{W}(j\to j + p_{span})$ is the mean for the values of array $W$ between index range of ($j, j+p_{span}$)
 
@@
 Maximum score of the matching ($Cn_{max}(p, W)$) represents similarity of the template in $W$, and offset index $j$ at which maximum occurs is the start point for matching.
-As the signature reverses with reversal of the direction of sampling, we compute the correlation once in a normal way and again after reversing $p$ and select the best matching score, offset index and the matching direction of sampling.
+As the signature reverses with reversal of the direction of sampling, we compute the correlation first in one direction and again after reversing $p$ and select the best matching score, offset index and the matching direction of sampling.
 Figure~\ref{ncc} depicts normalized cross correlation function over the sliding domain $j$ for part and whole curves.
@@
 Figure~\ref{mcc} depicts dissimilarity function over the sliding domain $j$.
-In this case as shown in Fig.~\ref{mcc}, we find that the first point itself is a point where the perfect match is occurred which is consistent with the fact that we slice the motion in similar manner.
+In this case as shown in Fig.~\ref{mcc}, we find that the first point itself is a point where the perfect match is occurred, which is consistent with the fact that we slice the whole motion to obtain the part motion.
 
@@
 \subsection{Objective Function for Synthesis}
-The functions in Eq.~\req{nccEq} or ~\req{mccEq} presented in the sections \ref{sec_ncc}, \ref{sec_mcc} can be used as the error measure for path or motion synthesis of any planar linkage, where the objective is to find a linkage, that produces a motion whose part or whole corresponds to target motion (or path).
+The functions in Eq.~\req{nccEq} and ~\req{mccEq} presented in the sections \ref{sec_ncc}, \ref{sec_mcc} can be used as the error measure for path and motion synthesis of any planar linkage, where the objective is to find a linkage, that produces a motion whose part or whole corresponds to target motion (or path).
 Thus we can formulate the path synthesis problem as,
@@
 \end{equation}
-where $\textbf{\emph{l}}$ is the vector of linkage parameters for particular planar linkage, p is the task curve taken as template for Normalized Cross-Correlation and ${\{W_i\}}_{i=0}^{s}$ is the signature set of all coupler paths generated by the linkage.
+where $\textbf{\emph{l}}$ is the vector of linkage parameters for particular planar linkage, p is signature the of task curve taken as template for Normalized Cross-Correlation and ${\{W_i\}}_{i=0}^{s}$ is the signature set of all $s$ coupler paths generated by the linkage corresponding to $\textbf{\emph{l}}$.
 In case of four-bar, $\textbf{\emph{l}}: l_1, l_2, l_3, l_4, l_5$, with $l_i$ is link ratio of $i^{th}$ link shown in Fig~\ref{fourbar}.
@@
 \end{equation}
-Here, E is the Dissimilarity function from eq.~\req{mccEq} while p and ${\{W_i\}}_{i=0}^{s}$ are motion signatures instead of path signatures.
+Here, E is the Dissimilarity function from Eq.~\req{mccEq} while p and ${\{W_i\}}_{i=0}^{s}$ are motion signatures instead of path signatures.
 
@@
 Considering highly non-linear nature of the problem, finding a good initial guess proves to be game changing.
-Thus we exploit the advantages of data driven approach for finding many good initial guesses or the solution itself.
+Thus we exploit machine learning techniques to create a database for finding many good initial guesses or the solution itself.
 
@@
 Owing to the complex relationship between parameter space and generated motion, small change in linkage parameters can produce large and discontinuous structural change in the generated motions.
-For example small change in crank length ($l_1$) can open a previously close loop.
+For example, small change in crank length ($l_1$) can open a previously close coupler path.
 Most of the methods based on Fourier descriptors are if defined, can not capture the continuity at such singular locations, which adversely affect the optimization process.
 In contrast to this behavior, the signatures derived in Sec.~\ref{sec_sign} have smooth transition at these singular locations due to shape similarity between a closed and just opened curve or motion.
+
 To make our point, we perform sensitivity analysis as follows:
 A four-bar with link ratios ($l_1:0.55$, $l_2:1$, $l_3:1.5$, $l_4:1$, $l_5:1$) is subjected to gradual change in parameters $l_1$ and $l_3$ by the amount (-0.2, 0.2) in steps of 0.01.
-Error function between motions of new and initial fourbar are calculated using eq.~\req{objectiveFunMotion} .
+Error function between motions of new and initial fourbar are calculated using Eq.~\req{objectiveFunMotion} .
 Figure~\ref{saCouplerCurves} shows coupler motion of some of the four-bars while Fig.~\ref{saMotionSignatures} depicts their motion signatures.
 It can be seen from Fig.~\ref{saCouplerCurves} that there exists a discontinuity in topology of the coupler curves even though their shapes have a continuous shift.
-Our method captures this continuity, which is shown by error function evaluations depicted in Fig.~\ref{saErrorFunction}.
+Our method captures this continuity, which is shown by error function evaluations depicted in Fig.~\ref{saErrorFunction}, where it is visible that surface is well behaved in the singularity region.
 
@@
 \includegraphics[width=240pt]{figure/fig_sa_distance_function.eps}
-  \caption{Distance ($E_{min}$) from eq.~\req{mccEq} as the parameters $l_1$ and $l_2$ are varied.
+  \caption{Distance ($E_{min}$) from Eq.~\req{mccEq} as the parameters $l_1$ and $l_2$ are varied.
 Although open loop breaks at $l_1$:0.55, $l_3$:1.5, there are no spikes of error function in the region near singularity, as the shape is very similar between the two topologies.}
@@
   h_i = ReLU(W_{i}h_{i-1} + b_{i}), \\
-  ReLU(x) = max(0, x).
+  ReLU(x) = max(0, x),
 \end{eqnarray}
-
-Where $W_i$ is weight matrix with dimensions $(d^{i}, d^{(i-1)})$ and $b_i$ is $d^{(i)}$ dimensional bias vector of $i^{th}$ layer, which are computed in the process of training.
+where $W_i$ is weight matrix with dimensions $(d^{i}, d^{(i-1)})$ and $b_i$ is $d^{(i)}$ dimensional bias vector of $i^{th}$ layer, which are computed in the process of training.
 Auto-encoders are trained to reconstruct the input, in this way each layer encodes the input, which is sufficient for the next layers to reconstruct the output.
@@
 \begin{equation}\label{nnloss}
-  \argminA_{W, b} \sum_{i=0}^{N} || X_i - \tilde{X}_i ||^2
+  \argminA_{W, b} \sum_{i=0}^{N} || X_i - \tilde{X}_i ||^2,
 \end{equation}
@@
 We use Agglomerative Clustering, a method of Hierarchical clustering, which is an approach to partitioning clustering for identifying groups in the dataset.
-\emph{Ward}\cite{ward1963} Linkage criterion is used for clustering, which minimizes the variance of the clusters being merged.
+\emph{Ward}\cite{ward1963} criterion is used for clustering, which minimizes the variance of the clusters being merged.
 The distance metric used is the euclidean distance in the latent space.
@@
 When user raises one such query, we first find k nearest neighbors among $1500$ cluster centers, then descend into their clusters if needed.
-Motion with highest similarity score is returned along with its corresponding linkage parameters which if required, are further fine-tuned to match the query using local optimization.
+Motion with highest similarity score is returned along with its corresponding linkage parameters, which if required are further fine-tuned to match the query using local optimization methods.
 
@@
 We compute its path signature by the steps mentioned in Algorithm ~\ref{alg_signature} and raise the query for nearest neighbors among 1500 cluster centers of our database.
-The distance metric for finding neighbors is $1-Cn_{max}$ in ~\req{objectiveFunPath}.
+The distance metric for finding neighbors is $1-Cn_{max}$ in Eq.~\req{objectiveFunPath}.
 Table~\ref{ex1_knnLinkageData} tabulates the link ratios corresponding to obtained nine nearest neighbors.
-Next step is compute actual parameters according to position, scale and orientation of the path.
-It is done by comparing analogous points found by offset index $j$ in eq.~\ref{nccEq}.
+Next step is to compute actual parameters according to position, scale and orientation of the path.
+It is done by comparing analogous points found by offset index $j$ in Eq.~\ref{nccEq}.
 Figure ~\ref{ex1_solns} shows first eight fourbar mechanisms corresponding to nearest signatures to path signature of input.
-As it can be clearly seen these linkages generate highly accurate paths without any defects throughout sit to stand activity.
+As it can be clearly seen, these linkages generate highly accurate paths without any defects throughout sit to stand activity.
 
@@
 The task is to find a pool of linkage systems that can perform snow-shoveling with a motion shown in Fig.~\ref{motionQuery}.
-The motion data is tabulated in Table ~\ref{poseData} to which we fit into a B-spline with cord length parameterization in order to get parametric representation of motion.
+The motion data is tabulated in Table ~\ref{poseData} to which we fit a B-spline with cord length parameterization in order to get parametric representation of motion.
 The task can also be treated as a finite position motion generation and solved for valid solutions.
-We try with our real time computational methods of algebraic fitting\cite{generalfitting-JCISE},\cite{deshpande2017} but obtained solutions suffer from circuit defect, which is not a surprise as those methods do not account for continuity of the input positions.
+We try with our real time computational methods of algebraic fitting\cite{generalfitting-JCISE},\cite{deshpande2017} but obtained solutions suffer from circuit defect, which is not surprising as those methods do not account for continuity of the input positions.
 
@@
 Table ~\ref{ex2_knnLinkageData} presents the linkage parameters corresponding to the nearest neighbors along with their distance score from the task.
-Coupler motions of these linkages have a part which matches with the shape of input motion query.
-Actual scaling and orientation of the linkage can be found out easily by comparing analogous points which are given by the offset index $j$ that corresponds to minimum distance$(E_min)$ in eq.~\req{mccEq}.
+Coupler motions of these linkages have a part, which matches with the shape of input motion query.
+Actual scaling and orientation of the linkage can be found out easily by comparing analogous points, which are given by the offset index $j$ that corresponds to minimum distance$(E_min)$ in Eq.~\req{mccEq}.
 Figure~\ref{ex2_solns} depict the solutions obtained after scaling and orienting the linkage to match required motion.
@@
 As ground or fixed pivot locations should lie above the ground, all solutions except the $4^{th}$ solution are suitable for the task.
-In light of these results, we can say that this approach produces a large variety of solutions which otherwise would be very hard to find using precision point approach.
+In light of these results, we can say that this approach produces a large variety of solutions, which otherwise would be very hard to find using precision point approach.
 
@@
 This approach presents a novel optimization approach towards defect free linkage synthesis.
-The framework is highly data efficient due to similarity invariant representation of paths and motion which also facilitates partial matching.
+The framework is highly data efficient due to similarity invariant representation of paths and motion, which also facilitates partial matching.
 The method always returns defect free solutions as it is inherently taken care of.
@@
 Hierarchically clustered database provides efficient query search.
-Finally, the effectiveness of presented approach is showcased by two case studies for each of which nine defect free solutions were found in contrast to one and zero solutions respectively by our algebraic fitting based precision point method.
-Although our method can provide highly accurate results, our focus here is to generate high number of defect free solutions that can perform the task in more or less similar fashion.
-Because more often than not, linkage synthesis algorithms are desired to be prolific in terms of concept generation than to produce highly accurate very few solutions.
+Finally, the effectiveness of presented approach is showcased by two case studies for each of which nine defect free solutions were found.
+Although our method can provide highly accurate results, our focus here is to generate high number of defect free solutions that can perform the task in more or less similar fashion;
+because more often than not, linkage synthesis algorithms are desired to be prolific in terms of concept generation than to produce highly accurate very few solutions.
 

### 2018-03-19 idetc2018.tex
Second Read Bug Fixes
Professor's edits

@@
 \usepackage{caption}
-\usepackage[font=small]{caption}
 \usepackage{algorithmicx}
@@
 %%% by ASME for your paper.
-\papernum{DRAFT: DETC2018-TBD}
+\papernum{DRAFT: DETC2018-85578}
 
-\title{Machine Learning-Driven Kinematic Synthesis of Defect-Free Planar Four-Bar Linkages for Motion and Path Generation using Shape Optimization}
+\title{A Machine Learning Approach to Kinematic Synthesis of Defect-Free Planar Four-Bar Linkages}
 %%% first author
-\author{Shrinath Deshpande, Anurag Purwar\footnote{Corresponding Author}\\
+\author{Shrinath Deshpande,
+	{\tensfb Anurag Purwar\thanks{Address all correspondence to this author at \href{anurag.purwar@stonybrook.edu}{anurag.purwar@stonybrook.edu}}}
     \affiliation{
-    Computer-Aided Design and Innovation Lab \\
+	Computer-Aided Design and Innovation Lab\\
 	Department of Mechanical Engineering\\
@@
 \begin{abstract}
-Success in Synthesis of mechanisms for motion generation refers to computing linkage type and dimensions to perform the task without disassembly.
-Majority of the methods formulate it as Precision Position problem (or Classical Burmester Problem) which inherently ignores the continuity information,
-resulting into solution linkages with branch, circuit and order defects.
-In this paper, we present a novel approach that addresses this issue into problem formulation and returns the solutions free from defects.
-At the heart of this approach lies an objective function that compares the motion as a whole, capturing designer's intent.
-In contrast to widely used structural error or loop-closer equation based error functions which convolute the optimization by considering shape, size, position and orientation simultaneously, this objective function computes motion difference in a form invariant to similarity transformations.
-Actual scale, position and orientation of linkage components are obtained by subsequent trivial fitting.
+The past forty years of research in mechanism synthesis has witnessed an unprecedented volume of work in formulating and solving planar four-bar linkage synthesis problems.
+However, finding practical and useful mechanisms for the motion synthesis problem has proven to be elusive as a large majority of mechanisms turn out to be defective with respect to their assembly modes.
+Most methods formulate the problem as a discrete precision position problem, which inherently ignores the continuity information in the input, resulting into linkages with branch-, circuit- and order-defects.
+In this paper, we bring together diverse fields of pattern recognition, machine learning, artificial neural network, and computational kinematics to present a novel approach that solves this problem both efficiently and effectively.
+At the heart of this approach lies an objective function that compares the motion as a whole thereby capturing designer's intent.
+In contrast to widely used structural error or loop-closure equation based error functions which convolute the optimization by considering shape, size, position and orientation simultaneously, this objective function computes motion difference in a form invariant to similarity transformations.
+We employ auto-encoder neural networks to create a compact and clustered database of invariant motions of known linkages.
+The query is raised in the database for nearest neighbors, which are either solutions or good initial conditions for fast local optimization techniques.
+In spite of highly non-linear parameters space, our approach discovers a wide pool of defect free solutions very quickly.
+We show that by employing proven machine learning techniques, this work could have far-reaching consequences to creating a multitude of useful and creative conceptual design solutions for mechanism synthesis problems, which go beyond planar four-bar linkages.
 
-We employ auto-encoder neural networks to create a compact and clustered database of invariant motions of known linkages.
-The query is raised in the database for k nearest neighbors, which are either solutions or good initial conditions for fast local optimization techniques.
-In spite of highly non-linear parameters space, our approach discovers a wide pool of defect free solutions.
+\textbf{keywords}: \emph{Machine Learning, Artificial Neural Network (ANN), Path Synthesis, Motion Synthesis, Planar Four-bar linkage, Type and Dimensional Synthesis, Circuit- Order-, and Branch-Defect}
+
 \end{abstract}
@@
 \section{Introduction}
-Classical mechanism synthesis problem deals with computing type and dimensions of linkage system for performing specific tasks, which are categorized as path, motion and function generation.
-These problems have been dealt with by many approaches with the aim of finding acceptable solutions for practical situations.
-Several text books, such McCarthy and Soh \cite{sohmccarthy}, Sandor and Erdman~\cite{Sandor}, Hunt \cite{Hunt78}, Hartenberg and Denavit \cite{Hartenberg},  Suh and Radcliffe \cite{Suh78}, and Lohse \cite{lohse2013} cover the science and art of planar four-bar and higher-order linkages.
-The majority of these theories don't account for circuit and branch defect in the synthesis process, which can render the solution useless for practical applications.
-These defects in single DOF mechanisms are thoroughly discussed by Chase and Mirth\cite{chasemirth}.
+Classical mechanism synthesis problem deals with computing type and dimensions of linkage system for performing specific tasks, which are categorized as path, motion and function generation; for an exhaustive reference see  books from such McCarthy and Soh \cite{sohmccarthy}, Sandor and Erdman~\cite{Sandor}, Hunt \cite{Hunt78}, Hartenberg and Denavit \cite{Hartenberg},  Suh and Radcliffe \cite{Suh78}, and Lohse \cite{lohse2013}.
+Various approaches have been proposed in the literature with the aim of finding acceptable solutions for practical situations.
+However, the majority of the approaches do not account for circuit and branch defect in the synthesis process, which can render the solution useless for practical applications.These defects in single degree of freedom mechanisms are thoroughly discussed by Chase and Mirth\cite{chasemirth}.
 
@@
 \includegraphics[width=\textwidth]{figure/overall_approach.eps}
-  \caption{General Layout of the approach.}
+  \caption{The Machine Learning approach begins by creating an invariant signature for the path and the motion data, which facilitates a compact and hierarchical clustered database and an auto-encoder Neural Network trained to elicit good, defect-free solutions or subjected to local, fast optimization.
+The results are astonishingly good, defect-free concept design solutions for input problems.}
 \label{overallMethod}
@@
 
-Original contribution of this paper are in 1) a novel objective function for defect-free motion generation problem, 2) discovering a representation of coupler motion and path which is invariant under similarity transformations (henceforth termed as motion signature and path signature respectively), 3) novel algorithm for partial matching of motions , 4) optimal storage data by means of auto-encoder neural network and efficient neighbor search in the clustered database.
-The objective function that drives the synthesis process, computes a distance measure of dissimilarity between the task motion and the coupler motion generated by current linkage parameters.
-This distance measure of dissimilarity inherently requires continuity of motion; ensuring the output mechanism is defect free throughout the task.
+In this paper, we 1) employ pattern recognition and computational shape analysis to create a similarity transforms-independent signature for the path and motion, 2) exploit the non-linear nature of relationship between the linkage parameters and the coupler motions to create a sensitive, wide-ranging, compact, and efficient database with hierarchical clustering, and 3) enable dimensionality reduction using Auto-encoder Neural Networks.
+When a user inputs a motion or a path, a query representing invariant signature \footnote{path or motion signature} of the input is raised for $k$ nearest neighbors among cluster centers in the database.
+The neighbor is defined as motion or path whose part has a similar signature to the input.
+These $k$ neighbors, if needed, are subjected to fine tuning by local optimization to obtain set of defect-free solutions.
+We define a novel objective function for defect-free motion generation problems and a novel algorithm for partial matching of motions.
+The objective function that drives the synthesis process computes a distance measure of dissimilarity between the task motion and the coupler motion generated by current linkage parameters.
+This distance measure of dissimilarity inherently requires continuity of motion, thus ensuring that the output mechanism is defect free throughout the task.
+The Fig.~\ref{overallMethod} illustrates an overview of our method, which is codified in Algorithm~\ref{alg_overall}.
 
-Path synthesis methods based on Fourier analysis do take the continuity information of the coupler path into account, however majority of them are only defined on closed loop curves.
+Path synthesis methods based on Fourier analysis do take the continuity information of the coupler path into account; however most of them are defined only for closed loop curves.
 Ullah and Kota\cite{ullah1997} have presented an invariant approach towards representation and synthesis of closed paths through shape optimization.
-They use combination of global and local search methods by optimizing Fourier Deviant function to compute the dimensions of planar fourbar linkage without any initial guesses.
-Wu et al.\cite{wu2011} presented a synthesis method for path generation based on finite Fourier series for synthesis of open and closed paths.
-In the case of motion generation, methods that take the branching defect into consideration, limit their search in the configuration space where Grashof condition holds true.
-To our best knowledge, no other motion generation method truly takes the motion continuity into account.
+They use a combination of global and local search methods by optimizing Fourier Deviant function to compute the dimensions of planar four bar linkages without any initial guesses.
+Wu et al.\cite{wu2011} presented a method for open and closed path generation based on finite Fourier series.
+In the case of motion generation, methods that take the branching defect into consideration limit their search in the configuration space where Grashof condition holds true.
+To the best of our knowledge, no motion generation methods truly take the motion continuity into account.
 
-Owing to the highly nonlinear nature of the problem, most optimization based methods require good initial condition to start.
+Due to the highly nonlinear nature of the problem, most optimization based methods require a good initial condition to start.
 Thus, an atlas or a design library is used to provide good initial conditions.
-McGarva\cite{mcgarva1994} has taken the earliest approach towards creating a library for coupler trajectories based on harmonic analysis.
+McGarva\cite{mcgarva1994} took the earliest approach towards creating a library for coupler trajectories based on harmonic analysis.
 Wandling\cite{wandling2000} has presented an atlas based approach, where coupler paths and motions are stored in terms of Fourier Transforms.
-Input motion is searched for neighbors based on euclidean distances of Fourier Transforms.
+Input motion is searched for neighbors based on Euclidean distances of Fourier Transforms.
 Yue et al.\cite{yue-pathgen2011} presented a similar approach of path generation using P-Type Fourier Descriptor applicable for open curves.
-In their approach, a task curve is transformed into normalized Fourier coefficients and queried for nearest neighbor search.
-The best match is returned as solution to input.
-Chu et al.\cite{chu2010} have showcased an atlas based method of synthesizing spatial fourbar linkage for function generation problem where orientation data is stored in terms of Fourier harmonics.
+In their approach, a task curve is transformed into normalized Fourier coefficients and queried for the nearest neighbor search.
+The best match is returned as a solution to input.
+Chu et al.\cite{chu2010} presented an atlas based method for synthesizing spatial four bar linkages for function generation problems where orientation data is stored in terms of Fourier descriptors.
 
 The above methods generate data based on uniform sampling in the linkage parameter space.
-Given the highly nonlinear mapping between linkage parameters and coupler trajectory, this way of sampling leads into non-uniform sampling of trajectory space causing under-representation of possible motions.
-We try to address this issue by employing log normal distribution in the linkage parameter space to generate data and perform compact clustering of the data using machine learning techniques.
-A Hierarchy is created in the database by means of clustering, where the top level comprises of few data points called cluster centers which are representative of the cluster points in the lower levels.
-Also the methods\cite{wandling2000},\cite{yue-pathgen2011} have built the library with all possible coupler curves, where one curve is broken down into many segments for creating data for partial curves.
+Given the highly nonlinear mapping between linkage parameters and coupler trajectory, this way of sampling leads to non-uniform sampling of trajectory space causing under-representation of possible motions.
+We address this issue by employing log-normal distribution in the linkage parameter space to generate data and perform compact clustering of the data using machine learning techniques.
+A hierarchy is created in the database by means of clustering, where the top level comprises of data points called cluster centers, which are representative of the cluster points in the lower levels.
+Wandling~\cite{wandling2000} and Yu et al.~\cite{yue-pathgen2011} have built libraries with all possible coupler curves, where one curve is broken down into many segments for creating data for partial curves.
 In contrast to this, we need to store only one curve representing all the segments in it as our representation facilitates partial matching.
-No other previous method facilitates this partial matching of open motion curve into another open or closed curve.
-Thus reducing the data requirement even further.
+No other previous methods facilitate this partial matching of open motion curve into another open or closed curve. This reduces the data requirement even further.
 
-When a user inputs a motion or a path, a query representing invariant signature \footnote{path or motion signature} of the input is raised for k nearest neighbors among cluster centers in the database.
-The neighbor is defined as motion or path whose part has a similar signature to the input. These k neighbors if needed, are subjected to fine tuning by local optimization to obtain set of solutions.
-Overall method depicted in Fig.~\ref{overallMethod} is codified in Algorithm ~\ref{alg_overall}.
-
-Organization of the paper is as follows. Section~\ref{sec_sign} presents the computation of motion and path signatures.
-Section~\ref{sec_distanceMetric} is comprised of evaluation criterion for two signatures based on the shape similarity, which leads to form the error function for optimization.
+Rest of this paper is organized as follows. Section~\ref{sec_sign} presents the computation of motion and path signatures.
+Section~\ref{sec_distanceMetric} is comprised of evaluation criterion for two signatures based on the shape similarity, which leads to a formulation of the error function for optimization.
 Section~\ref{sec_SA} discusses the nature of objective function via sensitivity analysis at a singularity.
-Section~\ref{sec_db_ae} explains the database generation and clustering using auto-encoders for efficient sampling and query operations.
-Finally, two case studies are presented~\ref{sec_example} to showcase efficacy of the method.
+Section~\ref{sec_db_ae} presents the database generation and clustering using auto-encoders for efficient sampling and query operations.
+Finally, two case studies are presented in section~\ref{sec_example} to illustrate the efficiency and efficacy of the method.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
     }
-    kNeighbors = getNeighbors(distances, k)
+    $k$Neighbors = getNeighbors(distances, $k$)
     \For{neighbor \textbf{in} kNeighbors}
@@
 \section{Signatures of Coupler Path and Motion}\label{sec_sign}
-The main focus of the paper is a novel method for motion generation that takes a continuous task motion or path as the input and returns defect-free linkages producing similar motion or path.
+The focus of the paper is on a novel method for motion generation that takes a continuous task motion or path as the input and returns defect-free linkages producing similar motion or path.
 The objective function evaluation requires the input motion to be transformed into a specific form, which we call the signature of input motion.
-This signature representation is invariant to similarity operations, which are reflection, rotation, translation and scaling.
-Signature for path and motion are termed as path signature and motion signature respectively.
-For calculating path signature we use formulations developed by Cui et.al\cite{cui2009}.
+This signature representation should be invariant to similarity operations, viz. reflection, rotation, translation and scaling.
+Signatures for path and motion are termed as path signature and motion signature, respectively.
+For calculating path signature, we use formulations developed by Cui et.al\cite{cui2009}.
 For this task, our approach requires the input in terms of a parametric motion $(x:x(t), y:y(t), \theta:\theta(t))$.
-This section explains the procedure of signature calculation given in Algorithm ~\ref{alg_signature}.
-
-\begin{algorithm}
-    \SetKwInOut{Input}{Input}
-    \SetKwInOut{Output}{Output}
-    \Input{Twice Differentiable Parametric Representation of Motion $(x:x(t), y:y(t), \theta:\theta(t))$}
-    \Output{signature //discretized signal in form of an array}
-    k(t) = ComputeCurvature(x, y) using Eq.~\ref{curvatureEq} \\
-    K(t) = IntergrateCumulatively(k(t)) using Eq.~\ref{kInt} \\
-    motionSignature = [] \\
-    pathSignature = [] \\
-    \For{$i = 0 \to max(K)$}
-    {
-      tmp = (value of t corresponding to which K has value i) \\
-      $i = i + 0.1$ \\
-      motionSignature.push(k(tmp)) \\
-      pathSignature.push(k(tmp))
-    }
-    \Return{PathSignature, MotionSignature}
-    \caption{Calculate Invariant Signatures}
-    \label{alg_signature}
-\end{algorithm}
 
@@
 \end{eqnarray}
-where $\dot{x}$, $\ddot{x}(t)$ are first and second order derivative w.r.t. parameter t.
-For an example, parametric motion could be a B-spline motion as shown in fig~\ref{bsplineFitting}.
-We compute the curvature of path along the direction of t, using Eq.~\ref{curvatureEq} and the cumulative integral by Eq.~\ref{kInt}.
-For implementation purposes, we use scipy\cite{scipy} module for computations of B-splines and their derivatives.
-Figure~\ref{curvatureK} shows computed curvatures and its unsigned integral of coupler path shown in Fig.~\ref{bsplineFitting}.
-It can be seen that curvature is very low at start, increases as the curve bends along the path and drops once again as the path straightens out.
-It is obvious that curvature plot will reverse if the direction of parameterization reverses.
+where $\dot{x}$, $\ddot{x}(t)$ are first and second order derivative with respect to parameter $t$.
+As an example, the parametric motion could be a B-spline motion as shown in Fig~\ref{bsplineFitting} or it could be a discrete set of poses, which could be represented by a continuous signal using Fourier series.
+We compute the curvature of path along the direction of $t$, using Eq.~\req{curvatureEq} and the cumulative integral by Eq.~\req{kInt}.
+Figure~\ref{curvatureK} shows computed curvature and its unsigned integral of the coupler path shown in Fig.~\ref{bsplineFitting}.
+It can be seen that curvature is small start, increases as the curve bends along the path and drops once again as the path straightens out.
+It is obvious that curvature plot will reverse if the direction of parameterizations reverses, while the integral is a monotonically increasing function.
 
@@
 \includegraphics[width=240pt]{figure/fig_bspline.eps}
-  \caption{a) The path of the input motion along with direction of parameterization. b) Motion components $x(t), y(t), \theta(t)$ are plotted against parameter t.}
+  \caption{a) The path of the input motion along with direction of parametrization. b) Motion components $x(t), y(t), \theta(t)$ are plotted against parameter t.}
 \label{bsplineFitting}
@@
 
-Now we re-sample the curvature at equal intervals of $K(t)$, which is equivalent to plotting $k$ vs $K$ in Fig~\ref{signature}(a).
-This is done by finding the parameter values of t where $K$ changes in the steps of some step size. For practical purposes we find array of parameter t such that $K$ increments by 0.1.
-For each value of t in such array, we compute $k(t)$ and $\theta(t)$ and store it as the path and motion signatures respectively.
+Now, we re-sample the curvature at equal intervals of $K(t)$, which is equivalent to plotting $k$ vs $K$ in Fig~\ref{signature}(a).
+This is done by finding the parameter values of $t$ where $K$ changes uniformly.
+For practical purposes, we find an array of parameter $t$ such that $K$ increments by 0.1.
+For each value of $t$ in the array, we compute $k(K)$ and $\theta(K)$ and store it as the path and motion signatures respectively. We note that there is a one-to-one mapping between $t$ and $K$.
 
 These signatures are invariant under similarity transformations; for proof see\cite{cui2009}.
-The general intuition is as follows:
-we know that curvature changes inversely to the scale of the curve, so when it is integrated along the scaled curve, the scale factor cancels itself out.
+We know that curvature changes inversely to the scale of the curve, so when it is integrated along the scaled curve, the scale factor cancels itself out.
 Reflection operation on the motion or the path, produces flipped path signature, but motion signature remains invariant.
 
-Figure~\ref{signature} shows path and motion signature obtained for the motion depicted in Fig.~\ref{bsplineFitting}
+Figure~\ref{signature} shows path and motion signature obtained for the motion depicted in Fig.~\ref{bsplineFitting}.
 It is important to note that signature depends on the direction along which we compute the curvature $k(t)$ as well as re-sample $\theta(t)$.
@@
 
+The procedure of signature calculation presented in this section is given in Algorithm ~\ref{alg_signature}.
+
+\begin{algorithm}
+    \SetKwInOut{Input}{Input}
+    \SetKwInOut{Output}{Output}
+    \Input{Twice Differentiable Parametric Representation of Motion $(x:x(t), y:y(t), \theta:\theta(t))$}
+    \Output{signature //discretized signal in form of an array}
+    $k(t)$ = ComputeCurvature$(x, y)$ using Eq.~\ref{curvatureEq} \\
+    $K(t)$ = IntergrateCumulatively($k(t)$) using Eq.~\ref{kInt} \\
+    motionSignature = [] \\
+    pathSignature = [] \\
+    \For{$i = 0 \to max(K)$}
+    {
+      $tmp$ = (value of $t$ corresponding to which $K$ has value $i$) \\
+      $i = i + 0.1$ \\
+      motionSignature.push($k$($tmp$)) \\
+      pathSignature.push($k$($tmp$))
+    }
+    \Return{PathSignature, MotionSignature}
+    \caption{Calculate Invariant Signatures}
+    \label{alg_signature}
+\end{algorithm}
+
 \section{Signature Matching and Error Function}\label{sec_distanceMetric}
 The signatures obtained in the previous steps contain important information about shape of the trajectory.
-In this section we formulate functions that evaluate the similarity (or distance) between two trajectories based on their signatures.
-These distance functions can be used as error metric which can be minimize using optimization methods.
+In this section, we formulate functions that evaluate the similarity (or, distance) between two trajectories based on their signatures.
+These distance functions can be used as error metric, which can be minimized using optimization methods.
 
@@
 
-Lets consider two coupler paths; namely part and whole as shown in~\ref{wholePart}.
-Let $p$ be path signature of the part path which acts as template, while $W$ is path signature of the whole path that can completely embed the template as shown in Fig.~\ref{pathSignature}.
-The orientation information shown in Fig.~\ref{wholePart}, is ignored for path matching.
+Let us consider two coupler paths; namely part and whole as shown in~\ref{wholePart}.
+Let $p$ be path signature of the part path which acts as a template, while $W$ is path signature of the whole path that can completely embed the template as shown in Fig.~\ref{pathSignature}.
+The orientation information shown in Fig.~\ref{wholePart} is ignored for path matching.
 It will be used later for matching of motion signature.
-The way this partial matching works is as follows:
+The partial matching works as follows:
 
@@
 \end{equation}
-where $Cn(j, p, W)$ is the normalized cross-correlation value when template $p$ is matched against $W$ at $j^{th}$ index, $p_{span}$ is the length of the array $p$ and $\bar{W}(j\to j + p_{span})$ is the mean for the values of array $W$ between index range of ($j, j+p_{span}$)
+where $Cn(j, p, W)$ is the normalized cross-correlation value when template $p$ is matched against $W$ at $j^{th}$ index; $p_{span}$ is the length of the array $p$ and $\bar{W}(j\to j + p_{span})$ is the mean for the values of array $W$ between index range of ($j, j+p_{span}$).
 
-Here $p$ acts as template that tries to find best match against $W$ while sliding over it along j.
+Here, $p$ acts as a template that tries to find best match against $W$ while sliding over it along $j$.
 Domain of $Cn(j, p, W)$ is [0, 1], where 1 represents the complete embedment.
 
-Maximum score of the matching ($Cn_{max}(p, W)$) represents similarity of the template in $W$, and offset index $j$ at which maximum occurs is the start point for matching.
+Maximum score of the matching $Cn_{max}(p, W)$ represents similarity of the template in $W$, and offset index $j$ at which maximum occurs is the start point for matching.
 As the signature reverses with reversal of the direction of sampling, we compute the correlation first in one direction and again after reversing $p$ and select the best matching score, offset index and the matching direction of sampling.
@@
 \includegraphics[width=240pt]{figure/fig_path_signatures.eps}
-  \caption{Path Signatures of part $p$ and whole $W$ from Fig.~\ref{wholePart}.The domain of path signature is scale invariant but the range still has a scaling factor, which is taken care by normalized cross-correlation.}
+  \caption{Path Signatures of part $p$ and whole $W$ from Fig.~\ref{wholePart}.
+The array index $i$ corresponds to the index location for the array of the $K$.
+The domain of path signature is scale invariant but the range still has a scaling factor, which is taken care of by normalized cross-correlation.}
 \label{pathSignature}
@@
 Consider part and whole motions shown in Fig.~\ref{wholePart}.
-Let $p$ and $W$ be the motion signatures of part and whole motions respectively.
-All the steps are same as done for partial matching of path signature except the cross-correlation function which is given by,
+Let $p$ and $W$ be the motion signatures of part and whole motions, respectively as shown in Fig.~\ref{motionSignature}.
+Similar to the partial matching of path signature, the cross-correlation function is given by,
 
@@
 Similar to path signature, motion signature is dependent on the sampling direction along the motion.
-Thus we compute the dissimilarity for both direction and the take whichever is the least i.e.
+Thus, we compute the dissimilarity for both direction and choose whichever is the least i.e.
 $E_{min}(p, W)$.
 Figure~\ref{mcc} depicts dissimilarity function over the sliding domain $j$.
-In this case as shown in Fig.~\ref{mcc}, we find that the first point itself is a point where the perfect match is occurred, which is consistent with the fact that we slice the whole motion to obtain the part motion.
+In this case, as shown in Fig.~\ref{mcc}, we find that the first point itself is a point where the perfect match occurs, which is consistent with the fact that we have essentially sliced the whole motion to obtain the part motion.
 
@@
 \centering
-\includegraphics[width=240pt]{figure/fig_motion_signatures.eps}
-  \caption{Motion Signatures of the trajectories shown in Fig.\ref{wholePart}. The domain as well as range of motion signature is invariant to similarity transformation.}
+\includegraphics[width=260pt]{figure/fig_motion_signatures.eps}
+  \caption{Motion Signatures of the trajectories shown in Fig.~\ref{wholePart}. The domain as well as range of motion signature is invariant to similarity transformation.}
 \label{motionSignature}
@@
 \subsection{Objective Function for Synthesis}
-The functions in Eq.~\req{nccEq} and ~\req{mccEq} presented in the sections \ref{sec_ncc}, \ref{sec_mcc} can be used as the error measure for path and motion synthesis of any planar linkage, where the objective is to find a linkage, that produces a motion whose part or whole corresponds to target motion (or path).
+The functions in Eq.~\req{nccEq} and ~\req{mccEq} presented in the sections \ref{sec_ncc}, \ref{sec_mcc} can be used as the error measure for path and motion synthesis of any planar linkage, where the objective is to find a linkage that produces a motion whose part or whole corresponds to target motion (or path).
 Thus we can formulate the path synthesis problem as,
@@
 \begin{equation}\label{objectiveFunPath}
-  \argminA_{\textbf{\emph{l}}, W_i} (1 - Cn_{max}(p, W_i)
+  \argminA_{\textbf{\emph{l}}, W_i} (1 - Cn_{max}(p, W_i),
 \end{equation}
-where $\textbf{\emph{l}}$ is the vector of linkage parameters for particular planar linkage, p is signature the of task curve taken as template for Normalized Cross-Correlation and ${\{W_i\}}_{i=0}^{s}$ is the signature set of all $s$ coupler paths generated by the linkage corresponding to $\textbf{\emph{l}}$.
-In case of four-bar, $\textbf{\emph{l}}: l_1, l_2, l_3, l_4, l_5$, with $l_i$ is link ratio of $i^{th}$ link shown in Fig~\ref{fourbar}.
+where $\textbf{\emph{l}}$ is the vector of linkage parameters for particular planar linkage, $p$ is signature the of task curve taken as template for Normalized Cross-Correlation and ${\{W_i\}}_{i=0}^{s}$ is the signature set of all $s$ coupler paths generated by the linkage corresponding to $\textbf{\emph{l}}$.
+In case of four-bar, $\textbf{\emph{l}}: l_1, l_2, l_3, l_4, l_5$, where $l_i$ is link ratio of $i^{th}$ link shown in Fig~\ref{fourbar}.
 
@@
 \begin{equation}\label{objectiveFunMotion}
-  \argminA_{\textbf{\emph{l}}, W_i} (E_{min}(p, W_i))
+  \argminA_{\textbf{\emph{l}}, W_i} (E_{min}(p, W_i)).
 \end{equation}
-Here, E is the Dissimilarity function from Eq.~\req{mccEq} while p and ${\{W_i\}}_{i=0}^{s}$ are motion signatures instead of path signatures.
+Here, $E$ is the Dissimilarity function from Eq.~\req{mccEq} while $p$ and ${\{W_i\}}_{i=0}^{s}$ are motion signatures instead of path signatures.
 
@@
 \centering
-\includegraphics[width=240pt]{figure/fig_fourbar.eps}
+\includegraphics[width=270pt]{figure/fig_fourbar.eps}
   \caption{Parametric representation of four-bar linkage with all revolute joints.
-We set $l_0 = 1$ and one fixed joint at origin of the global frame along with making fixed length of the fourbar parallel to x axis.}
+We set $l_0 = 1$ and one fixed joint at origin of the global frame along with making fixed length of the four bar parallel to x axis.}
 \label{fourbar}
@@
 
-Considering highly non-linear nature of the problem, finding a good initial guess proves to be game changing.
-Thus we exploit machine learning techniques to create a database for finding many good initial guesses or the solution itself.
+Considering highly non-linear nature of the problem, finding a good initial guess proves to be daunting.
+Thus, we exploit machine learning techniques to create a database for finding many good initial guesses or the solution itself.
 
 \section{Sensitivity Analysis of Signatures}\label{sec_SA}
-Owing to the complex relationship between parameter space and generated motion, small change in linkage parameters can produce large and discontinuous structural change in the generated motions.
-For example, small change in crank length ($l_1$) can open a previously close coupler path.
-Most of the methods based on Fourier descriptors are if defined, can not capture the continuity at such singular locations, which adversely affect the optimization process.
+Due to the complex relationship between parameter space and generated motion, small changes in linkage parameters can produce large and discontinuous structural changes in the generated motions.
+For example, a small change in crank length ($l_1$) can open a previously close coupler path.
+Most of the methods based on Fourier descriptors can not capture the continuity at such singular locations, which adversely affect the optimization process.
 In contrast to this behavior, the signatures derived in Sec.~\ref{sec_sign} have smooth transition at these singular locations due to shape similarity between a closed and just opened curve or motion.
 
-To make our point, we perform sensitivity analysis as follows:
+To illustrate this, we perform sensitivity analysis in the vicinity of a singularity as follows:
 A four-bar with link ratios ($l_1:0.55$, $l_2:1$, $l_3:1.5$, $l_4:1$, $l_5:1$) is subjected to gradual change in parameters $l_1$ and $l_3$ by the amount (-0.2, 0.2) in steps of 0.01.
-Error function between motions of new and initial fourbar are calculated using Eq.~\req{objectiveFunMotion} .
+Error function between motions of new and initial four bar are calculated using Eq.~\req{objectiveFunMotion} .
 Figure~\ref{saCouplerCurves} shows coupler motion of some of the four-bars while Fig.~\ref{saMotionSignatures} depicts their motion signatures.
+Please note that these two figures show the effect of changing only one parameter $l_1$.
 It can be seen from Fig.~\ref{saCouplerCurves} that there exists a discontinuity in topology of the coupler curves even though their shapes have a continuous shift.
 Our method captures this continuity, which is shown by error function evaluations depicted in Fig.~\ref{saErrorFunction}, where it is visible that surface is well behaved in the singularity region.
+This error function accounts for changes to both the parameters $l_1$ and $l_3$.
 
@@
 \includegraphics[width=240pt]{figure/fig_sa_coupler_curves.eps}
-  \caption{Coupler Motions of the fourbar linkage with variation of parameters $l_1$ and $l_2$. It can be seen that motion topology changes from close-loop Grashof to open loop Triple-Rocker.}
+  \caption{Coupler Motions of the four bar linkage with variation of parameters $l_1$ and $l_2$. It can be seen that motion topology changes from close-loop Grashof to open loop Triple-Rocker.}
 \label{saCouplerCurves}
@@
 \includegraphics[width=240pt]{figure/fig_sa_distance_function.eps}
-  \caption{Distance ($E_{min}$) from Eq.~\req{mccEq} as the parameters $l_1$ and $l_2$ are varied.
+  \caption{Distance ($E_{min}$) from Eq.~\req{mccEq} as the parameters $l_1$ and $l_3$ are varied.
 Although open loop breaks at $l_1$:0.55, $l_3$:1.5, there are no spikes of error function in the region near singularity, as the shape is very similar between the two topologies.}
@@
 \section{Clustered Database of Planar Linkages}\label{sec_db_ae}
-Having a invariant representation facilitating partial matching greatly reduces data required to sample all possible types shapes of coupler motion.
+Having an invariant representation facilitating partial matching greatly reduces data required to sample all possible types shapes of coupler motion.
 We have built a database of planar four-bar linkages with revolute joints as an example, but the approach is same for any planar motion generating machine.
@@
   \item Sampling should maximize the uniformity of its distribution over the space of four-bar coupler motions.
-  \item Data generation can be parallelized.
-  \item Scalable with linkages with more number of links.
+  \item Data generation should be parallelized.
+  \item It should be scalable to higher-order linkages.
 \end{enumerate}
 Figure~\ref{fourbar} represents parametric representation of four-bar linkage with parameters ($l_1,l_2,l_3,l_4,l_5$).
-As mapping between four-bar linkage parameter space and coupler motion space is highly non-linear, uniform distribution over linkage parameter space doesn't necessarily mean uniform sampling over motion space.
-Thus the efficient approach would be to sample more in the regions where sensitivity is maximum.
-Our observational intuition tells that whenever the link ratios of four-bar linkage are close to 1, the sensitivity of the shape of a coupler motion is higher than otherwise.
-Thus we have chosen Log-Normal probalitiy distribution ($\mu = 0,\sigma = 0.6 $) for selecting the link ratios : $(l_1, l_2, l_3)$ as shown in Fig.~\ref{logNormal}, and Normal Distribution ($\mu = 0,\sigma = 2 $) for $(l_4, l_5)$.
+As mapping between four-bar linkage parameter space and coupler motion space is highly non-linear, uniform distribution over linkage parameter space does not necessarily mean uniform sampling over motion space.
+Thus, an efficient approach would be to sample more in the regions where sensitivity is maximum.
+We have observed that whenever the link ratios of four-bar linkage are close to 1, the sensitivity of the shape of a coupler motion is higher than otherwise.
+Thus, we have chosen Log-Normal probability distribution ($\mu = 0,\sigma = 0.6 $) for selecting the link ratios : $(l_1, l_2, l_3)$ as shown in Fig.~\ref{logNormal}, and Normal Distribution ($\mu = 0,\sigma = 2 $) for $(l_4, l_5)$.
 
@@
 Auto-encoder is a powerful mapping model, which learns to encode the input data in very compact representation and can reconstruct the input with minimal error; performing much better than Principal Component Analysis\cite{hinton2006}.
-This Non-linear mapping by auto-encoder can greatly improve the representation of data for clustering (For details refer \cite{song2013}).
+This non-linear mapping by auto-encoder can greatly improve the representation of data for clustering~\cite{song2013}.
 Figure~\ref{autoEncoder} shows a Neural Network architecture similar to the one we designed for the task.
@@
 
-Once a network is trained, Output of the bottle-neck layer $(h_{ib})$ represents the compressed feature space ($Z$).
+Once a network is trained, output of the bottle-neck layer $(h_{ib})$ represents the compressed feature space ($Z$).
 As the bottleneck layer has 10 neurons and input is 100 dimensional vector, it is evident that information is compressed by a factor of 10, while achieving $95\%$ reconstruction accuracy as a result of training.
@@
 \emph{Ward}\cite{ward1963} criterion is used for clustering, which minimizes the variance of the clusters being merged.
-The distance metric used is the euclidean distance in the latent space.
+The distance metric used is the Euclidean distance in the latent space.
 Although the more accurate distance metric is distance function discussed in sec.~\ref{sec_distanceMetric}, it is very expensive to calculate it for entire database.
 Signatures with ${O}(m)$ points, take ${O}(m\log{}m)$ time for each comparisons and there are ${O}(N^2)$ number of comparisons to be made for database of $N$ points.
-When user raises one such query, we first find k nearest neighbors among $1500$ cluster centers, then descend into their clusters if needed.
-Motion with highest similarity score is returned along with its corresponding linkage parameters, which if required are further fine-tuned to match the query using local optimization methods.
+When user raises one such query, we first find $k$ nearest neighbors among $1500$ cluster centers, then descend into their clusters if needed.
+Motion with highest similarity score is returned along with its corresponding linkage parameters, which if required, are further fine-tuned to match the query using local optimization methods.
+Computationally, on a 2.4 GHz Core i5 MacBook Pro with 8 GB memory, every query takes 23 seconds on average to find the sorted list of nearest neighbors among cluster centers.
 
@@
 \centering
-\includegraphics[width=240pt]{figure/fig_auto_encoder.eps}
+\includegraphics[width=270pt]{figure/fig_auto_encoder.eps}
   \caption{A small scale version of the Auto-Encoder.
@@
 \subsection{Path Generation}
-In the design phase of a rehabilitation device that assists people stand from sitting position, it is required to generate linkages that can execute a sit-to-stand (STS) trajectory of hip as shown in Fig.~\ref{ex1_path}.
+In the design phase of a rehabilitation device that assists people stand from sitting position, it is required to generate linkages that can execute a sit-to-stand (STS) trajectory of the hip joint as shown in Fig.~\ref{ex1_path}.
 Table~\ref{hipPathTab} presents the discretized path data.
-As our approach requires parametric representation of path, we first fit a cubic B-Spline with cord length parameterization through path data points to generate parametric curve shown in Fig.~\ref{ex1_path}.
+As our approach requires parametric representation of path, we first fit a cubic B-Spline with cord length parametrization through path data points to generate parametric curve shown in Fig.~\ref{ex1_path}.
 We compute its path signature by the steps mentioned in Algorithm ~\ref{alg_signature} and raise the query for nearest neighbors among 1500 cluster centers of our database.
@@
 It is done by comparing analogous points found by offset index $j$ in Eq.~\ref{nccEq}.
-Figure ~\ref{ex1_solns} shows first eight fourbar mechanisms corresponding to nearest signatures to path signature of input.
-As it can be clearly seen, these linkages generate highly accurate paths without any defects throughout sit to stand activity.
+Figure ~\ref{ex1_solns} shows first eight four bar mechanisms corresponding to nearest signatures to path signature of input.
+It can be clearly seen that these linkages generate highly accurate paths for the sit to stand activity.
 
@@
 \end{tabular}
-\caption{First 8 Linkages in the table~\ref{ex1_knnLinkageData} and their resultant coupler paths.}
+\caption{First eight linkages in the table~\ref{ex1_knnLinkageData} and their resultant coupler paths.}
 \label{ex1_solns}
@@
 The task is to find a pool of linkage systems that can perform snow-shoveling with a motion shown in Fig.~\ref{motionQuery}.
-The motion data is tabulated in Table ~\ref{poseData} to which we fit a B-spline with cord length parameterization in order to get parametric representation of motion.
+The motion data is tabulated in Table ~\ref{poseData} to which we fit a B-spline with cord length parametrization in order to get parametric representation of motion.
 The task can also be treated as a finite position motion generation and solved for valid solutions.
@@
 Next we raise the signature query for nearest signatures among the cluster centers of the database.
-Fig.\ref{queryResult} shows nine nearest neighbor signatures along with the task signature.
-Table ~\ref{ex2_knnLinkageData} presents the linkage parameters corresponding to the nearest neighbors along with their distance score from the task.
+Fig.~\ref{queryResult} shows nine nearest neighbor signatures along with the task signature.
+Table~\ref{ex2_knnLinkageData} presents the linkage parameters corresponding to the nearest neighbors along with their distance score from the task.
 Coupler motions of these linkages have a part, which matches with the shape of input motion query.
@@
 \centering
-\includegraphics[width=240pt]{figure/fig_ex_motion_signatures.eps}
+\includegraphics[width=260pt]{figure/fig_ex_motion_signatures.eps}
   \caption{Case Study 2 - Query Result: Motion signatures in the dataset with highest similarity.}
@@
 
+\begin{figure}
+\begin{tabular}{cc}
+  1)\putindeepbox[2pt]{\includegraphics[width=120pt]{figure/sol1.eps}}
+    & 2)\putindeepbox[2pt]{\includegraphics[width=120pt]{figure/sol2.eps}} \\
+  3)\putindeepbox[2pt]{\includegraphics[width=120pt]{figure/sol3.eps}}
+    & 4)\putindeepbox[2pt]{\includegraphics[width=120pt]{figure/sol4.eps}}\\
+  5)\putindeepbox[2pt]{\includegraphics[width=120pt]{figure/sol6.eps}}
+    & 6)\putindeepbox[2pt]{\includegraphics[width=120pt]{figure/sol7.eps}} \\
+  7)\putindeepbox[2pt]{\includegraphics[width=120pt]{figure/sol8.eps}}
+    & 8)\putindeepbox[2pt]{\includegraphics[width=120pt]{figure/sol9.eps}}\\
+\end{tabular}
+\caption{Case Study 2: First eight linkages in the table~\ref{ex2_knnLinkageData} and their resultant coupler motions.}
+\label{ex2_solns}
+\end{figure}
+
 \begin{table}
@@
 
-\begin{figure}
-\begin{tabular}{cc}
-  1)\putindeepbox[2pt]{\includegraphics[width=120pt]{figure/sol1.eps}}
-    & 2)\putindeepbox[2pt]{\includegraphics[width=120pt]{figure/sol2.eps}} \\
-  3)\putindeepbox[2pt]{\includegraphics[width=120pt]{figure/sol3.eps}}
-    & 4)\putindeepbox[2pt]{\includegraphics[width=120pt]{figure/sol4.eps}}\\
-  5)\putindeepbox[2pt]{\includegraphics[width=120pt]{figure/sol6.eps}}
-    & 6)\putindeepbox[2pt]{\includegraphics[width=120pt]{figure/sol7.eps}} \\
-  7)\putindeepbox[2pt]{\includegraphics[width=120pt]{figure/sol8.eps}}
-    & 8)\putindeepbox[2pt]{\includegraphics[width=120pt]{figure/sol9.eps}}\\
-\end{tabular}
-\caption{Case Study 2: First 8 Linkages in the table~\ref{ex2_knnLinkageData} and their resultant coupler motions.}
-\label{ex2_solns}
-\end{figure}
-
 \section*{Conclusion}
-This approach presents a novel optimization approach towards defect free linkage synthesis.
-The framework is highly data efficient due to similarity invariant representation of paths and motion, which also facilitates partial matching.
-The method always returns defect free solutions as it is inherently taken care of.
-Sensitivity analysis indicates that complexity of the objective function, although obviously multimodal and nonlinear, is not overly complex and certainly well behaved in the singular spaces.
+This approach presents a novel machine-learning approach to generation of conceptual designs of defect-free linkage synthesis.
+The approach is highly data-efficient due to similarity invariant representation of paths and motion, which also facilitates partial matching.
+Sensitivity analysis indicates that complexity of the objective function, although multimodal and nonlinear, is not overly complex and certainly well behaved in the singular spaces.
 Hierarchically clustered database provides efficient query search.
@@
 Although our method can provide highly accurate results, our focus here is to generate high number of defect free solutions that can perform the task in more or less similar fashion;
-because more often than not, linkage synthesis algorithms are desired to be prolific in terms of concept generation than to produce highly accurate very few solutions.
+because more often than not, linkage synthesis algorithms are desired to be prolific in terms of concept generation than to produce highly accurate, but very few solutions.
+The approach is general enough to be extended to higher order linkage systems for which there are even fewer methods available for synthesizing defect-free solutions.
 

### 2018-04-15 idetc2018.tex
Journal version

@@
 %%% use twocolumn and 10pt options with the asme2e format
-\documentclass[twocolumn,10pt]{asme2e}
+\documentclass[twocolumn,10pt]{asme2ej}
 \newcommand{\gbf}[1] {\mbox{\boldmath${#1}$\unboldmath}}
@@
 \def \Shrocker{Schr\ddot{o}cker}
-
-%%% Replace here with information related to your conference
-\confshortname{IDETC/CIE 2018}
-\conffullname{the ASME 2018 International Design Engineering Technical Conferences \&\\
-              Computers and Information in Engineering Conference}
-
-%%%%% for date in a single month, use
-\confdate{26-29}
-\confmonth{August}
-%%%%% for date across two months, use
-\confyear{2018}
-\confcity{Quebec City}
-\confcountry{Canada}
-
-%%% Replace DETC2009/MESA-12345 with the number supplied to you
-%%% by ASME for your paper.
-\papernum{DRAFT: DETC2018-85578}
 
@@
 \begin{equation}\label{objectiveFunPath}
-  \argminA_{\textbf{\emph{l}}, W_i} (1 - Cn_{max}(p, W_i),
+  \argminA_{\textbf{\emph{l}}, W_i} (1 - Cn_{max}(p, W_i)),
 \end{equation}
@@
     & 2)\putindeepbox[7pt]{\includegraphics[width=60pt]{figure/path_solutions/path_sol2.eps}} \\
-  3)\putindeepbox[7pt]{\includegraphics[width=120pt]{figure/path_solutions/path_sol3.eps}}
-    & 4)\putindeepbox[7pt]{\includegraphics[width=120pt]{figure/path_solutions/path_sol4.eps}}\\
-  5)\putindeepbox[7pt]{\includegraphics[width=120pt]{figure/path_solutions/path_sol5.eps}}
-    & 6)\putindeepbox[7pt]{\includegraphics[width=120pt]{figure/path_solutions/path_sol6.eps}} \\
-  7)\putindeepbox[7pt]{\includegraphics[width=120pt]{figure/path_solutions/path_sol7.eps}}
-    & 8)\putindeepbox[7pt]{\includegraphics[width=120pt]{figure/path_solutions/path_sol8.eps}}\\
+  3)\putindeepbox[7pt]{\includegraphics[width=100pt]{figure/path_solutions/path_sol3.eps}}
+    & 4)\putindeepbox[7pt]{\includegraphics[width=100pt]{figure/path_solutions/path_sol4.eps}}\\
+  5)\putindeepbox[7pt]{\includegraphics[width=100pt]{figure/path_solutions/path_sol5.eps}}
+    & 6)\putindeepbox[7pt]{\includegraphics[width=100pt]{figure/path_solutions/path_sol6.eps}} \\
+  7)\putindeepbox[7pt]{\includegraphics[width=100pt]{figure/path_solutions/path_sol7.eps}}
+    & 8)\putindeepbox[7pt]{\includegraphics[width=100pt]{figure/path_solutions/path_sol8.eps}}\\
 \end{tabular}

### 2018-04-25 idetc2018_conf_version.tex
Merging into conference .tex

--- 2018-03-19 idetc2018.tex
@@
 The past forty years of research in mechanism synthesis has witnessed an unprecedented volume of work in formulating and solving planar four-bar linkage synthesis problems.
-However, finding practical and useful mechanisms for the motion synthesis problem has proven to be elusive as a large majority of mechanisms turn out to be defective with respect to their assembly modes.
-Most methods formulate the problem as a discrete precision position problem, which inherently ignores the continuity information in the input, resulting into linkages with branch-, circuit- and order-defects.
+However, finding practical and useful mechanisms for the motion synthesis problem has proven to be elusive, as a large majority of mechanisms turn out to be defective with respect to their assembly modes.
+Most methods formulate the problem as a discrete precision position problem, which inherently ignores the continuity information in the input, resulting in linkages with branch-, circuit- and order-defects.
 In this paper, we bring together diverse fields of pattern recognition, machine learning, artificial neural network, and computational kinematics to present a novel approach that solves this problem both efficiently and effectively.
 At the heart of this approach lies an objective function that compares the motion as a whole thereby capturing designer's intent.
-In contrast to widely used structural error or loop-closure equation based error functions which convolute the optimization by considering shape, size, position and orientation simultaneously, this objective function computes motion difference in a form invariant to similarity transformations.
+In contrast to widely used structural error or loop-closure equation based error functions which convolute the optimization by considering shape, size, position, and orientation simultaneously, this objective function computes motion difference in a form, which is invariant to similarity transformations.
 We employ auto-encoder neural networks to create a compact and clustered database of invariant motions of known linkages.
 The query is raised in the database for nearest neighbors, which are either solutions or good initial conditions for fast local optimization techniques.
-In spite of highly non-linear parameters space, our approach discovers a wide pool of defect free solutions very quickly.
+In spite of highly non-linear parameters space, our approach discovers a wide pool of defect-free solutions very quickly.
 We show that by employing proven machine learning techniques, this work could have far-reaching consequences to creating a multitude of useful and creative conceptual design solutions for mechanism synthesis problems, which go beyond planar four-bar linkages.
 
-\textbf{keywords}: \emph{Machine Learning, Artificial Neural Network (ANN), Path Synthesis, Motion Synthesis, Planar Four-bar linkage, Type and Dimensional Synthesis, Circuit- Order-, and Branch-Defect}
+\textbf{keywords}: \emph{Machine Learning, Artificial Neural Network (ANN), Path Synthesis, Motion Synthesis, Planar Four-bar linkage, Circuit- Order-, and Branch-Defect}
 
@@
 \section{Introduction}
-Classical mechanism synthesis problem deals with computing type and dimensions of linkage system for performing specific tasks, which are categorized as path, motion and function generation; for an exhaustive reference see  books from such McCarthy and Soh \cite{sohmccarthy}, Sandor and Erdman~\cite{Sandor}, Hunt \cite{Hunt78}, Hartenberg and Denavit \cite{Hartenberg},  Suh and Radcliffe \cite{Suh78}, and Lohse \cite{lohse2013}.
-Various approaches have been proposed in the literature with the aim of finding acceptable solutions for practical situations.
-However, the majority of the approaches do not account for circuit and branch defect in the synthesis process, which can render the solution useless for practical applications.These defects in single degree of freedom mechanisms are thoroughly discussed by Chase and Mirth\cite{chasemirth}.
+Classical mechanism synthesis problem deals with computing type and dimensions of linkage system for performing specific tasks, which are categorized as path, motion and function generation; for an exhaustive reference, see books from McCarthy and Soh \cite{sohmccarthy}, Sandor and Erdman~\cite{Sandor}, Hunt \cite{Hunt78}, Hartenberg and Denavit \cite{Hartenberg},  Suh and Radcliffe \cite{Suh78}, and Lohse \cite{lohse2013}.
+Various approaches have been proposed in the literature with aim of finding acceptable solutions for practical situations.
+However, the majority of the approaches do not account for circuit and branch defect in the synthesis process, which can render the solution useless for practical applications.
+These defects in the single degree of freedom mechanisms are thoroughly discussed by Chase and Mirth\cite{chasemirth}.
 
@@
 
-In this paper, we 1) employ pattern recognition and computational shape analysis to create a similarity transforms-independent signature for the path and motion, 2) exploit the non-linear nature of relationship between the linkage parameters and the coupler motions to create a sensitive, wide-ranging, compact, and efficient database with hierarchical clustering, and 3) enable dimensionality reduction using Auto-encoder Neural Networks.
+In this paper, we 1) employ pattern recognition and computational shape analysis, to create a similarity transforms-independent signature for coupler path and motion, 2) exploit the non-linear nature of relationship between the linkage parameters and coupler motions to create a sensitive, wide-ranging, compact, and efficient database with hierarchical clustering, and 3) enable dimensionality reduction using Auto-encoder Neural Networks.
 When a user inputs a motion or a path, a query representing invariant signature \footnote{path or motion signature} of the input is raised for $k$ nearest neighbors among cluster centers in the database.
-The neighbor is defined as motion or path whose part has a similar signature to the input.
-These $k$ neighbors, if needed, are subjected to fine tuning by local optimization to obtain set of defect-free solutions.
-We define a novel objective function for defect-free motion generation problems and a novel algorithm for partial matching of motions.
+These $k$ neighbors, if needed, are subjected to fine-tuning by local optimization to obtain a set of defect-free solutions.
+We define a novel objective function for defect-free motion generation problems and present an algorithm for partial matching of motions.
 The objective function that drives the synthesis process computes a distance measure of dissimilarity between the task motion and the coupler motion generated by current linkage parameters.
-This distance measure of dissimilarity inherently requires continuity of motion, thus ensuring that the output mechanism is defect free throughout the task.
+This distance measure of dissimilarity inherently requires continuity of motion, thus ensuring that the output mechanism is defect-free throughout the task.
 The Fig.~\ref{overallMethod} illustrates an overview of our method, which is codified in Algorithm~\ref{alg_overall}.
 
-Path synthesis methods based on Fourier analysis do take the continuity information of the coupler path into account; however most of them are defined only for closed loop curves.
-Ullah and Kota\cite{ullah1997} have presented an invariant approach towards representation and synthesis of closed paths through shape optimization.
-They use a combination of global and local search methods by optimizing Fourier Deviant function to compute the dimensions of planar four bar linkages without any initial guesses.
+Path synthesis methods based on Fourier analysis do take continuity information of the coupler path into account, however, most of them are defined only for closed loop curves.
+Ullah and Kota\cite{ullah1997} have presented an invariant approach towards representation and synthesis of closed loop paths through shape optimization.
+They use a combination of global and local search methods for optimizing Fourier Deviant function, to compute the dimensions of planar four-bar linkages without an initial guess.
 Wu et al.\cite{wu2011} presented a method for open and closed path generation based on finite Fourier series.
-In the case of motion generation, methods that take the branching defect into consideration limit their search in the configuration space where Grashof condition holds true.
-To the best of our knowledge, no motion generation methods truly take the motion continuity into account.
+In the case of motion generation, Li et al.\cite{li2016} have developed a Fourier descriptor-based approach for approximate motion generation.
 
-Due to the highly nonlinear nature of the problem, most optimization based methods require a good initial condition to start.
+Due to highly nonlinear nature of the problem, most optimization based methods require a good initial condition to start.
 Thus, an atlas or a design library is used to provide good initial conditions.
-McGarva\cite{mcgarva1994} took the earliest approach towards creating a library for coupler trajectories based on harmonic analysis.
-Wandling\cite{wandling2000} has presented an atlas based approach, where coupler paths and motions are stored in terms of Fourier Transforms.
+McGarva\cite{mcgarva1994} took the earliest approach towards creating a library for coupler trajectories based on a harmonic analysis.
+Wandling\cite{wandling2000} has presented an atlas-based approach, where coupler paths and motions are stored in terms of Fourier Transforms.
 Input motion is searched for neighbors based on Euclidean distances of Fourier Transforms.
@@
 In their approach, a task curve is transformed into normalized Fourier coefficients and queried for the nearest neighbor search.
-The best match is returned as a solution to input.
-Chu et al.\cite{chu2010} presented an atlas based method for synthesizing spatial four bar linkages for function generation problems where orientation data is stored in terms of Fourier descriptors.
+The best match is returned as the solution to input.
+Chu et al.\cite{chu2010} presented an atlas-based method for synthesizing spatial four-bar linkages for function generation problems, where orientation data is stored in terms of Fourier descriptors.
 
 The above methods generate data based on uniform sampling in the linkage parameter space.
-Given the highly nonlinear mapping between linkage parameters and coupler trajectory, this way of sampling leads to non-uniform sampling of trajectory space causing under-representation of possible motions.
+Given highly nonlinear mapping between linkage parameters and coupler trajectory, this way of sampling leads to a non-uniform sampling of trajectory space causing under-representation of possible motions.
 We address this issue by employing log-normal distribution in the linkage parameter space to generate data and perform compact clustering of the data using machine learning techniques.
-A hierarchy is created in the database by means of clustering, where the top level comprises of data points called cluster centers, which are representative of the cluster points in the lower levels.
+Hierarchy is created in the database by means of clustering, where the top level comprises of data points called cluster centers, which are representative of the cluster points in lower levels.
 Wandling~\cite{wandling2000} and Yu et al.~\cite{yue-pathgen2011} have built libraries with all possible coupler curves, where one curve is broken down into many segments for creating data for partial curves.
 In contrast to this, we need to store only one curve representing all the segments in it as our representation facilitates partial matching.
-No other previous methods facilitate this partial matching of open motion curve into another open or closed curve. This reduces the data requirement even further.
+None of the other previous methods facilitate this partial matching of open motion curve into another open or closed curve, which significantly contributes to providing a large number of solutions, and reduces the data requirement even further.
 
 Rest of this paper is organized as follows. Section~\ref{sec_sign} presents the computation of motion and path signatures.
-Section~\ref{sec_distanceMetric} is comprised of evaluation criterion for two signatures based on the shape similarity, which leads to a formulation of the error function for optimization.
+Section~\ref{sec_distanceMetric} is comprised of evaluation criterion for signatures based on the shape similarity, which leads to the formulation of error function for optimization.
 Section~\ref{sec_SA} discusses the nature of objective function via sensitivity analysis at a singularity.
@@
 \section{Signatures of Coupler Path and Motion}\label{sec_sign}
-The focus of the paper is on a novel method for motion generation that takes a continuous task motion or path as the input and returns defect-free linkages producing similar motion or path.
-The objective function evaluation requires the input motion to be transformed into a specific form, which we call the signature of input motion.
-This signature representation should be invariant to similarity operations, viz. reflection, rotation, translation and scaling.
+Focus of the paper is on a novel method for motion generation that takes a parametric motion $(x:x(t), y:y(t), \theta:\theta(t))$ or path $(x:x(t), y:y(t))$ as the input and returns defect-free linkages producing similar motion or path.
+The input is transformed into a representation, termed as a signature, which is invariant to similarity operations, viz. reflection, rotation, translation, and scaling.
 Signatures for path and motion are termed as path signature and motion signature, respectively.
 For calculating path signature, we use formulations developed by Cui et.al\cite{cui2009}.
-For this task, our approach requires the input in terms of a parametric motion $(x:x(t), y:y(t), \theta:\theta(t))$.
 
-Curvature $k(t)$ of the path of a parametric motion $(x:x(t), y:y(t), \theta:\theta(t))$ and its integral $K(t)$ is given by,
+Consider a motion given in parametric form as, $x:x(t), y:y(t), \theta:\theta(t)$.
+Here, $\theta(t)$ represents the change in orientation along the path, measured with respect to initial orientation and is not restricted in the domain $[-\pi, \pi]$.
+
+Curvature $\kappa(t)$ of the path $(x:x(t), y:y(t))$ and its integral $K(t)$ is given by,
 \begin{eqnarray}
-  k(t) = \frac{\ddot{y}(t)\dot{x}(t) - \ddot{x}(t)\dot{y}(t)}{{(\dot{x}^2(t) + \dot{y}^2(t))}^{(\frac 32)}}, \label{curvatureEq}\\
-  K(t) = \int^{t}_0 |k(t)|dt \label{kInt},
+  \kappa(t) = \frac{\ddot{y}(t)\dot{x}(t) - \ddot{x}(t)\dot{y}(t)}{{(\dot{x}^2(t) + \dot{y}^2(t))}^{(\frac 32)}}, \label{curvatureEq}\\
+  K(t) = \int^{t}_0 |\kappa(t)|dt \label{kInt},
 \end{eqnarray}
-where $\dot{x}$, $\ddot{x}(t)$ are first and second order derivative with respect to parameter $t$.
-As an example, the parametric motion could be a B-spline motion as shown in Fig~\ref{bsplineFitting} or it could be a discrete set of poses, which could be represented by a continuous signal using Fourier series.
-We compute the curvature of path along the direction of $t$, using Eq.~\req{curvatureEq} and the cumulative integral by Eq.~\req{kInt}.
+where $\dot{x}(t)$, $\ddot{x}(t)$ are first and second order derivative with respect to parameter $t$.
+As an example, the parametric motion could be a B-spline motion as shown in Fig~\ref{bsplineFitting}.
+We compute $\kappa(t)$ and $K(t)$ along the direction of $t$, using Eq.~\req{curvatureEq} and Eq.~\req{kInt} respectively.
 Figure~\ref{curvatureK} shows computed curvature and its unsigned integral of the coupler path shown in Fig.~\ref{bsplineFitting}.
-It can be seen that curvature is small start, increases as the curve bends along the path and drops once again as the path straightens out.
+It can be seen that curvature is small at the start, increases as the curve bends along the path and drops once again as the path straightens out.
 It is obvious that curvature plot will reverse if the direction of parameterizations reverses, while the integral is a monotonically increasing function.
@@
 
-Now, we re-sample the curvature at equal intervals of $K(t)$, which is equivalent to plotting $k$ vs $K$ in Fig~\ref{signature}(a).
+Now, we re-sample the curvature at equal intervals of $K(t)$, which is equivalent to plotting $\kappa$ vs $K$ in Fig~\ref{signature}(a).
 This is done by finding the parameter values of $t$ where $K$ changes uniformly.
-For practical purposes, we find an array of parameter $t$ such that $K$ increments by 0.1.
-For each value of $t$ in the array, we compute $k(K)$ and $\theta(K)$ and store it as the path and motion signatures respectively. We note that there is a one-to-one mapping between $t$ and $K$.
+For practical purposes, we find an array of the parameter $t$ such that $K$ increments by 0.1.
+For each value of $t$ in that array, we compute $\kappa(K)$ and $\theta(K)$ and store it as the path and motion signatures respectively.
+We note that there is a one-to-one mapping between $t$ and $K$.
 
 These signatures are invariant under similarity transformations; for proof see\cite{cui2009}.
-We know that curvature changes inversely to the scale of the curve, so when it is integrated along the scaled curve, the scale factor cancels itself out.
-Reflection operation on the motion or the path, produces flipped path signature, but motion signature remains invariant.
-
+We know that curvature changes inversely to scale of the curve, so when it is integrated along the scaled curve, the scale factor cancels itself out.
+Reflection operation produces flipped path signature, but motion signature remains invariant.
 Figure~\ref{signature} shows path and motion signature obtained for the motion depicted in Fig.~\ref{bsplineFitting}.
-It is important to note that signature depends on the direction along which we compute the curvature $k(t)$ as well as re-sample $\theta(t)$.
+It is important to note, that the signature depends on the direction of parameter t, as shown in Fig~\ref{bsplineFitting}.
+The procedure of signature calculation presented in this section is given in Algorithm ~\ref{alg_signature}.
 
@@
 
-The procedure of signature calculation presented in this section is given in Algorithm ~\ref{alg_signature}.
-
 \begin{algorithm}
@@
     \Output{signature //discretized signal in form of an array}
-    $k(t)$ = ComputeCurvature$(x, y)$ using Eq.~\ref{curvatureEq} \\
-    $K(t)$ = IntergrateCumulatively($k(t)$) using Eq.~\ref{kInt} \\
+    $\kappa(t)$ = ComputeCurvature$(x, y)$ using Eq.~\ref{curvatureEq} \\
+    $K(t)$ = IntergrateCumulatively($\kappa(t)$) using Eq.~\ref{kInt} \\
     motionSignature = [] \\
@@
       $i = i + 0.1$ \\
-      motionSignature.push($k$($tmp$)) \\
-      pathSignature.push($k$($tmp$))
+      motionSignature.push($\kappa$($tmp$)) \\
+      pathSignature.push($\kappa$($tmp$))
     }
@@
 \section{Signature Matching and Error Function}\label{sec_distanceMetric}
-The signatures obtained in the previous steps contain important information about shape of the trajectory.
-In this section, we formulate functions that evaluate the similarity (or, distance) between two trajectories based on their signatures.
+The signatures obtained in previous steps contain important information about the shape of the trajectory.
+In this section, we formulate functions that evaluate the similarity between two trajectories based on their signatures.
 These distance functions can be used as error metric, which can be minimized using optimization methods.
@@
 \subsection{Partial Matching of Path Signatures}\label{sec_ncc}
-When a path query is raised, it can be very useful to know whether this path already exists as a part in some other path present in the database.
+When a path query is raised, it can be very useful to know whether this path matches with the part of a path from the database.
 This subsection presents a method for determining this partial similarity.
 
-Let us consider two coupler paths; namely part and whole as shown in~\ref{wholePart}.
-Let $p$ be path signature of the part path which acts as a template, while $W$ is path signature of the whole path that can completely embed the template as shown in Fig.~\ref{pathSignature}.
-The orientation information shown in Fig.~\ref{wholePart} is ignored for path matching.
-It will be used later for matching of motion signature.
+Let us consider two coupler paths; namely \emph{Part} and \emph{Whole} as shown in~\ref{wholePart}.
+Let $p$ and $W$ be their signatures respectively, where $W$ completely contains $p$ as shown in Fig.~\ref{pathSignature}.
+The orientation information shown in Fig.~\ref{wholePart} is ignored for path matching. It will be used later for matching of motion signatures.
 The partial matching works as follows:
@@
   \item $p$ and $W$ are expressed in terms of arrays and $W$ must contain more points than $p$.
-  \item The template $p$ is slid with offset index $j$ along $W$.
-  \item For each offset $j$, we compute normalized cross-correlation function given by,
+  \item $p$ is slid with offset index $j$ along $W$.
+  \item For each offset $j$, we compute normalized cross-correlation\cite{lewis1995fast} function given by,
 \end{enumerate}
@@
 \begin{equation}\label{nccEq}
-  Cn(j, p, W) = |\sum_{i}^{p_{span}} \frac{(W(i+j) - \bar{W}(j\to j + p_{span}))(p(i) - \bar{p})}{\sqrt{\sum_{i}^{p_{span}}{(W(i+j) - \bar{W}_{p_{span}})}^2\sum_{i}^{p_{span}}{(p(i) - \bar{p})}^2}} |,
+  Cn(j, p, W) = |\sum_{i}^{p_{span}} \frac{(W(i+j) - \bar{W}(j : j + p_{span}))(p(i) - \bar{p})}{\sqrt{\sum_{i}^{p_{span}}{(W(i+j) - \bar{W}_{p_{span}})}^2\sum_{i}^{p_{span}}{(p(i) - \bar{p})}^2}} |,
 \end{equation}
-where $Cn(j, p, W)$ is the normalized cross-correlation value when template $p$ is matched against $W$ at $j^{th}$ index; $p_{span}$ is the length of the array $p$ and $\bar{W}(j\to j + p_{span})$ is the mean for the values of array $W$ between index range of ($j, j+p_{span}$).
+where $Cn(j, p, W)$ is the normalized cross-correlation value when $p$ is matched against $W$ at $j^{th}$ index; $p_{span}$ is length of the array $p$ and $\bar{W}(j:j + p_{span})$ is mean of the values of array $W$ between index range of ($j, j+p_{span}$).
 
-Here, $p$ acts as a template that tries to find best match against $W$ while sliding over it along $j$.
-Domain of $Cn(j, p, W)$ is [0, 1], where 1 represents the complete embedment.
+Here, $p$ acts as a template that tries to find the best match against $W$ while sliding over it along $j$.
+Domain of $Cn(j, p, W)$ is [0, 1], where 1 represents the complete embedment of $p$ inside $W$.
 
-Maximum score of the matching $Cn_{max}(p, W)$ represents similarity of the template in $W$, and offset index $j$ at which maximum occurs is the start point for matching.
-As the signature reverses with reversal of the direction of sampling, we compute the correlation first in one direction and again after reversing $p$ and select the best matching score, offset index and the matching direction of sampling.
-Figure~\ref{ncc} depicts normalized cross correlation function over the sliding domain $j$ for part and whole curves.
+The maximum score of the matching $Cn_{max}(p, W)$ represents similarity of the template in $W$, and offset index $j$ at which maximum occurs is the start point for matching.
+As we know that the signature reverses with reversal of the direction of $t$, we compute the correlation along both directions and select the best matching score, offset index and the matching direction of sampling.
+Figure~\ref{ncc} depicts normalized cross correlation function over the sliding domain $j$ for \emph{Part} and \emph{Whole} curves.
 
@@
 The array index $i$ corresponds to the index location for the array of the $K$.
-The domain of path signature is scale invariant but the range still has a scaling factor, which is taken care of by normalized cross-correlation.}
+The domain of path signature is scale-invariant but the range still has a scaling factor, which is taken care of by normalized cross-correlation.}
 \label{pathSignature}
@@
 This section presents how a template motion can be checked against other motion for potential matching.
-Consider part and whole motions shown in Fig.~\ref{wholePart}.
-Let $p$ and $W$ be the motion signatures of part and whole motions, respectively as shown in Fig.~\ref{motionSignature}.
-Similar to the partial matching of path signature, the cross-correlation function is given by,
+Consider \emph{Part} and \emph{Whole} motions shown in Fig.~\ref{wholePart}.
+Let $p$ and $W$ be the motion signatures of the \emph{Part} and \emph{Whole} motions, respectively as shown in Fig.~\ref{motionSignature}.
+Similar to partial matching of path signatures, the cross-correlation function is given by,
 
 \begin{equation}\label{mccEq}
-  E(j, p, W) = \sum_{i}^{p_{span}} {((W(i+j) - \bar{W}(j\to j + p_{span})) - (p(i) - \bar{p}))}^2,
+  E(j, p, W) = \sum_{i}^{p_{span}} {((W(i+j) - \bar{W}(j: j + p_{span})) - (p(i) - \bar{p}))}^2,
 \end{equation}
-where $E(j, p, W)$ is the dissimilarity value when template $p$ is matched to $W$ at $j^{th}$ index. Here $p$ tries to find best match against $W(i)$ while sliding over it.
-Similar to path signature, motion signature is dependent on the sampling direction along the motion.
-Thus, we compute the dissimilarity for both direction and choose whichever is the least i.e.
-$E_{min}(p, W)$.
+where $E(j, p, W)$ is the dissimilarity value when template $p$ is matched to $W$ at $j^{th}$ index. Here $p$ tries to find the best match against $W(i)$ while sliding over it.
+Similar to path signature, motion signature is dependent on the direction of $t$. Thus, we compute the dissimilarity for both directions and choose whichever is the least i.e. $E_{min}(p, W)$.
 Figure~\ref{mcc} depicts dissimilarity function over the sliding domain $j$.
-In this case, as shown in Fig.~\ref{mcc}, we find that the first point itself is a point where the perfect match occurs, which is consistent with the fact that we have essentially sliced the whole motion to obtain the part motion.
+In this case, as shown in Fig.~\ref{mcc}, we find that the first point is the matching point, which is consistent with the fact that we have essentially sliced the whole motion to obtain the part motion.
 
@@
 \includegraphics[width=240pt]{figure/fig_mcc.eps}
-  \caption{Dissimilarity function of two motion signatures along both directions. It can be seen that exact match is found at $j=0$, where template is fully embedded inside the other motion.}
+  \caption{Dissimilarity function of two motion signatures along both directions. It can be seen that exact match is found at $j=0$, where the template is fully embedded inside the other motion.}
 \label{mcc}
@@
 \subsection{Objective Function for Synthesis}
-The functions in Eq.~\req{nccEq} and ~\req{mccEq} presented in the sections \ref{sec_ncc}, \ref{sec_mcc} can be used as the error measure for path and motion synthesis of any planar linkage, where the objective is to find a linkage that produces a motion whose part or whole corresponds to target motion (or path).
+The functions in Eq.~\req{nccEq} and ~\req{mccEq} presented in the sections \ref{sec_ncc}, \ref{sec_mcc} can be used as the error measure for path and motion synthesis of any planar linkage, where the objective is to find a linkage that produces a motion whose part or whole corresponds to the target motion (or path).
 Thus we can formulate the path synthesis problem as,
@@
   \caption{Parametric representation of four-bar linkage with all revolute joints.
-We set $l_0 = 1$ and one fixed joint at origin of the global frame along with making fixed length of the four bar parallel to x axis.}
+We set $l_0 = 1$ and one fixed joint at the origin of the global frame along with making the fixed length of four-bar parallel to the x-axis.}
 \label{fourbar}
@@
 Objective function evaluation step consists of calculation of coupler motion or path and finding its dissimilarity score.
-It is important to note that representation obtained in Section~\ref{sec_sign} reduces size of the linkage parameters in optimization.
+It is important to note that representation obtained in Section~\ref{sec_sign} reduces the size of the linkage parameters in optimization.
 This optimization problem can be solved using search methods which do not require gradient computation.
-We can employ global optimization methods such as differential evolution at the start and local optimization methods link Powell's method towards the end for faster convergence\cite{ullah1997}.
+We can employ global optimization methods such as differential evolution at the start, and local optimization methods link Powell's method towards the end for faster convergence\cite{ullah1997}.
 %Section~\ref{examples} presents results for the optimization technique used.
@@
 Due to the complex relationship between parameter space and generated motion, small changes in linkage parameters can produce large and discontinuous structural changes in the generated motions.
-For example, a small change in crank length ($l_1$) can open a previously close coupler path.
-Most of the methods based on Fourier descriptors can not capture the continuity at such singular locations, which adversely affect the optimization process.
-In contrast to this behavior, the signatures derived in Sec.~\ref{sec_sign} have smooth transition at these singular locations due to shape similarity between a closed and just opened curve or motion.
+For example, a small change in crank length ($l_1$) can open a previously closed coupler path.
+Most of the methods based on Fourier descriptors cannot capture the continuity at such singular locations, which adversely affect the optimization process.
+In contrast to this behavior, the signatures derived in Sec.~\ref{sec_sign} have a smooth transition at these singular locations due to shape similarity between closed and just opened curve or motion.
 
-To illustrate this, we perform sensitivity analysis in the vicinity of a singularity as follows:
+To illustrate this, we perform sensitivity analysis in the vicinity of the singularity as follows:
 A four-bar with link ratios ($l_1:0.55$, $l_2:1$, $l_3:1.5$, $l_4:1$, $l_5:1$) is subjected to gradual change in parameters $l_1$ and $l_3$ by the amount (-0.2, 0.2) in steps of 0.01.
-Error function between motions of new and initial four bar are calculated using Eq.~\req{objectiveFunMotion} .
+Error function between motions of new and initial four-bar are calculated using Eq.~\req{objectiveFunMotion} .
 Figure~\ref{saCouplerCurves} shows coupler motion of some of the four-bars while Fig.~\ref{saMotionSignatures} depicts their motion signatures.
 Please note that these two figures show the effect of changing only one parameter $l_1$.
-It can be seen from Fig.~\ref{saCouplerCurves} that there exists a discontinuity in topology of the coupler curves even though their shapes have a continuous shift.
+It can be seen from Fig.~\ref{saCouplerCurves} that there exists a discontinuity in the topology of coupler curves even though their shapes have a continuous shift.
 Our method captures this continuity, which is shown by error function evaluations depicted in Fig.~\ref{saErrorFunction}, where it is visible that surface is well behaved in the singularity region.
@@
 \includegraphics[width=240pt]{figure/fig_sa_coupler_curves.eps}
-  \caption{Coupler Motions of the four bar linkage with variation of parameters $l_1$ and $l_2$. It can be seen that motion topology changes from close-loop Grashof to open loop Triple-Rocker.}
+  \caption{Coupler Motions of the four-bar linkage with variation of parameters $l_1$ and $l_2$. It can be seen that motion topology changes from close-loop Grashof to open loop Triple-Rocker.}
 \label{saCouplerCurves}
@@
 \section{Clustered Database of Planar Linkages}\label{sec_db_ae}
-Having an invariant representation facilitating partial matching greatly reduces data required to sample all possible types shapes of coupler motion.
+Having an invariant representation facilitating partial matching greatly reduces data required to sample all possible types of shapes of coupler motion.
 We have built a database of planar four-bar linkages with revolute joints as an example, but the approach is same for any planar motion generating machine.
-We generate this database comprising of $40,000$ linkages, while taking following aspects into consideration.
+We generate this database comprising of $40,000$ linkages while taking following aspects into consideration.
 \begin{enumerate}
@@
 Figure~\ref{fourbar} represents parametric representation of four-bar linkage with parameters ($l_1,l_2,l_3,l_4,l_5$).
-As mapping between four-bar linkage parameter space and coupler motion space is highly non-linear, uniform distribution over linkage parameter space does not necessarily mean uniform sampling over motion space.
+As mapping between four-bar linkage parameter space and coupler motion space is highly non-linear, uniform distribution over linkage parameter space does not necessarily mean uniform sampling over coupler motion space.
 Thus, an efficient approach would be to sample more in the regions where sensitivity is maximum.
-We have observed that whenever the link ratios of four-bar linkage are close to 1, the sensitivity of the shape of a coupler motion is higher than otherwise.
+We have observed that whenever the link ratios of four-bar linkage are close to 1, the sensitivity of shape of a coupler motion is higher than otherwise.
 Thus, we have chosen Log-Normal probability distribution ($\mu = 0,\sigma = 0.6 $) for selecting the link ratios : $(l_1, l_2, l_3)$ as shown in Fig.~\ref{logNormal}, and Normal Distribution ($\mu = 0,\sigma = 2 $) for $(l_4, l_5)$.
@@
 \subsection{Dimensionality Reduction using Auto-Encoders}
-Each data point in database consists of discrete signature of motion, which is kept to be of 100 float digits.
+Each data point in the database consists of discrete signature, which is kept to be of 100 float digits.
 In order to have efficient query operations, we perform Hierarchical Clustering; a method that summarizes and creates a hierarchy in the database.
@@
 Auto-encoders are trained to reconstruct the input, in this way each layer encodes the input, which is sufficient for the next layers to reconstruct the output.
-Objective of the training is to find out set of weights and biases that minimizes the error loss given by,
+The objective of training is to find out the set of weights and biases that minimizes the error loss given by,
 
@@
 
-Once a network is trained, output of the bottle-neck layer $(h_{ib})$ represents the compressed feature space ($Z$).
-As the bottleneck layer has 10 neurons and input is 100 dimensional vector, it is evident that information is compressed by a factor of 10, while achieving $95\%$ reconstruction accuracy as a result of training.
+Once a network is trained, the output of the bottle-neck layer $(h_{ib})$ represents the compressed feature space ($Z$).
+As bottleneck layer has 10 neurons and input is a 100-dimensional vector, it is evident that information is compressed by a factor of 10, while achieving $95\%$ reconstruction accuracy as the result of training.
 Standard clustering algorithms are performed on this latent\footnote{compressed output of bottleneck layer.} space for better clustering\cite{song2013}.
@@
 The distance metric used is the Euclidean distance in the latent space.
-Although the more accurate distance metric is distance function discussed in sec.~\ref{sec_distanceMetric}, it is very expensive to calculate it for entire database.
-Signatures with ${O}(m)$ points, take ${O}(m\log{}m)$ time for each comparisons and there are ${O}(N^2)$ number of comparisons to be made for database of $N$ points.
+Although the more accurate distance metric is distance function discussed in sec.~\ref{sec_distanceMetric}, it is very expensive to calculate it for the entire database.
+Signatures with ${O}(m)$ points take ${O}(m\log{}m)$ time for each comparison and there are ${O}(N^2)$ number of comparisons to be made for the database of $N$ points.
 When user raises one such query, we first find $k$ nearest neighbors among $1500$ cluster centers, then descend into their clusters if needed.
@@
 \includegraphics[width=270pt]{figure/fig_auto_encoder.eps}
-  \caption{A small scale version of the Auto-Encoder.
-This network takes 5 dimensional input in the input layer.
-At each encoder layer, input is compressed into vector of lesser dimensions, lowest at the bottleneck layer.}
+  \caption{A small-scale version of the Auto-Encoder.
+This network takes 5-dimensional input in the input layer.
+At each encoder layer, the input is compressed into a vector of lesser dimensions, lowest at the bottleneck layer.}
 \label{autoEncoder}
@@
 \section{Case Studies}\label{sec_example}
-This sections presents two case studies presenting the effectiveness of our approach for path and motion synthesis applications.
+This section presents two case studies presenting the effectiveness of our approach for path and motion synthesis applications.
 \subsection{Path Generation}
-In the design phase of a rehabilitation device that assists people stand from sitting position, it is required to generate linkages that can execute a sit-to-stand (STS) trajectory of the hip joint as shown in Fig.~\ref{ex1_path}.
+In the design phase of a rehabilitation device that assists people to stand from sitting position, it is required to generate linkages that can execute a sit-to-stand (STS) trajectory of the hip joint as shown in Fig.~\ref{ex1_path}.
 Table~\ref{hipPathTab} presents the discretized path data.
@@
 Table~\ref{ex1_knnLinkageData} tabulates the link ratios corresponding to obtained nine nearest neighbors.
-Next step is to compute actual parameters according to position, scale and orientation of the path.
+Next step is to compute actual parameters according to position, scale, and orientation of the path.
 It is done by comparing analogous points found by offset index $j$ in Eq.~\ref{nccEq}.
-Figure ~\ref{ex1_solns} shows first eight four bar mechanisms corresponding to nearest signatures to path signature of input.
+Figure ~\ref{ex1_solns} shows first eight four-bar mechanisms corresponding to nearest signatures to path signature of input.
 It can be clearly seen that these linkages generate highly accurate paths for the sit to stand activity.
@@
 \begin{tabular}{cc}
-  1)\putindeepbox[7pt]{\includegraphics[width=100pt]{figure/path_solutions/path_sol1.eps}}
+  1)\putindeepbox[7pt]{\includegraphics[width=120pt]{figure/path_solutions/path_sol1.eps}}
     & 2)\putindeepbox[7pt]{\includegraphics[width=60pt]{figure/path_solutions/path_sol2.eps}} \\
@@
 The task is to find a pool of linkage systems that can perform snow-shoveling with a motion shown in Fig.~\ref{motionQuery}.
-The motion data is tabulated in Table ~\ref{poseData} to which we fit a B-spline with cord length parametrization in order to get parametric representation of motion.
+The motion data is tabulated in Table ~\ref{poseData} to which we fit a B-spline with cord length parametrization in order to get the parametric representation of motion.
 The task can also be treated as a finite position motion generation and solved for valid solutions.
-We try with our real time computational methods of algebraic fitting\cite{generalfitting-JCISE},\cite{deshpande2017} but obtained solutions suffer from circuit defect, which is not surprising as those methods do not account for continuity of the input positions.
+We try with our real-time computational methods of algebraic fitting\cite{generalfitting-JCISE},\cite{shrinathpurwar2017} but obtained solutions suffer from circuit defect, which is not surprising as those methods do not account for the continuity of input positions.
 
 Now we employ the approach presented in this paper.
-First step is to calculate motion signature of the task motion using steps mentioned in Algorithm ~\ref{alg_signature}.
-For that we follow the steps given in section~\ref{sec_sign} to obtain the motion signature depicted in Fig.~\ref{queryResult}.
-Next we raise the signature query for nearest signatures among the cluster centers of the database.
+The first step is to calculate motion signature of the task motion using steps mentioned in Algorithm ~\ref{alg_signature}.
+For that, we follow the steps given in section~\ref{sec_sign} to obtain the motion signature depicted in Fig.~\ref{queryResult}.
+Next, we raise the signature query for nearest signatures among cluster centers of the database.
 Fig.~\ref{queryResult} shows nine nearest neighbor signatures along with the task signature.
@@
 Sensitivity analysis indicates that complexity of the objective function, although multimodal and nonlinear, is not overly complex and certainly well behaved in the singular spaces.
-Hierarchically clustered database provides efficient query search.
-Finally, the effectiveness of presented approach is showcased by two case studies for each of which nine defect free solutions were found.
-Although our method can provide highly accurate results, our focus here is to generate high number of defect free solutions that can perform the task in more or less similar fashion;
+The hierarchically clustered database provides efficient query search.
+Finally, the effectiveness of the presented approach is showcased by two case studies for each of which nine defect-free solutions were found.
+Although our method can provide highly accurate results, our focus here is to generate a high number of defect-free solutions that can perform the task in more or less similar fashion;
 because more often than not, linkage synthesis algorithms are desired to be prolific in terms of concept generation than to produce highly accurate, but very few solutions.
@@
 \bibliography{References}
-\newpage
-\clearpage
-\listoftables
-\listoffigures
 

### 2018-04-25 idetc2018_journal.tex
Merging into conference .tex

--- 2018-04-25 idetc2018_conf_version.tex
@@
 \begin{tabular}{cc}
-  1)\putindeepbox[7pt]{\includegraphics[width=120pt]{figure/path_solutions/path_sol1.eps}}
+  1)\putindeepbox[7pt]{\includegraphics[width=100pt]{figure/path_solutions/path_sol1.eps}}
     & 2)\putindeepbox[7pt]{\includegraphics[width=60pt]{figure/path_solutions/path_sol2.eps}} \\
-  3)\putindeepbox[7pt]{\includegraphics[width=120pt]{figure/path_solutions/path_sol3.eps}}
-    & 4)\putindeepbox[7pt]{\includegraphics[width=120pt]{figure/path_solutions/path_sol4.eps}}\\
-  5)\putindeepbox[7pt]{\includegraphics[width=120pt]{figure/path_solutions/path_sol5.eps}}
-    & 6)\putindeepbox[7pt]{\includegraphics[width=120pt]{figure/path_solutions/path_sol6.eps}} \\
-  7)\putindeepbox[7pt]{\includegraphics[width=120pt]{figure/path_solutions/path_sol7.eps}}
-    & 8)\putindeepbox[7pt]{\includegraphics[width=120pt]{figure/path_solutions/path_sol8.eps}}\\
+  3)\putindeepbox[7pt]{\includegraphics[width=100pt]{figure/path_solutions/path_sol3.eps}}
+    & 4)\putindeepbox[7pt]{\includegraphics[width=100pt]{figure/path_solutions/path_sol4.eps}}\\
+  5)\putindeepbox[7pt]{\includegraphics[width=100pt]{figure/path_solutions/path_sol5.eps}}
+    & 6)\putindeepbox[7pt]{\includegraphics[width=100pt]{figure/path_solutions/path_sol6.eps}} \\
+  7)\putindeepbox[7pt]{\includegraphics[width=100pt]{figure/path_solutions/path_sol7.eps}}
+    & 8)\putindeepbox[7pt]{\includegraphics[width=100pt]{figure/path_solutions/path_sol8.eps}}\\
 \end{tabular}
@@
 \bibliography{References}
+\newpage
+\clearpage
+\listoftables
+\listoffigures
 

### 2018-04-25 idetc2018_conf_version.tex
Some more corrections

@@
 
-In this paper, we 1) employ pattern recognition and computational shape analysis, to create a similarity transforms-independent signature for coupler path and motion, 2) exploit the non-linear nature of relationship between the linkage parameters and coupler motions to create a sensitive, wide-ranging, compact, and efficient database with hierarchical clustering, and 3) enable dimensionality reduction using Auto-encoder Neural Networks.
+In this paper, we 1) employ pattern recognition and computational shape analysis, to create a similarity transform-independent signature for coupler path and motion, 2) exploit the non-linear nature of relationship between the linkage parameters and coupler motions to create a sensitive, wide-ranging, compact, and efficient database with hierarchical clustering, and 3) enable dimensionality reduction using Auto-encoder Neural Networks.
 When a user inputs a motion or a path, a query representing invariant signature \footnote{path or motion signature} of the input is raised for $k$ nearest neighbors among cluster centers in the database.
@@
 Wandling~\cite{wandling2000} and Yu et al.~\cite{yue-pathgen2011} have built libraries with all possible coupler curves, where one curve is broken down into many segments for creating data for partial curves.
-In contrast to this, we need to store only one curve representing all the segments in it as our representation facilitates partial matching.
+In contrast to this, we need to store only one curve representing all the segments in it, as our representation facilitates partial matching.
 None of the other previous methods facilitate this partial matching of open motion curve into another open or closed curve, which significantly contributes to providing a large number of solutions, and reduces the data requirement even further.
@@
 Consider a motion given in parametric form as, $x:x(t), y:y(t), \theta:\theta(t)$.
-Here, $\theta(t)$ represents the change in orientation along the path, measured with respect to initial orientation and is not restricted in the domain $[-\pi, \pi]$.
+Where, $\theta(t)$ is the change in orientation along the path with respect to initial orientation.
+It should be noted that $\theta(t)$ is a continuous curve with domain ($-\infty$, $\infty$) in contrast to conventional domain i.e. [$-\pi$, $\pi$].
 
@@
 \subsection{Partial Matching of Path Signatures}\label{sec_ncc}
-When a path query is raised, it can be very useful to know whether this path matches with the part of a path from the database.
+When a path query is raised, it can be very useful to know whether this path matches with a part of a path from the database.
 This subsection presents a method for determining this partial similarity.
@@
 Here, $p$ acts as a template that tries to find the best match against $W$ while sliding over it along $j$.
-Domain of $Cn(j, p, W)$ is [0, 1], where 1 represents the complete embedment of $p$ inside $W$.
+Domain of $Cn(j, p, W)$ is [0, 1], where 1 represents the complete embedment\footnote{\emph{Path} is identical to a portion of \emph{Whole}.} of $p$ inside $W$.
 
@@
 \includegraphics[width=240pt]{figure/fig_whole_part.eps}
-  \caption{Part path is formed by trimming whole path followed by translation and scaling.}
+  \caption{\emph{Part} path is formed by trimming whole path followed by translation and scaling. Arrows indicate the increasing direction of parameter $t$.}
 \label{wholePart}

### 2018-04-25 idetc2018_conf_version.tex
some more bugs

@@
 \section{Signatures of Coupler Path and Motion}\label{sec_sign}
-Focus of the paper is on a novel method for motion generation that takes a parametric motion $(x:x(t), y:y(t), \theta:\theta(t))$ or path $(x:x(t), y:y(t))$ as the input and returns defect-free linkages producing similar motion or path.
+Focus of the paper is on a novel method for mechanism synthesis that takes a parametric motion $(x:x(t), y:y(t), \theta:\theta(t))$ or path $(x:x(t), y:y(t))$ as the input, and returns defect-free linkages that produce similar motion or path.
 The input is transformed into a representation, termed as a signature, which is invariant to similarity operations, viz. reflection, rotation, translation, and scaling.
@@
 Figure~\ref{curvatureK} shows computed curvature and its unsigned integral of the coupler path shown in Fig.~\ref{bsplineFitting}.
-It can be seen that curvature is small at the start, increases as the curve bends along the path and drops once again as the path straightens out.
+It can be seen that the curvature is small at start, increases as the curve bends along the path and drops once again as the path straightens out.
 It is obvious that curvature plot will reverse if the direction of parameterizations reverses, while the integral is a monotonically increasing function.
@@
 Figure~\ref{signature} shows path and motion signature obtained for the motion depicted in Fig.~\ref{bsplineFitting}.
-It is important to note, that the signature depends on the direction of parameter t, as shown in Fig~\ref{bsplineFitting}.
+It is important to note, that the signature depends on the direction of parameter $t$.
 The procedure of signature calculation presented in this section is given in Algorithm ~\ref{alg_signature}.
@@
 \end{equation}
-where $E(j, p, W)$ is the dissimilarity value when template $p$ is matched to $W$ at $j^{th}$ index. Here $p$ tries to find the best match against $W(i)$ while sliding over it.
+where $E(j, p, W)$ is the dissimilarity value when template $p$ is matched to $W$ at $j^{th}$ index. Here $p$ tries to find the best match against $W$ while sliding over it.
 Similar to path signature, motion signature is dependent on the direction of $t$. Thus, we compute the dissimilarity for both directions and choose whichever is the least i.e. $E_{min}(p, W)$.
@@
 \end{equation}
-where $\textbf{\emph{l}}$ is the vector of linkage parameters for particular planar linkage, $p$ is signature the of task curve taken as template for Normalized Cross-Correlation and ${\{W_i\}}_{i=0}^{s}$ is the signature set of all $s$ coupler paths generated by the linkage corresponding to $\textbf{\emph{l}}$.
+where $\textbf{\emph{l}}$ is the vector of linkage parameters for particular planar linkage, $p$ is signature the of task path taken as the template and ${\{W_i\}}_{i=0}^{s}$ is the signature set of all $s$ coupler paths generated by the linkage corresponding to $\textbf{\emph{l}}$.
 In case of four-bar, $\textbf{\emph{l}}: l_1, l_2, l_3, l_4, l_5$, where $l_i$ is link ratio of $i^{th}$ link shown in Fig~\ref{fourbar}.
@@
 It can be clearly seen that these linkages generate highly accurate paths for the sit to stand activity.
+It is important to note that every solution is a result of partial matching of coupler paths, and otherwise would be very hard to search using other atlas-based approaches that only have the whole-to-whole matching facility.
 
@@
 Coupler motions of these linkages have a part, which matches with the shape of input motion query.
-Actual scaling and orientation of the linkage can be found out easily by comparing analogous points, which are given by the offset index $j$ that corresponds to minimum distance$(E_min)$ in Eq.~\req{mccEq}.
+Actual scaling and orientation of the linkage can be found out easily by comparing analogous points, which are given by the offset index $j$ that corresponds to minimum distance$(E_{min})$ in Eq.~\req{mccEq}.
 Figure~\ref{ex2_solns} depict the solutions obtained after scaling and orienting the linkage to match required motion.

### 2018-06-21 rebuttal/rebuttal.tex
Updated after journal reviews

\documentclass{article}
\title{Rebuttal}
\author{Shrinath Deshpande, Anurag Purwar}

\begin{document}
\maketitle
We are grateful to all of the reviewers, who took out their valuable time to review our paper. This work would be incomplete without the reviewers' inputs.
The reviewers' comments are given in \emph{italicized}, whereas our answers are in normal text.

\section{Reviewer 1}
%The authors propose applying machine learning techniques to solving planar four-bar linkage problems. The authors claim gaps exist in existing methods that do not account for circuit and branch defects in the synthesis process.
%Significant technical deficiencies and several editorial issues exist in the submitted manuscript. Therefore, this reviewer must recommend a reject and encourage the authors to make major revisions before the manuscript could be acceptable for publication.
\begin{itemize}
  \item \emph{
Overall, the paper lacks a clear motivation for why the described method is required.
The authors highlight several gaps in existing methods identified by the literature.
However, the authors do not explain how those defects affect current practice or why a new method is necessary.
While gaps may exist in current methods, are those gaps significant enough to not produce accurate results? If so, why? The introduction of the manuscript reads as a background knowledge section.
This reviewer recommends the authors include a new introduction that strongly motivates their work described in the manuscript and rename the current introduction.
Example questions for identifying a motivation are: what stakeholders benefit from the authors' contributions? What are the expected benefits and/or impacts of the novel contributions? To what type of real, practical problems does the method apply?
}

Thank you for pointing out an important point. We have added the motivation subsection, which clearly explains the significance of the gaps in current practices.
The defects in linkages is a major concern faced by the current state of the art methods.
We also state that, being defect-free with respect to precision positions alone is not enough for the mechanism, to be useful.
\\

  \item \emph{
Overall, the paper lacks a clear motivation for why the described method is required.
Further, most of the citations in the manuscript, not including the authors' previous work, are over 10 years old.
}

Thanks, we are added recent citations reporting the work in the area of mechanism synthesis, and machine learning applications to mechanisms.
\\

  \item \emph{
    Absent a strong motivation, the manuscript reads as if the authors pursued a machine-learning problem for the sake of machine learning. This reviewer finds little value in answering these types of research questions.
  }

We exploit machine learning to maximize the diversity, and for efficient storage of the linkage database.
The outcomes of this approach are a large number of diverse concept solutions.
The importance of diverse concept generation is mentioned in motivation subsection by following lines,
"Thus, the synthesis method should be prolific in terms of concept generation to 1) realize the potential of attainable design possibilities, and 2) have the agility to adapt a design to evolving requirements."
\\

  \item \emph{
Instead, the authors should motivate their work with important use cases that address necessary research questions for an identified stakeholder. Tell the reader why this work is important? The authors claim the current approaches are useless for practical applications. What are the practical applications and what are their requirements? The authors do include two use cases, but their practical relevance is not discussed.
}

Thank you for your comments.
We have added one example in the motivation section, which clearly explains the limitations of current practices.
We use the same example in the example sections, to clearly juxtapose our results against results of precision point approach.
\\

  \item \emph{
Manuscript lacks a clear motivation linked to the practitioner.
The research objective, methods, and approach are not clear.
}

Thank you for the feedback.
We have rewritten the introduction sections, to clearly explain motivation and overview of the approach.
\\

  \item \emph{
 The reason for employing machine learning techniques is artificially explained in one sentence at the end of Section 3.3. Expand the reason for employing machine learning.
}

We have expanded the reason for employing machine learning techniques in the subsection titled 'Dimensionality Reduction using Auto-Encoders' as follows,

"In order to have efficient query operations, we perform Hierarchical Clustering; a method that summarizes and creates a hierarchy in the database.
Clustering in higher dimensions suffers from \emph{Curse of Dimensionality}\cite{marimont1979}, thus we first perform dimensionality reduction using Auto-encoder Neural Networks.
Auto-encoder is a powerful mapping model, which learns to encode the input data in very compact representation and can reconstruct the input with minimal error; performing much better than Principal Component Analysis\cite{hinton2006}.
This nonlinear mapping by auto-encoder can greatly improve the representation of data for clustering~\cite{song2013}."

In addition to that, we have added following lines to explain the motivation behind using clustering,
"We use machine learning techniques such as clustering and data-compression using auto-encoder neural networks to come up with good initial guesses for local optimization.
First, We cluster the database using hierarchical clustering algorithm.
Then, we find representative data point in each cluster called cluster center and form their set.
This set of cluster centers represent a diverse group of linkages.
When a query is raised in the database, the first step is to search for neighbors in the set of cluster centers.
This often yields a diverse set of neighbors and is used as a set of initial guesses for local optimization.
"
\\

  \item \emph{
  In Fig. 1 (overview), should an arrow return from "Local Optimizer" to "Accurate?" or is the assumption that all outputs from the "Local Optimizer" are accurate?
}

Thanks for catching that, we fixed it.
\\

  \item \emph{
The values used in the sensitivity analysis are not justified. How did the authors choose the values?
}

Thank you for the comment. We made following changes in the lines,
"
To illustrate this via example, we perform sensitivity analysis in the vicinity of a singularity as follows... ",
and added, "The link ratios are chosen such that, small changes in some parameters lead to a topological change in the coupler curve."
\\

  \item \emph{
The quality of research methods cannot be assessed.
}

We have employed already proven techniques such as b-spline interpolation, hierarchical clustering, data compression using auto-encoders, Powell's local search.
We formulate the signatures of coupler path and motion, based on proven 2D curve matching technique by Cui et al.\cite{cui2009}.
We present the validation of the partial matching algorithms using examples in section 4.
Finally, we present two case studies, where we obtain the diverse set of useful linkage solutions for path and motion generation problem.
\\

  \item \emph{
The conclusion is too short. It lacks a critical discussion of the research. The authors should critically assess the proposed approach.
}

Thanks for the important feedback, we have modified the conclusion by adding critical discussion of the research.

  \item \emph{
 Review the usage of "that" versus "which". There are some instances where the usage should be reversed.
 \\
 Several instances exist throughout the manuscript where nouns could benefit from having a "the" put in from of them. For example, the first sentence of Section 5.1 reads as, "Each data point in the database consists of discrete..." Instead, the sentence should read as, "Each data point in [the] database consists of discrete..."
 Check usage of hyphens. Inconsistent usage exists in the manuscript.
 }

 Thanks for the comments. We have revised the text and fixed it.
\\

\end{itemize}

\section{Reviewer 2}

\begin{itemize}
  \item \emph{
$1$. Please provide brief descriptions (possibly with examples) of circuit and branch defects that
occur when using existing synthesis methods.
}

Thanks for raising this point.
We have added one example in the introduction section, to illustrate the defects in mechanisms when using existing synthesis methods.
\\

  \item \emph{
  $2$. In Figure 2b, why is the range of parameter $t$ for $\theta(t)$ is only 0-50, rather than 0-100?
}

Thanks for catching that. It was a plotting mistake. We fixed it.
\\

  \item \emph{
$3.$ In Algorithm 2, Line 8, should it be $\theta(tmp)$ instead of $\kappa(tmp)$ ?\\
$4.$ Please check the parenthesis in Equation 5.\\
$6.$ There are several typos involving subscripts all throughput the paper. Please fix them.
}

Thanks for catching those. We fixed them. Thanks
\\

  \item \emph{
$5.$ In Figure 15, $X$ and $\tilde{X}$ mismatch the input and output vectors shown in the diagram.
}

Figure 15 shows $X$ as the input and $\tilde{X}$ as the output of auto-encoder network, which matches with the description.
The query regarding the mismatch is not clear to us.
Could you please elaborate on the query?
\\

  \item \emph{
$7.$ In section 5.1, it is argued that Euclidean distance is used as the distance metric in latent space for
computational efficiency, whereas in section 6.1, $(1 − Cn)$ is mentioned as the distance
metric. Please clarify.
}

Thanks for the feedback. We have made changes in the text to clarify which metric is used at what point.
In section 5.1, we added following lines, "The distance metric used for clustering is the Euclidean distance in the latent space.
Although the more accurate distance metric is distance function discussed in sec 3, it is very expensive to calculate it for the entire database.
Signatures with ${O}(m)$ points take ${O}(m\log{}m)$ time for each comparison and there are ${O}(N^2)$ number of comparisons to be made for the database of $N$ points.

Now, when the user raises a query, we use the distance function from sec.3 for finding $k$ nearest neighbors among $1500$ cluster centers.
If a cluster center is not sufficiently close, we descend into its corresponding cluster to find the closest data point. "
" The distance metric for finding neighbors among cluster centers is $1-Cn_{max}$ in Eq. 5.  "
\\

  \item \emph{
$8.$ It is unclear how local optimization is performed after finding the nearest cluster centers. Is the
search performed in each cluster independently? Are multiple paths/motions in the database
combined with partial matching? Please elaborate.
}

Thanks for the comments.
We use the cluster centers as independent initial guesses and do a local search on each initial guess independently.
We added following lines in section 5 to clarify that.

"When a query is raised in the database, the first step is to search for neighbors in the set of cluster centers.
This often yields a diverse set of neighbors, and is used as a set of independent initial guesses for local optimization."
\\

  \item \emph{
$9.$ Please comment on how this approach can be extended to handle process specific constraints?
For example, the pivots should lie above ground in show-shoveling case study (6.2).
}

Thank you for mentioning that. We added following lines in the conclusion.
"The partial matching metric although more accurate, but is expensive in terms of computation cost.
Thus, we use Euclidean metric in the latent space of compressed data for hierarchical clustering.
The formulation is invariant with respect to translation, orientation, and scaling.
Hence, constraints like geometric restrictions on pivots, have to be addressed after finding feasible solutions for the task."

\end{itemize}

\bibliographystyle{purwar}
\bibliography{References}

\end{document}

### 2018-06-21 idetc2018_journal.tex
Updated after journal reviews

@@
 The query is raised in the database for nearest neighbors, which are either solutions or good initial conditions for fast local optimization techniques.
-In spite of highly non-linear parameters space, our approach discovers a wide pool of defect-free solutions very quickly.
+In spite of highly nonlinear parameters space, our approach discovers a wide pool of defect-free solutions very quickly.
 We show that by employing proven machine learning techniques, this work could have far-reaching consequences to creating a multitude of useful and creative conceptual design solutions for mechanism synthesis problems, which go beyond planar four-bar linkages.
@@
 \section{Introduction}
-Classical mechanism synthesis problem deals with computing type and dimensions of linkage system for performing specific tasks, which are categorized as path, motion and function generation; for an exhaustive reference, see books from McCarthy and Soh \cite{sohmccarthy}, Sandor and Erdman~\cite{Sandor}, Hunt \cite{Hunt78}, Hartenberg and Denavit \cite{Hartenberg},  Suh and Radcliffe \cite{Suh78}, and Lohse \cite{lohse2013}.
-Various approaches have been proposed in the literature with aim of finding acceptable solutions for practical situations.
-However, the majority of the approaches do not account for circuit and branch defect in the synthesis process, which can render the solution useless for practical applications.
-These defects in the single degree of freedom mechanisms are thoroughly discussed by Chase and Mirth\cite{chasemirth}.
+\begin{figure}
+\centering
+\includegraphics[width=200pt]{figure/fig_circuit_defect.eps}
+  \caption{The mechanism synthesis problem for the prescribed motion.
+  The four-bar mechanism obtained using the precision position approach suffers from circuit defect, as no coupler circuit passes through all precision positions.}
+\label{circuit_defect}
+\end{figure}
 
@@
 
-In this paper, we 1) employ pattern recognition and computational shape analysis, to create a similarity transform-independent signature for coupler path and motion, 2) exploit the non-linear nature of relationship between the linkage parameters and coupler motions to create a sensitive, wide-ranging, compact, and efficient database with hierarchical clustering, and 3) enable dimensionality reduction using Auto-encoder Neural Networks.
-When a user inputs a motion or a path, a query representing invariant signature \footnote{path or motion signature} of the input is raised for $k$ nearest neighbors among cluster centers in the database.
-These $k$ neighbors, if needed, are subjected to fine-tuning by local optimization to obtain a set of defect-free solutions.
-We define a novel objective function for defect-free motion generation problems and present an algorithm for partial matching of motions.
-The objective function that drives the synthesis process computes a distance measure of dissimilarity between the task motion and the coupler motion generated by current linkage parameters.
-This distance measure of dissimilarity inherently requires continuity of motion, thus ensuring that the output mechanism is defect-free throughout the task.
-The Fig.~\ref{overallMethod} illustrates an overview of our method, which is codified in Algorithm~\ref{alg_overall}.
+The classical mechanism synthesis problem deals with computing type and dimensions of a linkage system for performing specific tasks, which are categorized as the path, motion and function generation.
+Path generation task aims to synthesize a mechanism, which can guide a point along a prescribed path.
+On the other hand, the objective of motion generation task is to synthesize a mechanism, which can guide a rigid body along a prescribed motion\footnote{motion is the combination of position and orientation.}.
+For an exhaustive reference, see books from McCarthy and Soh \cite{sohmccarthy}, Sandor and Erdman~\cite{Sandor}, Hunt~\cite{Hunt78}, Hartenberg and Denavit \cite{Hartenberg},  Suh and Radcliffe \cite{Suh78}, and Lohse \cite{lohse2013}.
+Various approaches have been proposed in the literature with aim of finding acceptable solutions for path and motion generation problem.
+In the majority of the methods, the first step is choosing a mechanism type and then calculating the design parameters of chosen mechanism type.
+The prior step is called Type Synthesis, and the later step is Dimension Synthesis.
+This paper presents an approach to Dimension Synthesis of planar four-bar linkages, but the approach is general enough to be applied on any planar linkage.
 
-Path synthesis methods based on Fourier analysis do take continuity information of the coupler path into account, however, most of them are defined only for closed loop curves.
+\subsection{Motivation}
+The majority of mechanism synthesis methods are based on the precision point approach.
+This approach is a clever approximation trick to solve the abovementioned tasks, where the task is discretized into precision points.
+These points, instead of the actual task, are now treated as interpolation or approximation task for mechanism synthesis.
+However, this way of formulation loses important information about the actual continuous task and can lead to solutions with the order, circuit and branch defects.
+The defect in a mechanism renders itself useless for its intended application.
+The defects in the single degree of freedom mechanisms are thoroughly discussed by Chase and Mirth\cite{chasemirth}.
+
+Let's see an example of this in a motion generation task.
+The objective is to synthesize a four-bar mechanism that can perform the prescribed motion.
+Figure~\ref{circuit_defect} shows the prescribed motion and its discretized precision positions.
+In the case of motion generation problem, a four-bar can go through at most five precision positions, and it is called as classical Burmester~\cite{Burmester86} problem.
+For this type of problem, only finite solutions exist and in this case, only one solution is obtained as shown in Fig.~\ref{circuit_defect}.
+It can be seen that, although coupler of the four-bar passes exactly through five precision positions, it can not do it without changing the circuit.
+A circuit represents an assembly mode in which the mechanism is put together.
+This phenomenon is called circuit defect in the linkage, which makes the linkage useless for the prescribed task.
+To deal with it, a naive approach is to tweak precision positions in a brute-force way within the tolerance until a solution is found.
+Even if the defect-free solution is found, the coupler motion in-between the precision points may not have the desired properties.
+This happens because the method discards the functional aspect of continuous motion and turns it into a vacuous interpolation problem.
+This tells us that just finding a defect-free linkage with respect to the precision positions, is not enough to qualify as a useful mechanism.
+
+Thus, we present a perceptive way of synthesizing defect free linkages for motion and path generation problems.
+%As a guiding direction to advance state of the art, we propose following criteria for an effective mechanism synthesis method,
+%  \item \textbf{Data Driven}: The method should evolve by learning from its previous experiences, including providing quicker solutions for problems similar to previously solved problems.
+%\end{enumerate}
+To capture the complete prescribed task, we represent it as a continuous parametric curve.
+The objective is to find a linkage, that has a coupler motion or path compatible with the task.
+We developed the compatibility measure in a way that is invariant to similarity transformations.
+Next step is to conduct a search in the space of linkage parameters to find linkages with coupler motions compatible with the prescribed task.
+Although global search methods can be applied for finding solutions, we employ an efficiently clustered database and Powell's local search method to come up with a variety of different solutions.
+The motivation behind using clustered database is rooted in the broader objective of machine design.
+Mechanism synthesis is a part of the conceptual design phase, which is one of the earliest stages of product design cycle of a machine.
+Thus, the synthesis method should be prolific in terms of concept generation to 1) realize the potential of attainable design possibilities, and 2) have the agility to adapt a design to evolving requirements.
+The method only deals with the coupler curves and is indifferent to the linkage type.
+Thus, it is readily scalable to any type of planar linkage.
+In section~\ref{subsec_motiongen}, we present the obtained solutions for the prescribed motion presented in Fig.~\ref{circuit_defect}.
+
+\subsection{Literature Survey}
+% Global search methods
+Instead of brute-force search within tolerance regions, some approaches apply separate constraints to take care of the defects and form an optimization problem of Non-Differentiable objective function.
+It can be solved by metaheuristic algorithms like Differential-evolution(DE), Particle Swarm Optimization (PSO), Cuckoo Search (CS).
+Cabrera et al.\cite{Cabrera2002} used Genetic Algorithm as the tool for optimization in mechanism synthesis.
+Sardashti et al.\cite{sardashti2013} used PSO towards the defect-free synthesis of four-bar linkage with joint clearance for path generation problem.
+Ebrahimi and Payvandy\cite{Ebrahimi2015} presented an application of Imperialist Competitive Algorithm (ICA) for synthesizing path generating four-bars having desired workspace limits.
+Bulatovic\cite{Bulatovic2013} used Cuckoo Search for solving the problem of optimum synthesis of a six-bar double dwell linkage.
+The above methods can produce many defect-free solutions and are scalable to any type of linkages.
+However, these methods tend to be slow and inefficient, as they start from scratch for every instance, and with no guarantee of converging to an acceptable solution.
+
+Path synthesis methods based on Fourier analysis do take the continuity information of coupler path into account.
+However, most of them are defined only for closed loop curves.
 Ullah and Kota\cite{ullah1997} have presented an invariant approach towards representation and synthesis of closed loop paths through shape optimization.
 They use a combination of global and local search methods for optimizing Fourier Deviant function, to compute the dimensions of planar four-bar linkages without an initial guess.
-Wu et al.\cite{wu2011} presented a method for open and closed path generation based on finite Fourier series.
+Wu et al.\cite{wu2011} presented a method based on finite Fourier series for open and closed path generation, but it is specific to four-bar mechanisms.
 In the case of motion generation, Li et al.\cite{li2016} have developed a Fourier descriptor-based approach for approximate motion generation.
+Bu$\acute{s}$kiewicz et al.\cite{Buskiewicz2009} used curvature of the coupler curve for path synthesis using Genetic Algorithms.
+Khan et al.\cite{khan2015} presented on approach where an artificial neural network is used for mapping between Fourier coefficients corresponding to a coupler path and corresponding linkage parameters.
+% ---
 
-Due to highly nonlinear nature of the problem, most optimization based methods require a good initial condition to start.
-Thus, an atlas or a design library is used to provide good initial conditions.
-McGarva\cite{mcgarva1994} took the earliest approach towards creating a library for coupler trajectories based on a harmonic analysis.
+% Atlas Based Methods ---
+Instead of the global search, an alternative approach is to start from a good initial guess based on an atlas and use local search methods.
+We adopt this approach and combine with our novel formulation to generate a diverse set of concept solutions.
+McGarva\cite{mcgarva1994} took the earliest approach towards creating a library for coupler trajectories based on the harmonic analysis.
 Wandling\cite{wandling2000} has presented an atlas-based approach, where coupler paths and motions are stored in terms of Fourier Transforms.
@@
 In their approach, a task curve is transformed into normalized Fourier coefficients and queried for the nearest neighbor search.
-The best match is returned as the solution to input.
+The best match is returned as the solution to the input.
 Chu et al.\cite{chu2010} presented an atlas-based method for synthesizing spatial four-bar linkages for function generation problems, where orientation data is stored in terms of Fourier descriptors.
@@
 The above methods generate data based on uniform sampling in the linkage parameter space.
-Given highly nonlinear mapping between linkage parameters and coupler trajectory, this way of sampling leads to a non-uniform sampling of trajectory space causing under-representation of possible motions.
-We address this issue by employing log-normal distribution in the linkage parameter space to generate data and perform compact clustering of the data using machine learning techniques.
-Hierarchy is created in the database by means of clustering, where the top level comprises of data points called cluster centers, which are representative of the cluster points in lower levels.
+Given highly nonlinear mapping between linkage parameters and coupler trajectory, this way of sampling leads to a nonuniform sampling of trajectory space, which causes under-representation of possible motions.
+We address this issue by employing log-normal distribution in the linkage parameter space to generate the data samples.
+Then, we perform compact clustering of the data using machine learning techniques.
+A hierarchy is created in the database by means of clustering, where the top level comprises of data points called cluster centers, which are representative of the cluster points in lower levels.
 Wandling~\cite{wandling2000} and Yu et al.~\cite{yue-pathgen2011} have built libraries with all possible coupler curves, where one curve is broken down into many segments for creating data for partial curves.
-In contrast to this, we need to store only one curve representing all the segments in it, as our representation facilitates partial matching.
+In contrast to this, we need to store only one curve that represents all the segments in it.
+This is because our representation facilitates part-to-whole matching.
 None of the other previous methods facilitate this partial matching of open motion curve into another open or closed curve, which significantly contributes to providing a large number of solutions, and reduces the data requirement even further.
+%  ---
+\subsection{The Method Overview}
+
+The original contributions in the paper are as follows:
+
+1) a perceptive problem formulation for path and motion generation, that solves the issues associated with precision point approach.
+The formulation is based on a measure of dissimilarity between two planar motions or paths, which is invariant to similarity transforms.
+2) we exploit the nonlinear nature of the relationship between the linkage parameters and coupler motions to create a sensitive, wide-ranging, compact, and efficient database with hierarchical clustering.
+
+%In this paper, we 1) employ pattern recognition and computational shape analysis, to create a similarity transform-independent signature for coupler path and motion, 2) exploit the nonlinear nature of relationship between the linkage parameters and coupler motions to create a sensitive, wide-ranging, compact, and efficient database with hierarchical clustering, and 3) enable dimensionality reduction using Auto-encoder Neural Networks.
+
+In this paper, we employ pattern recognition and computational shape analysis, to create a similarity transform-independent signature for coupler path and motion.
+When a user provides the prescribed motion or path, a query representing invariant signature \footnote{path or motion signature} of the input is raised for $k$ nearest neighbors among cluster centers in the database.
+These $k$ neighbors, if needed, are subjected to fine-tuning by local optimization to obtain a set of defect-free solutions.
+The objective function that drives the synthesis process computes a distance measure of dissimilarity between the task and the coupler motion or path generated by current linkage parameters.
+This distance measure of dissimilarity inherently requires continuity of motion, thus ensuring that the output mechanism is defect-free throughout the task.
+Figure~\ref{overallMethod} illustrates an overview of our method, which is codified in Algorithm~\ref{alg_overall}.
 
@@
 Figure~\ref{curvatureK} shows computed curvature and its unsigned integral of the coupler path shown in Fig.~\ref{bsplineFitting}.
-It can be seen that the curvature is small at start, increases as the curve bends along the path and drops once again as the path straightens out.
+It can be seen that the curvature is small at the start, increases as the curve bends along the path and drops once again as the path straightens out.
 It is obvious that curvature plot will reverse if the direction of parameterizations reverses, while the integral is a monotonically increasing function.
@@
 We note that there is a one-to-one mapping between $t$ and $K$.
+Although it seems natural to use dual-quaternions for representing motion and finding its signature,
+it couples orientation with the path in a way, such that the signatures formed no longer remain invariant to similarity transformation.
 
@@
       $i = i + 0.1$ \\
-      motionSignature.push($\kappa$($tmp$)) \\
+      motionSignature.push($\theta$($tmp$)) \\
       pathSignature.push($\kappa$($tmp$))
@@
 \begin{equation}\label{nccEq}
-  Cn(j, p, W) = |\sum_{i}^{p_{span}} \frac{(W(i+j) - \bar{W}(j : j + p_{span}))(p(i) - \bar{p})}{\sqrt{\sum_{i}^{p_{span}}{(W(i+j) - \bar{W}_{p_{span}})}^2\sum_{i}^{p_{span}}{(p(i) - \bar{p})}^2}} |,
+  Cn(j, p, W) = |\sum_{i}^{p_{sp}} \frac{(W(i+j) - \bar{W}(j : j + p_{sp}))(p(i) - \bar{p})}{\sqrt{\sum_{i}^{p_{sp}}{(W(i+j) - \bar{W}_{p_{sp}})}^2\sum_{i}^{p_{sp}}{(p(i) - \bar{p})}^2}} |,
 \end{equation}
-where $Cn(j, p, W)$ is the normalized cross-correlation value when $p$ is matched against $W$ at $j^{th}$ index; $p_{span}$ is length of the array $p$ and $\bar{W}(j:j + p_{span})$ is mean of the values of array $W$ between index range of ($j, j+p_{span}$).
+where $Cn(j, p, W)$ is the normalized cross-correlation value when $p$ is matched against $W$ at $j^{th}$ index; $p_{sp}$ is length of the array $p$ and $\bar{W}(j:j + p_{sp})$ is mean of the values of array $W$ between index range of ($j, j+p_{sp}$).
 
@@
 \begin{equation}\label{mccEq}
-  E(j, p, W) = \sum_{i}^{p_{span}} {((W(i+j) - \bar{W}(j: j + p_{span})) - (p(i) - \bar{p}))}^2,
+  E(j, p, W) = \sum_{i}^{p_{sp}} {((W(i+j) - \bar{W}(j: j + p_{sp})) - (p(i) - \bar{p}))}^2,
 \end{equation}
@@
 Objective function evaluation step consists of calculation of coupler motion or path and finding its dissimilarity score.
-It is important to note that representation obtained in Section~\ref{sec_sign} reduces the size of the linkage parameters in optimization.
+It is important to note that representation obtained in Section~\ref{sec_sign} reduces the number of parameters in optimization.
 This optimization problem can be solved using search methods which do not require gradient computation.
 We can employ global optimization methods such as differential evolution at the start, and local optimization methods link Powell's method towards the end for faster convergence\cite{ullah1997}.
-%Section~\ref{examples} presents results for the optimization technique used.
 
-Considering highly non-linear nature of the problem, finding a good initial guess proves to be daunting.
+Considering highly nonlinear nature of the problem, finding a good initial guess proves to be daunting.
+Also, as we mentioned in the motivation, it is important to generate a diverse set of solutions.
+This requires a diverse and large number of good initial guesses.
 Thus, we exploit machine learning techniques to create a database for finding many good initial guesses or the solution itself.
+Section~\ref{sec_db_ae} presents the details on the approach.
 
@@
 
-To illustrate this, we perform sensitivity analysis in the vicinity of the singularity as follows:
+To illustrate this via example, we perform sensitivity analysis in the vicinity of a singularity as follows:
 A four-bar with link ratios ($l_1:0.55$, $l_2:1$, $l_3:1.5$, $l_4:1$, $l_5:1$) is subjected to gradual change in parameters $l_1$ and $l_3$ by the amount (-0.2, 0.2) in steps of 0.01.
+The link ratios are chosen such that, small changes in some parameters lead to the topological change in the coupler curve.
 Error function between motions of new and initial four-bar are calculated using Eq.~\req{objectiveFunMotion} .
@@
 \section{Clustered Database of Planar Linkages}\label{sec_db_ae}
+
 Having an invariant representation facilitating partial matching greatly reduces data required to sample all possible types of shapes of coupler motion.
-We have built a database of planar four-bar linkages with revolute joints as an example, but the approach is same for any planar motion generating machine.
+We have built a database of planar four-bar linkages with revolute joints as an example, but the approach is same for any planar motion generating mechanism.
 We generate this database comprising of $40,000$ linkages while taking following aspects into consideration.
@@
 Figure~\ref{fourbar} represents parametric representation of four-bar linkage with parameters ($l_1,l_2,l_3,l_4,l_5$).
-As mapping between four-bar linkage parameter space and coupler motion space is highly non-linear, uniform distribution over linkage parameter space does not necessarily mean uniform sampling over coupler motion space.
+As mapping between four-bar linkage parameter space and coupler motion space is highly nonlinear, uniform distribution over linkage parameter space does not necessarily mean uniform sampling over coupler motion space.
 Thus, an efficient approach would be to sample more in the regions where sensitivity is maximum.
 We have observed that whenever the link ratios of four-bar linkage are close to 1, the sensitivity of shape of a coupler motion is higher than otherwise.
-Thus, we have chosen Log-Normal probability distribution ($\mu = 0,\sigma = 0.6 $) for selecting the link ratios : $(l_1, l_2, l_3)$ as shown in Fig.~\ref{logNormal}, and Normal Distribution ($\mu = 0,\sigma = 2 $) for $(l_4, l_5)$.
+Thus, we have chosen Log Normal probability distribution ($\mu = 0,\sigma = 0.6 $) for selecting the link ratios : $(l_1, l_2, l_3)$ as shown in Fig.~\ref{logNormal}, and Normal Distribution ($\mu = 0,\sigma = 2 $) for $(l_4, l_5)$.
 
@@
 
+We use machine learning techniques such as clustering and data-compression using auto-encoder neural networks to come up with good initial guesses for local optimization.
+First, We cluster the database using hierarchical clustering algorithm.
+Then, we find representative data point in each cluster called cluster center and form their set.
+This set of cluster centers represent a diverse group of linkages.
+When a query is raised in the database, the first step is to search for neighbors in the set of cluster centers.
+This often yields a diverse set of neighbors and is used as the set of independent initial guesses for local optimization.
+
 \subsection{Dimensionality Reduction using Auto-Encoders}
 Each data point in the database consists of discrete signature, which is kept to be of 100 float digits.
-In order to have efficient query operations, we perform Hierarchical Clustering; a method that summarizes and creates a hierarchy in the database.
+In order to have efficient query operations, we perform hierarchical Clustering; a method that summarizes and creates a hierarchy in the database.
 Clustering in higher dimensions suffers from \emph{Curse of Dimensionality}\cite{marimont1979}, thus we first perform dimensionality reduction using Auto-encoder Neural Networks.
 Auto-encoder is a powerful mapping model, which learns to encode the input data in very compact representation and can reconstruct the input with minimal error; performing much better than Principal Component Analysis\cite{hinton2006}.
-This non-linear mapping by auto-encoder can greatly improve the representation of data for clustering~\cite{song2013}.
+This nonlinear mapping by auto-encoder can greatly improve the representation of data for clustering~\cite{song2013}.
 Figure~\ref{autoEncoder} shows a Neural Network architecture similar to the one we designed for the task.
@@
 Standard clustering algorithms are performed on this latent\footnote{compressed output of bottleneck layer.} space for better clustering\cite{song2013}.
-We use Agglomerative Clustering, a method of Hierarchical clustering, which is an approach to partitioning clustering for identifying groups in the dataset.
+We use Agglomerative Clustering, a method of hierarchical clustering, which is an approach to partitioning clustering for identifying groups in the dataset.
 \emph{Ward}\cite{ward1963} criterion is used for clustering, which minimizes the variance of the clusters being merged.
-The distance metric used is the Euclidean distance in the latent space.
+The distance metric used for clustering is the Euclidean distance in the latent space.
 Although the more accurate distance metric is distance function discussed in sec.~\ref{sec_distanceMetric}, it is very expensive to calculate it for the entire database.
 Signatures with ${O}(m)$ points take ${O}(m\log{}m)$ time for each comparison and there are ${O}(N^2)$ number of comparisons to be made for the database of $N$ points.
-When user raises one such query, we first find $k$ nearest neighbors among $1500$ cluster centers, then descend into their clusters if needed.
+
+Now, when the user raises a query, we use the distance function from sec.~\ref{sec_distanceMetric} for finding $k$ nearest neighbors among $1500$ cluster centers.
+If a cluster center is not sufficiently close, we descend into its corresponding cluster to find the closest data point.
 Motion with highest similarity score is returned along with its corresponding linkage parameters, which if required, are further fine-tuned to match the query using local optimization methods.
@@
 We compute its path signature by the steps mentioned in Algorithm ~\ref{alg_signature} and raise the query for nearest neighbors among 1500 cluster centers of our database.
-The distance metric for finding neighbors is $1-Cn_{max}$ in Eq.~\req{objectiveFunPath}.
+The distance metric for finding neighbors among cluster centers is $1-Cn_{max}$ in Eq.~\req{objectiveFunPath}.
 Table~\ref{ex1_knnLinkageData} tabulates the link ratios corresponding to obtained nine nearest neighbors.
@@
 
-\subsection{Motion Generation}
-The task is to find a pool of linkage systems that can perform snow-shoveling with a motion shown in Fig.~\ref{motionQuery}.
-The motion data is tabulated in Table ~\ref{poseData} to which we fit a B-spline with cord length parametrization in order to get the parametric representation of motion.
-The task can also be treated as a finite position motion generation and solved for valid solutions.
-We try with our real-time computational methods of algebraic fitting\cite{generalfitting-JCISE},\cite{shrinathpurwar2017} but obtained solutions suffer from circuit defect, which is not surprising as those methods do not account for the continuity of input positions.
-
-Now we employ the approach presented in this paper.
-The first step is to calculate motion signature of the task motion using steps mentioned in Algorithm ~\ref{alg_signature}.
-For that, we follow the steps given in section~\ref{sec_sign} to obtain the motion signature depicted in Fig.~\ref{queryResult}.
-Next, we raise the signature query for nearest signatures among cluster centers of the database.
-Fig.~\ref{queryResult} shows nine nearest neighbor signatures along with the task signature.
-Table~\ref{ex2_knnLinkageData} presents the linkage parameters corresponding to the nearest neighbors along with their distance score from the task.
-Coupler motions of these linkages have a part, which matches with the shape of input motion query.
-Actual scaling and orientation of the linkage can be found out easily by comparing analogous points, which are given by the offset index $j$ that corresponds to minimum distance$(E_{min})$ in Eq.~\req{mccEq}.
-Figure~\ref{ex2_solns} depict the solutions obtained after scaling and orienting the linkage to match required motion.
-All of these linkages satisfactorily perform the input task without any defect.
-As ground or fixed pivot locations should lie above the ground, all solutions except the $4^{th}$ solution are suitable for the task.
-In light of these results, we can say that this approach produces a large variety of solutions, which otherwise would be very hard to find using precision point approach.
+\subsection{Motion Generation}\label{subsec_motiongen}
 
@@
 \end{figure}
+
+\begin{figure}
+\begin{tabular}{cc}
+  1)\putindeepbox[2pt]{\includegraphics[width=120pt]{figure/sol1.eps}}
+    & 2)\putindeepbox[2pt]{\includegraphics[width=120pt]{figure/sol2.eps}} \\
+  3)\putindeepbox[2pt]{\includegraphics[width=120pt]{figure/sol3.eps}}
+    & 4)\putindeepbox[2pt]{\includegraphics[width=120pt]{figure/sol4.eps}}\\
+  5)\putindeepbox[2pt]{\includegraphics[width=120pt]{figure/sol6.eps}}
+    & 6)\putindeepbox[2pt]{\includegraphics[width=120pt]{figure/sol7.eps}} \\
+  7)\putindeepbox[2pt]{\includegraphics[width=120pt]{figure/sol8.eps}}
+    & 8)\putindeepbox[2pt]{\includegraphics[width=120pt]{figure/sol9.eps}}\\
+\end{tabular}
+\caption{Case Study 2: First eight linkages in the table~\ref{ex2_knnLinkageData} and their resultant coupler motions.}
+\label{ex2_solns}
+\end{figure}
+
+The task is to find a pool of linkage systems that can perform snow-shoveling with a motion shown in Fig.~\ref{motionQuery}.
+The motion data is tabulated in Table ~\ref{poseData} to which we fit a B-spline with cord length parametrization in order to get the parametric representation of motion.
+The task can also be treated as a finite position motion generation and solved for valid solutions.
+We try with our real-time computational methods of algebraic fitting\cite{generalfitting-JCISE},\cite{shrinathpurwar2017} but obtained solutions suffer from circuit defect, which is not surprising as those methods do not account for the continuity of input positions.
+Also, It is obvious that the coupler should not drop the snow during its entire motion except at the end.
+The prescribed motion entails this information.
+However, precision point approach cannot capture it.
+
+Now we employ the approach presented in this paper.
+The first step is to calculate motion signature of the task motion using steps mentioned in Algorithm ~\ref{alg_signature}.
+For that, we follow the steps given in section~\ref{sec_sign} to obtain the motion signature depicted in Fig.~\ref{queryResult}.
+Next, we raise the signature query for nearest signatures among cluster centers of the database.
+Fig.~\ref{queryResult} shows nine nearest neighbor signatures along with the task signature.
+Table~\ref{ex2_knnLinkageData} presents the linkage parameters corresponding to the nearest neighbors along with their distance score from the task.
+Coupler motions of these linkages have a part, which matches with the shape of input motion query.
+Actual scaling and orientation of the linkage can be found out easily by comparing analogous points, which are given by the offset index $j$ that corresponds to minimum distance$(E_{min})$ in Eq.~\req{mccEq}.
+Figure~\ref{ex2_solns} depict the solutions obtained after scaling and orienting the linkage to match required motion.
+All of these linkages satisfactorily perform the input task without any defect.
+As ground or fixed pivot locations should lie above the ground, all solutions except the $4^{th}$ solution are suitable for the task.
+Although Fig.~\ref{ex2_solns} shows that $5^{th}$ and $7^{th}$ solution may slightly interfere with the ground, it can be rectified by lifting the mechanism slightly up or making small changes in coupler dimensions.
+In light of these results, we can say that this approach produces a large variety of solutions, which otherwise would be very hard to find using precision point approach.
 
@@
 \end{table}
-
-\begin{figure}
-\begin{tabular}{cc}
-  1)\putindeepbox[2pt]{\includegraphics[width=120pt]{figure/sol1.eps}}
-    & 2)\putindeepbox[2pt]{\includegraphics[width=120pt]{figure/sol2.eps}} \\
-  3)\putindeepbox[2pt]{\includegraphics[width=120pt]{figure/sol3.eps}}
-    & 4)\putindeepbox[2pt]{\includegraphics[width=120pt]{figure/sol4.eps}}\\
-  5)\putindeepbox[2pt]{\includegraphics[width=120pt]{figure/sol6.eps}}
-    & 6)\putindeepbox[2pt]{\includegraphics[width=120pt]{figure/sol7.eps}} \\
-  7)\putindeepbox[2pt]{\includegraphics[width=120pt]{figure/sol8.eps}}
-    & 8)\putindeepbox[2pt]{\includegraphics[width=120pt]{figure/sol9.eps}}\\
-\end{tabular}
-\caption{Case Study 2: First eight linkages in the table~\ref{ex2_knnLinkageData} and their resultant coupler motions.}
-\label{ex2_solns}
-\end{figure}
 
@@
 \section*{Conclusion}
-This approach presents a novel machine-learning approach to generation of conceptual designs of defect-free linkage synthesis.
-The approach is highly data-efficient due to similarity invariant representation of paths and motion, which also facilitates partial matching.
-Sensitivity analysis indicates that complexity of the objective function, although multimodal and nonlinear, is not overly complex and certainly well behaved in the singular spaces.
+The methods based on precision point approach do not capture continuity of the task.
+This causes the solutions to have the branch, circuit and order defects.
+Also, the formulation fails to detect undesired properties of the coupler motion in the region between precision points.
+Thus, we present a perceptive problem formulation, by considering the entire prescribed task.
+We solve the formulation by employing machine-learning techniques and generate a large number of defect-free conceptual designs.
+The approach is highly data-efficient due to similarity invariant representation and partial matching.
+Sensitivity analysis indicates that complexity of the objective function is well behaved at the singular locations.
 The hierarchically clustered database provides efficient query search.
-Finally, the effectiveness of the presented approach is showcased by two case studies for each of which nine defect-free solutions were found.
-Although our method can provide highly accurate results, our focus here is to generate a high number of defect-free solutions that can perform the task in more or less similar fashion;
-because more often than not, linkage synthesis algorithms are desired to be prolific in terms of concept generation than to produce highly accurate, but very few solutions.
+Finally, the effectiveness of the presented approach is showcased by two case studies.
+Every solution presented in the examples section is a result of part-to-whole matching.
+The other atlas-based approaches facilitate only whole-to-whole matching, hence they would need a very large amount of data to find these results.
+
+Although the partial matching metric is more accurate, it is expensive in terms of computation cost.
+Thus, we use Euclidean metric in the latent space of compressed data for hierarchical clustering of the database.
+The problem formulation is invariant with respect to translation, orientation, and scaling.
+Hence, constraints like geometric restrictions on pivots, have to be addressed after finding feasible solutions for the task.
 The approach is general enough to be extended to higher order linkage systems for which there are even fewer methods available for synthesizing defect-free solutions.
+However, the database size increases exponentially with the number of links in the mechanisms.
+A potential solution to this problem could be to use learning based methods, where the pattern is learned instead of storing all of the information.
+Overall, the method provides a holistic approach towards the prescribed path and motion synthesis and encourages artificial intelligence techniques to make an impact.
 

### 2018-06-21 orig.idetc2018.tex
Updated after journal reviews

--- 2018-03-12 idetc2018.tex
@@
 %%% by ASME for your paper.
-\papernum{DRAFT: DETC2018-TBD}
+\papernum{DRAFT: DETC2018-85578}
 
@@
 \begin{abstract}
+% Mechanisms design is generally the earliest phase in a machines design stages.
+
 Success in Synthesis of mechanisms for motion generation refers to computing linkage type and dimensions to perform the task without disassembly.
-Majority of the methods formulate it as Precision Position problem (or Classical Burmester Problem) which inherently ignores the continuity information,
-resulting into solution linkages with branch, circuit and order defects.
-In this paper, we present a novel approach that addresses this issue into problem formulation and returns the solutions free from defects.
-At the heart of this approach lies an objective function that compares the motion as a whole, capturing designer's intent.
+However, majority of the methods formulate it as Precision Position problem (or Classical Burmester Problem) which inherently ignores the continuity information.
+Which, in turn results into solution linkages with branch, circuit and order defects.
+In this paper, we present a novel approach that addresses this issue into problem formulation and returns solutions free from defects.
+At the heart of this approach lies an objective function that compares the motion as a whole; thus, capturing designer's intent.
 In contrast to widely used structural error or loop-closer equation based error functions which convolute the optimization by considering shape, size, position and orientation simultaneously, this objective function computes motion difference in a form invariant to similarity transformations.
@@
 
-We employ auto-encoder neural networks to create a compact and clustered database of invariant motions of known linkages.
+The approach starts with creating database of invariant motions of known linkages.
   The query is raised in the database for k nearest neighbors, which are either solutions or good initial conditions for fast local optimization techniques.
@@
 \section{Introduction}
-Classical mechanism synthesis problem deals with computing type and dimensions of linkage system for performing specific tasks, which are categorized as path, motion and function generation.
-These problems have been dealt with by many approaches with the aim of finding acceptable solutions for practical situations.
-Several text books, such McCarthy and Soh \cite{sohmccarthy}, Sandor and Erdman~\cite{Sandor}, Hunt \cite{Hunt78}, Hartenberg and Denavit \cite{Hartenberg},  Suh and Radcliffe \cite{Suh78}, and Lohse \cite{lohse2013} cover the science and art of planar four-bar and higher-order linkages.
-The majority of these theories don't account for circuit and branch defect in the synthesis process, which can render the solution useless for practical applications.
-These defects in single DOF mechanisms are thoroughly discussed by Chase and Mirth\cite{chasemirth}.
+Classic mechanism synthesis problem deals with computing type and dimensions of linkage system for performing specific tasks, which are categorized as path, motion and function generation.
+This problem has been dealt with many approaches with the aim of finding acceptable solutions for practical situations.
 
@@
 
-Original contribution of this paper are in 1) a novel objective function for defect-free motion generation problem, 2) discovering a representation of coupler motion and path which is invariant under similarity transformations (henceforth termed as motion signature and path signature respectively), 3) novel algorithm for partial matching of motions , 4) optimal storage data by means of auto-encoder neural network and efficient neighbor search in the clustered database.
-The objective function that drives the synthesis process, computes a distance measure of dissimilarity between the task motion and the coupler motion generated by current linkage parameters.
-This distance measure of dissimilarity inherently requires continuity of motion; ensuring the output mechanism is defect free throughout the task.
+The motion and path generation problems are exhaustively researched topics.
+Several text books, such McCarthy and Soh \cite{sohmccarthy}, Sandor and Erdman~\cite{Sandor}, Hunt \cite{Hunt78}, Hartenberg and Denavit \cite{Hartenberg},  Suh and Radcliffe \cite{Suh78}, and Lohse \cite{lohse2013} cover the science and art of planar four-bar and higher-order linkages.
+The majority of these theories don't account for circuit and branch defect in the synthesis process, which can render the solution useless for practical applications.
+These defects in single DOF mechanisms are thoroughly discussed by Chase and Mirth\cite{chasemirth}.
+
+Original contribution of this paper are in 1) a novel objective function for defect-free motion generation problem, 2) discovering a representation of coupler motion and path which is invariant under similarity transformations (henceforth termed as motion signature and path signature respectively), 3) novel algorithm for partial matching of motions , 4) optimal storage by means of auto-encoder neural network and efficient neighbor search in the clustered database.
+The objective function that drives the synthesis process computes a distance measure of dissimilarity between the task motion and the coupler motion generated by current linkage parameters.
+The distance measure of dissimilarity inherently requires continuity of motion; ensuring the output mechanism is defect free throughout the task.
 
@@
 Wu et al.\cite{wu2011} presented a synthesis method for path generation based on finite Fourier series for synthesis of open and closed paths.
-In the case of motion generation, methods that take the branching defect into consideration, limit their search in the configuration space where Grashof condition holds true.
-To our best knowledge, no other motion generation method truly takes the motion continuity into account.
+In the case of motion generation, methods that take the branching defect into consideration limit their search into configuration space where Grashof condition holds true.
+To the authors' best knowledge, no other method truly take the motion continuity into account.
 
@@
 McGarva\cite{mcgarva1994} has taken the earliest approach towards creating a library for coupler trajectories based on harmonic analysis.
-Wandling\cite{wandling2000} has presented an atlas based approach, where coupler paths and motions are stored in terms of Fourier Transforms.
+Wandling\cite{wandling2000} has presented an atlas based approach where, coupler paths and motions are stored in terms of Fourier Transforms.
 Input motion is searched for neighbors based on euclidean distances of Fourier Transforms.
@@
 The above methods generate data based on uniform sampling in the linkage parameter space.
-Given the highly nonlinear mapping between linkage parameters and coupler trajectory, this way of sampling leads into non-uniform sampling of trajectory space causing under-representation of possible motions.
-We try to address this issue by employing log normal distribution in the linkage parameter space to generate data and perform compact clustering of the data using machine learning techniques.
-A Hierarchy is created in the database by means of clustering, where the top level comprises of few data points called cluster centers which are representative of the cluster points in the lower levels.
-Also the methods\cite{wandling2000},\cite{yue-pathgen2011} have built the library with all possible coupler curves, where one curve is broken down into many segments for creating data for partial curves.
-In contrast to this, we need to store only one curve representing all the segments in it as our representation facilitates partial matching.
+Given the highly nonlinear mapping between linkage parameters and coupler trajectory, this way of sampling leads into non-uniform sampling of trajectory space which causes under-representation of possible motions.
+We try to address this issue by employing log normal distribution in the linkage parameter space and clustering the generated data.
+Also other methods have their library consists of all possible coupler curves, where one curve is broken down into many segments for creating data for partial curves.
+In contrast to this, we need to store only one curve because our curve representation facilitates partial matching.
 No other previous method facilitates this partial matching of open motion curve into another open or closed curve.
@@
 
+A Hierarchy is created in the database by means of clustering, where top level comprises of few data points called cluster centers which are representative of the cluster points in the lower levels.
 When a user inputs a motion or a path, a query representing invariant signature \footnote{path or motion signature} of the input is raised for k nearest neighbors among cluster centers in the database.
-The neighbor is defined as motion or path whose part has a similar signature to the input. These k neighbors if needed, are subjected to fine tuning by local optimization to obtain set of solutions.
-Overall method depicted in Fig.~\ref{overallMethod} is codified in Algorithm ~\ref{alg_overall}.
+The neighbor is defined as motion or path whose part has a similar signature to the input.
+These k neighbors if needed, are subjected to fine tuning by local optimization to obtain set of solutions.
+Overall method is given in algorithm~\ref{alg_overall} and depicted in Fig.~\ref{overallMethod}.
 
@@
 Section~\ref{sec_db_ae} explains the database generation and clustering using auto-encoders for efficient sampling and query operations.
-Finally, two case studies are presented~\ref{sec_example} to showcase efficacy of the method.
+Finally, a case study is presented~\ref{sec_example} to showcase the efficacy of the method.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{Signatures of Coupler Path and Motion}\label{sec_sign}
-The main focus of the paper is a novel method for motion generation that takes a continuous task motion or path as the input and returns defect-free linkages producing similar motion or path.
+The main focus of the paper is a novel method for motion generation that takes a continuous task motion as the input and returns defect free linkages producing similar motion.
 The objective function evaluation requires the input motion to be transformed into a specific form, which we call the signature of input motion.
-This signature representation is invariant to similarity operations, which are reflection, rotation, translation and scaling.
+This signature representation is invariant to similarity operations which are reflection, rotation, translation and scaling.
 Signature for path and motion are termed as path signature and motion signature respectively.
@@
     \Output{signature //discretized signal in form of an array}
-    k(t) = ComputeCurvature(x, y) using Eq.~\ref{curvatureEq} \\
-    K(t) = IntergrateCumulatively(k(t)) using Eq.~\ref{kInt} \\
+    k(t) = ComputeCurvature(x, y) using eq.~\ref{curvatureEq} \\
+    K(t) = IntergrateCumulatively(k) using eq.~\ref{kInt} \\
     motionSignature = [] \\
@@
 \begin{eqnarray}
-  k(t) = \frac{\ddot{y}(t)\dot{x}(t) - \ddot{x}(t)\dot{y}(t)}{{(\dot{x}^2(t) + \dot{y}^2(t))}^{(\frac 32)}}, \label{curvatureEq}\\
+  k(t) = \frac{\ddot{y}(t)\dot{x}(t) - \ddot{x}(t)\dot{y}(t)}{{(\dot{x}^2(t) + \dot{y}^2(t))}^{(\frac 32)}} \label{curvatureEq}\\
   K(t) = \int^{t}_0 |k(t)|dt \label{kInt},
@@
 For an example, parametric motion could be a B-spline motion as shown in fig~\ref{bsplineFitting}.
-We compute the curvature of path along the direction of t, using Eq.~\ref{curvatureEq} and the cumulative integral by Eq.~\ref{kInt}.
+We compute the curvature of path along the direction of t, using eq.~\ref{curvatureEq} and the cumulative integral by eq.~\ref{kInt}.
 For implementation purposes, we use scipy\cite{scipy} module for computations of B-splines and their derivatives.
@@
 The general intuition is as follows:
-we know that curvature changes inversely to the scale of the curve, so when it is integrated along the scaled curve, the scale factor cancels itself out.
+we know that curvature changes inversely to the scale of the curve, so when it is integrated along the scaled curve the scale factor cancels itself out.
 Reflection operation on the motion or the path, produces flipped path signature, but motion signature remains invariant.
@@
 \end{equation}
-where $Cn(j, p, W)$ is the normalized cross-correlation value when template $p$ is matched against $W$ at $j^{th}$ index, $p_{span}$ is the length of the array $p$ and $\bar{W}(j\to j + p_{span})$ is the mean for the values of array $W$ between index range of ($j, j+p_{span}$)
+where $Cn(j, p, W)$ is the normalized cross-correlation value when template $p$ is matched to $W$ at $j^{th}$ index, $p_{span}$ is the length of the array $p$ and $\bar{W}(j\to j + p_{span})$ is the mean for the values of array $W$ between index range of ($j, j+p_{span}$)
 
@@
 Maximum score of the matching ($Cn_{max}(p, W)$) represents similarity of the template in $W$, and offset index $j$ at which maximum occurs is the start point for matching.
-As the signature reverses with reversal of the direction of sampling, we compute the correlation first in one direction and again after reversing $p$ and select the best matching score, offset index and the matching direction of sampling.
+As the signature reverses with reversal of the direction of sampling, we compute the correlation once in a normal way and again after reversing $p$ and select the best matching score, offset index and the matching direction of sampling.
 Figure~\ref{ncc} depicts normalized cross correlation function over the sliding domain $j$ for part and whole curves.
@@
 Figure~\ref{mcc} depicts dissimilarity function over the sliding domain $j$.
-In this case as shown in Fig.~\ref{mcc}, we find that the first point itself is a point where the perfect match is occurred, which is consistent with the fact that we slice the whole motion to obtain the part motion.
+In this case as shown in Fig.~\ref{mcc}, we find that the first point itself is a point where the perfect match is occurred which is consistent with the fact that we slice the motion in similar manner.
 
@@
 \subsection{Objective Function for Synthesis}
-The functions in Eq.~\req{nccEq} and ~\req{mccEq} presented in the sections \ref{sec_ncc}, \ref{sec_mcc} can be used as the error measure for path and motion synthesis of any planar linkage, where the objective is to find a linkage, that produces a motion whose part or whole corresponds to target motion (or path).
+The functions in Eq.~\req{nccEq} or ~\req{mccEq} presented in the sections \ref{sec_ncc}, \ref{sec_mcc} can be used as the error measure for path or motion synthesis of any planar linkage, where the objective is to find a linkage, that produces a motion whose part or whole corresponds to target motion (or path).
 Thus we can formulate the path synthesis problem as,
@@
 \end{equation}
-where $\textbf{\emph{l}}$ is the vector of linkage parameters for particular planar linkage, p is signature the of task curve taken as template for Normalized Cross-Correlation and ${\{W_i\}}_{i=0}^{s}$ is the signature set of all $s$ coupler paths generated by the linkage corresponding to $\textbf{\emph{l}}$.
+where $\textbf{\emph{l}}$ is the vector of linkage parameters for particular planar linkage, p is the task curve taken as template for Normalized Cross-Correlation and ${\{W_i\}}_{i=0}^{s}$ is the signature set of all coupler paths generated by the linkage.
 In case of four-bar, $\textbf{\emph{l}}: l_1, l_2, l_3, l_4, l_5$, with $l_i$ is link ratio of $i^{th}$ link shown in Fig~\ref{fourbar}.
@@
 \end{equation}
-Here, E is the Dissimilarity function from Eq.~\req{mccEq} while p and ${\{W_i\}}_{i=0}^{s}$ are motion signatures instead of path signatures.
+Here, E is the Dissimilarity function from eq.~\req{mccEq} while p and ${\{W_i\}}_{i=0}^{s}$ are motion signatures instead of path signatures.
 
@@
 Considering highly non-linear nature of the problem, finding a good initial guess proves to be game changing.
-Thus we exploit machine learning techniques to create a database for finding many good initial guesses or the solution itself.
+Thus we exploit the advantages of data driven approach for finding many good initial guesses or the solution itself.
 
@@
 Owing to the complex relationship between parameter space and generated motion, small change in linkage parameters can produce large and discontinuous structural change in the generated motions.
-For example, small change in crank length ($l_1$) can open a previously close coupler path.
+For example small change in crank length ($l_1$) can open a previously close loop.
 Most of the methods based on Fourier descriptors are if defined, can not capture the continuity at such singular locations, which adversely affect the optimization process.
 In contrast to this behavior, the signatures derived in Sec.~\ref{sec_sign} have smooth transition at these singular locations due to shape similarity between a closed and just opened curve or motion.
-
 To make our point, we perform sensitivity analysis as follows:
 A four-bar with link ratios ($l_1:0.55$, $l_2:1$, $l_3:1.5$, $l_4:1$, $l_5:1$) is subjected to gradual change in parameters $l_1$ and $l_3$ by the amount (-0.2, 0.2) in steps of 0.01.
-Error function between motions of new and initial fourbar are calculated using Eq.~\req{objectiveFunMotion} .
+Error function between motions of new and initial fourbar are calculated using eq.~\req{objectiveFunMotion} .
 Figure~\ref{saCouplerCurves} shows coupler motion of some of the four-bars while Fig.~\ref{saMotionSignatures} depicts their motion signatures.
 It can be seen from Fig.~\ref{saCouplerCurves} that there exists a discontinuity in topology of the coupler curves even though their shapes have a continuous shift.
-Our method captures this continuity, which is shown by error function evaluations depicted in Fig.~\ref{saErrorFunction}, where it is visible that surface is well behaved in the singularity region.
+Our method captures this continuity, which is shown by error function evaluations depicted in Fig.~\ref{saErrorFunction}.
 
@@
 \includegraphics[width=240pt]{figure/fig_sa_distance_function.eps}
-  \caption{Distance ($E_{min}$) from Eq.~\req{mccEq} as the parameters $l_1$ and $l_2$ are varied.
+  \caption{Distance ($E_{min}$) from eq.~\req{mccEq} as the parameters $l_1$ and $l_2$ are varied.
 Although open loop breaks at $l_1$:0.55, $l_3$:1.5, there are no spikes of error function in the region near singularity, as the shape is very similar between the two topologies.}
@@
   h_i = ReLU(W_{i}h_{i-1} + b_{i}), \\
-  ReLU(x) = max(0, x),
+  ReLU(x) = max(0, x).
 \end{eqnarray}
-where $W_i$ is weight matrix with dimensions $(d^{i}, d^{(i-1)})$ and $b_i$ is $d^{(i)}$ dimensional bias vector of $i^{th}$ layer, which are computed in the process of training.
+
+Where $W_i$ is weight matrix with dimensions $(d^{i}, d^{(i-1)})$ and $b_i$ is $d^{(i)}$ dimensional bias vector of $i^{th}$ layer, which are computed in the process of training.
 Auto-encoders are trained to reconstruct the input, in this way each layer encodes the input, which is sufficient for the next layers to reconstruct the output.
@@
 \begin{equation}\label{nnloss}
-  \argminA_{W, b} \sum_{i=0}^{N} || X_i - \tilde{X}_i ||^2,
+  \argminA_{W, b} \sum_{i=0}^{N} || X_i - \tilde{X}_i ||^2
 \end{equation}
@@
 We use Agglomerative Clustering, a method of Hierarchical clustering, which is an approach to partitioning clustering for identifying groups in the dataset.
-\emph{Ward}\cite{ward1963} criterion is used for clustering, which minimizes the variance of the clusters being merged.
+\emph{Ward}\cite{ward1963} Linkage criterion is used for clustering, which minimizes the variance of the clusters being merged.
 The distance metric used is the euclidean distance in the latent space.
@@
 When user raises one such query, we first find k nearest neighbors among $1500$ cluster centers, then descend into their clusters if needed.
-Motion with highest similarity score is returned along with its corresponding linkage parameters, which if required are further fine-tuned to match the query using local optimization methods.
+Motion with highest similarity score is returned along with its corresponding linkage parameters which if required, are further fine-tuned to match the query using local optimization.
 
@@
 We compute its path signature by the steps mentioned in Algorithm ~\ref{alg_signature} and raise the query for nearest neighbors among 1500 cluster centers of our database.
-The distance metric for finding neighbors is $1-Cn_{max}$ in Eq.~\req{objectiveFunPath}.
+The distance metric for finding neighbors is $1-Cn_{max}$ in ~\req{objectiveFunPath}.
 Table~\ref{ex1_knnLinkageData} tabulates the link ratios corresponding to obtained nine nearest neighbors.
-Next step is to compute actual parameters according to position, scale and orientation of the path.
-It is done by comparing analogous points found by offset index $j$ in Eq.~\ref{nccEq}.
+Next step is compute actual parameters according to position, scale and orientation of the path.
+It is done by comparing analogous points found by offset index $j$ in eq.~\ref{nccEq}.
 Figure ~\ref{ex1_solns} shows first eight fourbar mechanisms corresponding to nearest signatures to path signature of input.
-As it can be clearly seen, these linkages generate highly accurate paths without any defects throughout sit to stand activity.
+As it can be clearly seen these linkages generate highly accurate paths without any defects throughout sit to stand activity.
 
@@
 The task is to find a pool of linkage systems that can perform snow-shoveling with a motion shown in Fig.~\ref{motionQuery}.
-The motion data is tabulated in Table ~\ref{poseData} to which we fit a B-spline with cord length parameterization in order to get parametric representation of motion.
+The motion data is tabulated in Table ~\ref{poseData} to which we fit into a B-spline with cord length parameterization in order to get parametric representation of motion.
 The task can also be treated as a finite position motion generation and solved for valid solutions.
-We try with our real time computational methods of algebraic fitting\cite{generalfitting-JCISE},\cite{deshpande2017} but obtained solutions suffer from circuit defect, which is not surprising as those methods do not account for continuity of the input positions.
+We try with our real time computational methods of algebraic fitting\cite{generalfitting-JCISE},\cite{deshpande2017} but obtained solutions suffer from circuit defect, which is not a surprise as those methods do not account for continuity of the input positions.
 
@@
 Table ~\ref{ex2_knnLinkageData} presents the linkage parameters corresponding to the nearest neighbors along with their distance score from the task.
-Coupler motions of these linkages have a part, which matches with the shape of input motion query.
-Actual scaling and orientation of the linkage can be found out easily by comparing analogous points, which are given by the offset index $j$ that corresponds to minimum distance$(E_min)$ in Eq.~\req{mccEq}.
+Coupler motions of these linkages have a part which matches with the shape of input motion query.
+Actual scaling and orientation of the linkage can be found out easily by comparing analogous points which are given by the offset index $j$ that corresponds to minimum distance$(E_min)$ in eq.~\req{mccEq}.
 Figure~\ref{ex2_solns} depict the solutions obtained after scaling and orienting the linkage to match required motion.
@@
 As ground or fixed pivot locations should lie above the ground, all solutions except the $4^{th}$ solution are suitable for the task.
-In light of these results, we can say that this approach produces a large variety of solutions, which otherwise would be very hard to find using precision point approach.
+In light of these results, we can say that this approach produces a large variety of solutions which otherwise would be very hard to find using precision point approach.
 
@@
 This approach presents a novel optimization approach towards defect free linkage synthesis.
-The framework is highly data efficient due to similarity invariant representation of paths and motion, which also facilitates partial matching.
+The framework is highly data efficient due to similarity invariant representation of paths and motion which also facilitates partial matching.
 The method always returns defect free solutions as it is inherently taken care of.
@@
 Hierarchically clustered database provides efficient query search.
-Finally, the effectiveness of presented approach is showcased by two case studies for each of which nine defect free solutions were found.
-Although our method can provide highly accurate results, our focus here is to generate high number of defect free solutions that can perform the task in more or less similar fashion;
-because more often than not, linkage synthesis algorithms are desired to be prolific in terms of concept generation than to produce highly accurate very few solutions.
+Finally, the effectiveness of presented approach is showcased by two case studies for each of which nine defect free solutions were found in contrast to one and zero solutions respectively by our algebraic fitting based precision point method.
+Although our method can provide highly accurate results, our focus here is to generate high number of defect free solutions that can perform the task in more or less similar fashion.
+Because more often than not, linkage synthesis algorithms are desired to be prolific in terms of concept generation than to produce highly accurate very few solutions.
 

### 2018-07-04 rebuttal/rebuttal.tex
Comma fixes, Rebuttal fixes and some fixes in paper

@@
 \documentclass{article}
+\usepackage{graphicx}
 \title{Rebuttal}
@@
 To what type of real, practical problems does the method apply?
+Overall, the paper lacks a clear motivation for why the described method is required.
+Absent a strong motivation, the manuscript reads as if the authors pursued a machine-learning problem for the sake of machine learning.
+This reviewer finds little value in answering these types of research questions.
+Manuscript lacks a clear motivation linked to the practitioner.
+The research objective, methods, and approach are not clear.
 }
 
-Thank you for pointing out an important point. We have added the motivation subsection, which clearly explains the significance of the gaps in current practices.
-The defects in linkages is a major concern faced by the current state of the art methods.
-We also state that, being defect-free with respect to precision positions alone is not enough for the mechanism, to be useful.
+Thank you for pointing out an important point.
+We have rewritten the introduction section to clearly explain motivation and overview of the approach.
+The motivation subsection clearly explains the significance of the gaps in current practices.
+We summarize the motivation as follows,
+
+The classical mechanism synthesis problem deals with computing type and dimensions of a linkage system for performing specific tasks, which are categorized as the path, motion and function generation.
+Path generation task aims to synthesize a mechanism which can guide a point along a prescribed path.
+On the other hand, the objective of motion generation task is to synthesize a mechanism which can guide a rigid body along a prescribed motion.
+The prescribed path is a time sequence of positions, whereas the prescribed motion is a time sequence of positions and orientations.
+
+The majority of mechanism synthesis methods are based on the precision point approach.
+This approach is a clever approximation trick to solve the synthesis tasks, where the task is discretized into precision points.
+These points instead of the actual task, are treated as interpolation or approximation task for mechanism synthesis.
+However, this way of formulation loses important information about the actual continuous task and can lead to solutions with the order, circuit and branch defects.
+The defect in a mechanism renders itself useless for its intended application.
+
+\begin{figure}
+\centering
+\includegraphics[width=200pt]{fig_circuit_defect.eps}
+  \caption{The mechanism synthesis problem for the prescribed motion.
+  The four-bar mechanism obtained using the precision position approach suffers from circuit defect, as no coupler circuit passes through all precision positions.}
+\label{circuit_defect}
+\end{figure}
+
+Figure~\ref{circuit_defect} shows the prescribed motion and its discretized precision positions.
+In the case of motion generation problem, a four-bar can go through at most five precision positions and it is called as classical Burmester~\cite{Burmester86} problem.
+For this type of problem, only finite solutions exist and in this case only one solution is obtained as shown in the Fig.~\ref{circuit_defect}.
+Although it can be seen that coupler of the four-bar passes exactly through five precision positions, it can not do it without changing the circuit.
+A circuit represents an assembly mode in which the mechanism is put together.
+This phenomenon is called circuit defect in the linkage, which makes the linkage useless for the prescribed task.
+Even if the defect-free solution is found, the coupler motion in-between the precision points may go through undesired position and orientation.
+This happens because the method discards the functional aspect of continuous motion and turns it into a vacuous interpolation problem.
+This tells us that just finding a defect-free linkage with respect to the precision positions is not enough to qualify as a useful mechanism.
+
+To capture the complete prescribed task, we represent it as a continuous parametric curve.
+The objective is to find a linkage, that has a coupler motion or path compatible with the task.
+Next step is to conduct a search in the space of linkage parameters to find linkages with coupler motions compatible with the prescribed task.
+Although global search methods can be applied for finding solutions, we employ an efficiently clustered database and Powell's local search method to come up with a variety of different solutions.
+We exploit machine learning to maximize the diversity, and for efficient storage of the linkage database.
+The outcomes of this approach are a large number of diverse concept solutions.
+The importance of diverse concept generation is mentioned in motivation subsection by following lines,
+``Thus, the synthesis method should be prolific in terms of concept generation to 1) realize the potential of attainable design possibilities, and 2) have the agility to adapt a design to evolving requirements."
 \\
@@
   \item \emph{
-Overall, the paper lacks a clear motivation for why the described method is required.
 Further, most of the citations in the manuscript, not including the authors' previous work, are over 10 years old.
@@
 
-Thanks, we are added recent citations reporting the work in the area of mechanism synthesis, and machine learning applications to mechanisms.
-\\
-
-  \item \emph{
-    Absent a strong motivation, the manuscript reads as if the authors pursued a machine-learning problem for the sake of machine learning.
-This reviewer finds little value in answering these types of research questions.
-  }
-
-We exploit machine learning to maximize the diversity, and for efficient storage of the linkage database.
-The outcomes of this approach are a large number of diverse concept solutions.
-The importance of diverse concept generation is mentioned in motivation subsection by following lines,
-"Thus, the synthesis method should be prolific in terms of concept generation to 1) realize the potential of attainable design possibilities, and 2) have the agility to adapt a design to evolving requirements."
+Thanks, we have added recent citations reporting the work in the area of mechanism synthesis and machine learning applications to mechanisms.
 \\
@@
 Thank you for your comments.
-We have added one example in the motivation section, which clearly explains the limitations of current practices.
-We use the same example in the example sections, to clearly juxtapose our results against results of precision point approach.
-\\
-
-  \item \emph{
-Manuscript lacks a clear motivation linked to the practitioner.
-The research objective, methods, and approach are not clear.
-}
-
-Thank you for the feedback.
-We have rewritten the introduction sections, to clearly explain motivation and overview of the approach.
+We have added the example shown in the Fig.~\ref{circuit_defect} to the motivation section, which clearly explains the limitations of current practices.
+We have used the same example in the example section to clearly juxtapose our results against results of precision point approach.
 \\
@@
 
-"In order to have efficient query operations, we perform Hierarchical Clustering; a method that summarizes and creates a hierarchy in the database.
+``In order to have efficient query operations, we perform Hierarchical Clustering; a method that summarizes and creates a hierarchy in the database.
 Clustering in higher dimensions suffers from \emph{Curse of Dimensionality}\cite{marimont1979}, thus we first perform dimensionality reduction using Auto-encoder Neural Networks.
@@
 In addition to that, we have added following lines to explain the motivation behind using clustering,
-"We use machine learning techniques such as clustering and data-compression using auto-encoder neural networks to come up with good initial guesses for local optimization.
+``We use machine learning techniques such as clustering and data-compression using auto-encoder neural networks to come up with good initial guesses for local optimization.
 First, We cluster the database using hierarchical clustering algorithm.
@@
   \item \emph{
-  In Fig. 1 (overview), should an arrow return from "Local Optimizer" to "Accurate?" or is the assumption that all outputs from the "Local Optimizer" are accurate?
+  In Fig. 1 (overview), should an arrow return from ``Local Optimizer" to ``Accurate?" or is the assumption that all outputs from the ``Local Optimizer" are accurate?
 }
 
-Thanks for catching that, we fixed it.
+Thank you for mentioning that.
+We have fixed it.
 \\
@@
 
-Thank you for the comment. We made following changes in the lines,
-"
-To illustrate this via example, we perform sensitivity analysis in the vicinity of a singularity as follows... ",
-and added, "The link ratios are chosen such that, small changes in some parameters lead to a topological change in the coupler curve."
+Thank you for the comment. We have added following line,
+``The link ratios are chosen such that, small changes in some parameters lead to a topological change in the coupler curve."
 \\
@@
 We have employed already proven techniques such as b-spline interpolation, hierarchical clustering, data compression using auto-encoders, Powell's local search.
-We formulate the signatures of coupler path and motion, based on proven 2D curve matching technique by Cui et al.\cite{cui2009}.
-We present the validation of the partial matching algorithms using examples in section 4.
+We have formulated the signatures of coupler path and motion, based on proven 2D curve matching technique by Cui et al.\cite{cui2009}.
+We have presented the validation of the partial matching algorithms using examples in section 4.
 Finally, we present two case studies, where we obtain the diverse set of useful linkage solutions for path and motion generation problem.
@@
 
-Thanks for the important feedback, we have modified the conclusion by adding critical discussion of the research.
+Thanks for the important feedback, we have modified the conclusion by adding critical assessment of the approach as follows,
+`` The problem formulation is invariant with respect to translation, orientation, and scaling.
+Hence, constraints like geometric restrictions on pivots have to be addressed after finding feasible solutions for the task.
+The approach is general enough to be extended to higher order linkage systems for which there are even fewer methods available for synthesizing defect-free solutions.
+However, the database size increases exponentially with the number of links in the mechanisms.
+As an example, a Watt type six-bar database needs to be roughly 400 times larger than four-bar database.
+
+A potential solution to this problem could be to use learning based methods, where the pattern is learned instead of storing all of the information.
+Overall, the method provides a holistic approach towards the prescribed path and motion synthesis and encourages artificial intelligence techniques to make an impact.
+"
 
   \item \emph{
- Review the usage of "that" versus "which". There are some instances where the usage should be reversed.
+ Review the usage of ``that" versus ``which". There are some instances where the usage should be reversed.
  \\
- Several instances exist throughout the manuscript where nouns could benefit from having a "the" put in from of them.
-For example, the first sentence of Section 5.1 reads as, "Each data point in the database consists of discrete..." Instead, the sentence should read as, "Each data point in [the] database consists of discrete..."
+ Several instances exist throughout the manuscript where nouns could benefit from having a ``the" put in from of them.
+For example, the first sentence of Section 5.1 reads as, ``Each data point in the database consists of discrete..." Instead, the sentence should read as, ``Each data point in [the] database consists of discrete..."
  Check usage of hyphens. Inconsistent usage exists in the manuscript.
@@
 
-Thanks for catching that. It was a plotting mistake. We fixed it.
+Thank you for the comment. It was a plotting mistake. We have fixed it.
 \\
@@
 
-Thanks for catching those. We fixed them. Thanks
+Thanks for the comments. We have fixed them.
 \\
@@
 Thanks for the feedback. We have made changes in the text to clarify which metric is used at what point.
-In section 5.1, we added following lines, "The distance metric used for clustering is the Euclidean distance in the latent space.
+In section 5.1, we added following lines, ``The distance metric used for clustering is the Euclidean distance in the latent space.
 Although the more accurate distance metric is distance function discussed in sec 3, it is very expensive to calculate it for the entire database.
@@
 Now, when the user raises a query, we use the distance function from sec.3 for finding $k$ nearest neighbors among $1500$ cluster centers.
-If a cluster center is not sufficiently close, we descend into its corresponding cluster to find the closest data point. "
-" The distance metric for finding neighbors among cluster centers is $1-Cn_{max}$ in Eq. 5.  "
+If a cluster center is not sufficiently close, we descend into its corresponding cluster to find the closest data point.
+The distance metric for finding neighbors among cluster centers is $1-Cn_{max}$ in Eq. 5.  "
 \\
@@
 We use the cluster centers as independent initial guesses and do a local search on each initial guess independently.
-We added following lines in section 5 to clarify that.
+We have added following lines in section 5 to clarify that.
 
-"When a query is raised in the database, the first step is to search for neighbors in the set of cluster centers.
+``When a query is raised in the database, the first step is to search for neighbors in the set of cluster centers.
 This often yields a diverse set of neighbors, and is used as a set of independent initial guesses for local optimization."
@@
 
-Thank you for mentioning that. We added following lines in the conclusion.
-"The partial matching metric although more accurate, but is expensive in terms of computation cost.
+Thank you for mentioning that. We have added following lines in the conclusion.
+``The partial matching metric although more accurate, but is expensive in terms of computation cost.
 Thus, we use Euclidean metric in the latent space of compressed data for hierarchical clustering.

### 2018-07-04 idetc2018_journal.tex
Comma fixes, Rebuttal fixes and some fixes in paper

@@
 The classical mechanism synthesis problem deals with computing type and dimensions of a linkage system for performing specific tasks, which are categorized as the path, motion and function generation.
-Path generation task aims to synthesize a mechanism, which can guide a point along a prescribed path.
-On the other hand, the objective of motion generation task is to synthesize a mechanism, which can guide a rigid body along a prescribed motion\footnote{motion is the combination of position and orientation.}.
+Path generation task aims to synthesize a mechanism which can guide a point along a prescribed path.
+On the other hand, the objective of motion generation task is to synthesize a mechanism which can guide a rigid body along a prescribed motion.
+The prescribed path is a time sequence of positions, whereas the prescribed motion is a time sequence of positions and orientations.
 For an exhaustive reference, see books from McCarthy and Soh \cite{sohmccarthy}, Sandor and Erdman~\cite{Sandor}, Hunt~\cite{Hunt78}, Hartenberg and Denavit \cite{Hartenberg},  Suh and Radcliffe \cite{Suh78}, and Lohse \cite{lohse2013}.
@@
 In the majority of the methods, the first step is choosing a mechanism type and then calculating the design parameters of chosen mechanism type.
-The prior step is called Type Synthesis, and the later step is Dimension Synthesis.
+The first step is called as Type Synthesis, and the later step is called as Dimension Synthesis.
 This paper presents an approach to Dimension Synthesis of planar four-bar linkages, but the approach is general enough to be applied on any planar linkage.
@@
 This approach is a clever approximation trick to solve the abovementioned tasks, where the task is discretized into precision points.
-These points, instead of the actual task, are now treated as interpolation or approximation task for mechanism synthesis.
+These points instead of the actual task, are treated as interpolation or approximation task for mechanism synthesis.
 However, this way of formulation loses important information about the actual continuous task and can lead to solutions with the order, circuit and branch defects.
@@
 Figure~\ref{circuit_defect} shows the prescribed motion and its discretized precision positions.
-In the case of motion generation problem, a four-bar can go through at most five precision positions, and it is called as classical Burmester~\cite{Burmester86} problem.
-For this type of problem, only finite solutions exist and in this case, only one solution is obtained as shown in Fig.~\ref{circuit_defect}.
-It can be seen that, although coupler of the four-bar passes exactly through five precision positions, it can not do it without changing the circuit.
+In the case of motion generation problem, a four-bar can go through at most five precision positions and it is called as classical Burmester~\cite{Burmester86} problem.
+For this type of problem, only finite solutions exist and in this case only one solution is obtained as shown in the Fig.~\ref{circuit_defect}.
+Although it can be seen that coupler of the four-bar passes exactly through five precision positions, it can not do it without changing the circuit.
 A circuit represents an assembly mode in which the mechanism is put together.
@@
 To deal with it, a naive approach is to tweak precision positions in a brute-force way within the tolerance until a solution is found.
-Even if the defect-free solution is found, the coupler motion in-between the precision points may not have the desired properties.
+Even if the defect-free solution is found, the coupler motion in-between the precision points may go through undesired position and orientation.
 This happens because the method discards the functional aspect of continuous motion and turns it into a vacuous interpolation problem.
-This tells us that just finding a defect-free linkage with respect to the precision positions, is not enough to qualify as a useful mechanism.
+This tells us that just finding a defect-free linkage with respect to the precision positions is not enough to qualify as a useful mechanism.
 
@@
 Thus, it is readily scalable to any type of planar linkage.
-In section~\ref{subsec_motiongen}, we present the obtained solutions for the prescribed motion presented in Fig.~\ref{circuit_defect}.
+In section~\ref{subsec_motiongen}, we present the obtained solutions for the prescribed motion presented in the Fig.~\ref{circuit_defect}.
 
-\subsection{Literature Survey}
+\subsection{Literature Survey and Overview}
 % Global search methods
@@
 The above methods can produce many defect-free solutions and are scalable to any type of linkages.
-However, these methods tend to be slow and inefficient, as they start from scratch for every instance, and with no guarantee of converging to an acceptable solution.
+However, these methods tend to be slow and inefficient as they start from scratch for every instance with no guarantee of converging to an acceptable solution.
 
@@
 Ullah and Kota\cite{ullah1997} have presented an invariant approach towards representation and synthesis of closed loop paths through shape optimization.
-They use a combination of global and local search methods for optimizing Fourier Deviant function, to compute the dimensions of planar four-bar linkages without an initial guess.
-Wu et al.\cite{wu2011} presented a method based on finite Fourier series for open and closed path generation, but it is specific to four-bar mechanisms.
+They use a combination of global and local search methods for optimizing Fourier Deviant function to compute the dimensions of planar four-bar linkages without an initial guess.
+Wu et al.\cite{wu2011} presented a method based on finite Fourier series for open and closed path generation of four-bar mechanisms.
 In the case of motion generation, Li et al.\cite{li2016} have developed a Fourier descriptor-based approach for approximate motion generation.
@@
 %  ---
-\subsection{The Method Overview}
 
-The original contributions in the paper are as follows:
-
-1) a perceptive problem formulation for path and motion generation, that solves the issues associated with precision point approach.
-The formulation is based on a measure of dissimilarity between two planar motions or paths, which is invariant to similarity transforms.
-2) we exploit the nonlinear nature of the relationship between the linkage parameters and coupler motions to create a sensitive, wide-ranging, compact, and efficient database with hierarchical clustering.
-
-%In this paper, we 1) employ pattern recognition and computational shape analysis, to create a similarity transform-independent signature for coupler path and motion, 2) exploit the nonlinear nature of relationship between the linkage parameters and coupler motions to create a sensitive, wide-ranging, compact, and efficient database with hierarchical clustering, and 3) enable dimensionality reduction using Auto-encoder Neural Networks.
-
-In this paper, we employ pattern recognition and computational shape analysis, to create a similarity transform-independent signature for coupler path and motion.
-When a user provides the prescribed motion or path, a query representing invariant signature \footnote{path or motion signature} of the input is raised for $k$ nearest neighbors among cluster centers in the database.
+The synthesis routine starts by creating a continuous parametric representation of a prescribed path or motion.
+we employ pattern recognition and computational shape analysis to create a similarity transform-independent signature for a parametric path and motion.
+A query representing invariant signature \footnote{path or motion signature} of the prescribed path or motion is raised for $k$ nearest neighbors among cluster centers in the database.
 These $k$ neighbors, if needed, are subjected to fine-tuning by local optimization to obtain a set of defect-free solutions.
@@
 Figure~\ref{overallMethod} illustrates an overview of our method, which is codified in Algorithm~\ref{alg_overall}.
+
+The original contributions in the paper are as follows:
+1) a perceptive problem formulation for path and motion generation, that solves the issues associated with precision point approach,
+%The formulation is based on a measure of dissimilarity between two planar motions or paths, which is invariant to similarity transforms.
+2) we exploit the nonlinear nature of the relationship between the linkage parameters and coupler motions to create a sensitive, wide-ranging, compact, and efficient database with hierarchical clustering, and 3) an algorithm for partial matching of motions and paths which significantly improves the synthesis of open prescribed tasks.
+
+%In this paper, we 1) employ pattern recognition and computational shape analysis to create a similarity transform-independent signature for coupler path and motion, 2) exploit the nonlinear nature of relationship between the linkage parameters and coupler motions to create a sensitive, wide-ranging, compact, and efficient database with hierarchical clustering, and 3) enable dimensionality reduction using Auto-encoder Neural Networks.
 
@@
 Here, $p$ acts as a template that tries to find the best match against $W$ while sliding over it along $j$.
-Domain of $Cn(j, p, W)$ is [0, 1], where 1 represents the complete embedment\footnote{\emph{Path} is identical to a portion of \emph{Whole}.} of $p$ inside $W$.
+Domain of $Cn(j, p, W)$ is [0, 1], where 1 represents the complete embedment\footnote{\emph{Part} is identical to a portion of \emph{Whole}.} of $p$ inside $W$.
 
@@
 where $W_i$ is weight matrix with dimensions $(d^{i}, d^{(i-1)})$ and $b_i$ is $d^{(i)}$ dimensional bias vector of $i^{th}$ layer, which are computed in the process of training.
-Auto-encoders are trained to reconstruct the input, in this way each layer encodes the input, which is sufficient for the next layers to reconstruct the output.
+Auto-encoders are trained to reconstruct the input.
+In this way each layer encodes the input, which is sufficient for the next layers to reconstruct the output.
 The objective of training is to find out the set of weights and biases that minimizes the error loss given by,
@@
 If a cluster center is not sufficiently close, we descend into its corresponding cluster to find the closest data point.
-Motion with highest similarity score is returned along with its corresponding linkage parameters, which if required, are further fine-tuned to match the query using local optimization methods.
+Motion with highest similarity score is returned along with its corresponding linkage parameters.
+If required, the parameters are fine-tuned to match the query using local optimization methods.
 Computationally, on a 2.4 GHz Core i5 MacBook Pro with 8 GB memory, every query takes 23 seconds on average to find the sorted list of nearest neighbors among cluster centers.
@@
 Also, It is obvious that the coupler should not drop the snow during its entire motion except at the end.
-The prescribed motion entails this information.
-However, precision point approach cannot capture it.
+Although, the prescribed motion entails this information, precision point approach cannot capture it.
 
@@
 The first step is to calculate motion signature of the task motion using steps mentioned in Algorithm ~\ref{alg_signature}.
-For that, we follow the steps given in section~\ref{sec_sign} to obtain the motion signature depicted in Fig.~\ref{queryResult}.
+For that we follow the steps given in section~\ref{sec_sign} to obtain the motion signature depicted in Fig.~\ref{queryResult}.
 Next, we raise the signature query for nearest signatures among cluster centers of the database.
@@
 Thus, we present a perceptive problem formulation, by considering the entire prescribed task.
-We solve the formulation by employing machine-learning techniques and generate a large number of defect-free conceptual designs.
+We solve the proposed formulation by employing machine-learning techniques and generate a large number of defect-free conceptual designs.
 The approach is highly data-efficient due to similarity invariant representation and partial matching.
@@
 The problem formulation is invariant with respect to translation, orientation, and scaling.
-Hence, constraints like geometric restrictions on pivots, have to be addressed after finding feasible solutions for the task.
+Hence, constraints like geometric restrictions on pivots have to be addressed after finding feasible solutions for the task.
 The approach is general enough to be extended to higher order linkage systems for which there are even fewer methods available for synthesizing defect-free solutions.
 However, the database size increases exponentially with the number of links in the mechanisms.
+As an example, a Watt type six-bar database needs to be roughly 400 times larger than four-bar database.
 A potential solution to this problem could be to use learning based methods, where the pattern is learned instead of storing all of the information.

### 2018-07-04 idetc2018_journal.tex
minor typos

@@
 Various approaches have been proposed in the literature with aim of finding acceptable solutions for path and motion generation problem.
-In the majority of the methods, the first step is choosing a mechanism type and then calculating the design parameters of chosen mechanism type.
+In the majority of methods, the first step is choosing a mechanism type and then calculating the design parameters of chosen mechanism type.
 The first step is called as Type Synthesis, and the later step is called as Dimension Synthesis.
@@
 In the case of motion generation problem, a four-bar can go through at most five precision positions and it is called as classical Burmester~\cite{Burmester86} problem.
-For this type of problem, only finite solutions exist and in this case only one solution is obtained as shown in the Fig.~\ref{circuit_defect}.
+For this type of problem, only finite solutions exist and in this case, only one solution is obtained as shown in the Fig.~\ref{circuit_defect}.
 Although it can be seen that coupler of the four-bar passes exactly through five precision positions, it can not do it without changing the circuit.
@@
 The synthesis routine starts by creating a continuous parametric representation of a prescribed path or motion.
-we employ pattern recognition and computational shape analysis to create a similarity transform-independent signature for a parametric path and motion.
+we employ pattern recognition and computational shape analysis to create an invariant signature for the prescribed path and motion.
 A query representing invariant signature \footnote{path or motion signature} of the prescribed path or motion is raised for $k$ nearest neighbors among cluster centers in the database.
@@
 %The formulation is based on a measure of dissimilarity between two planar motions or paths, which is invariant to similarity transforms.
-2) we exploit the nonlinear nature of the relationship between the linkage parameters and coupler motions to create a sensitive, wide-ranging, compact, and efficient database with hierarchical clustering, and 3) an algorithm for partial matching of motions and paths which significantly improves the synthesis of open prescribed tasks.
+2) we exploit the nonlinear nature of the relationship between the linkage parameters and coupler motions to create a sensitive, wide-ranging, compact, and efficient database with hierarchical clustering, and 3) an algorithm for partial matching of motions and paths which significantly improves the synthesis.
 
@@
 Consider a motion given in parametric form as, $x:x(t), y:y(t), \theta:\theta(t)$.
-Where, $\theta(t)$ is the change in orientation along the path with respect to initial orientation.
+Where $\theta(t)$ is the change in orientation along the path with respect to initial orientation.
 It should be noted that $\theta(t)$ is a continuous curve with domain ($-\infty$, $\infty$) in contrast to conventional domain i.e. [$-\pi$, $\pi$].
@@
 Auto-encoders are trained to reconstruct the input.
-In this way each layer encodes the input, which is sufficient for the next layers to reconstruct the output.
+In this way, each layer encodes the input, which is sufficient for the next layers to reconstruct the output.
 The objective of training is to find out the set of weights and biases that minimizes the error loss given by,
@@
 Also, It is obvious that the coupler should not drop the snow during its entire motion except at the end.
-Although, the prescribed motion entails this information, precision point approach cannot capture it.
+Although the prescribed motion entails this information, precision point approach cannot capture it.
 
@@
 The first step is to calculate motion signature of the task motion using steps mentioned in Algorithm ~\ref{alg_signature}.
-For that we follow the steps given in section~\ref{sec_sign} to obtain the motion signature depicted in Fig.~\ref{queryResult}.
+For that, we follow the steps given in section~\ref{sec_sign} to obtain the motion signature depicted in Fig.~\ref{queryResult}.
 Next, we raise the signature query for nearest signatures among cluster centers of the database.
@@
 However, the database size increases exponentially with the number of links in the mechanisms.
-As an example, a Watt type six-bar database needs to be roughly 400 times larger than four-bar database.
+As an example, a Watt type six-bar database needs to be roughly 400 times larger than the four-bar database.
 A potential solution to this problem could be to use learning based methods, where the pattern is learned instead of storing all of the information.

### 2018-07-04 rebuttal/rebuttal.tex
minor typos

@@
 We have rewritten the introduction section to clearly explain motivation and overview of the approach.
-The motivation subsection clearly explains the significance of the gaps in current practices.
+The motivation subsection clearly explains significance of the gaps in current practices.
 We summarize the motivation as follows,
@@
 This happens because the method discards the functional aspect of continuous motion and turns it into a vacuous interpolation problem.
-This tells us that just finding a defect-free linkage with respect to the precision positions is not enough to qualify as a useful mechanism.
+This tells us that just being a defect-free linkage with respect to the precision positions is not enough to qualify as a useful mechanism.
 
@@
 The outcomes of this approach are a large number of diverse concept solutions.
-The importance of diverse concept generation is mentioned in motivation subsection by following lines,
-``Thus, the synthesis method should be prolific in terms of concept generation to 1) realize the potential of attainable design possibilities, and 2) have the agility to adapt a design to evolving requirements."
+
+The importance of diverse concept generation is mentioned in motivation subsection as follows,
+``The synthesis method should be prolific in terms of concept generation to 1) realize the potential of attainable design possibilities, and 2) have the agility to adapt a design to evolving requirements."
 \\
@@
 
-Thanks, we have added recent citations reporting the work in the area of mechanism synthesis and machine learning applications to mechanisms.
+Thanks, we have added recent citations reporting work in the area of mechanism synthesis and machine learning applications to mechanisms.
 \\
@@
 
-We have expanded the reason for employing machine learning techniques in the subsection titled 'Dimensionality Reduction using Auto-Encoders' as follows,
+We have expanded the reason for employing machine learning techniques in the subsection titled `Dimensionality Reduction using Auto-Encoders' as follows,
 
@@
 
-In addition to that, we have added following lines to explain the motivation behind using clustering,
+In addition to that, we have added following lines to explain the motivation behind clustering,
 ``We use machine learning techniques such as clustering and data-compression using auto-encoder neural networks to come up with good initial guesses for local optimization.
 First, We cluster the database using hierarchical clustering algorithm.
-Then, we find representative data point in each cluster called cluster center and form their set.
+Then, we find representative data point in each cluster called cluster centers and form their set.
 This set of cluster centers represent a diverse group of linkages.
@@
 Thanks for the important feedback, we have modified the conclusion by adding critical assessment of the approach as follows,
+
 `` The problem formulation is invariant with respect to translation, orientation, and scaling.
@@
 $7.$ In section 5.1, it is argued that Euclidean distance is used as the distance metric in latent space for
-computational efficiency, whereas in section 6.1, $(1 − Cn)$ is mentioned as the distance
+computational efficiency, whereas in section 6.1, $(1 - C_n)$ is mentioned as the distance
 metric. Please clarify.
@@
 Thanks for the feedback. We have made changes in the text to clarify which metric is used at what point.
-In section 5.1, we added following lines, ``The distance metric used for clustering is the Euclidean distance in the latent space.
+In section 5.1, we added following lines,
+
+``The distance metric used for clustering is the Euclidean distance in the latent space.
 Although the more accurate distance metric is distance function discussed in sec 3, it is very expensive to calculate it for the entire database.
@@
 
-Thank you for mentioning that. We have added following lines in the conclusion.
-``The partial matching metric although more accurate, but is expensive in terms of computation cost.
-Thus, we use Euclidean metric in the latent space of compressed data for hierarchical clustering.
-The formulation is invariant with respect to translation, orientation, and scaling.
+Thank you for mentioning that. We have added following lines in the conclusion,
+`` The formulation is invariant with respect to translation, orientation, and scaling.
 Hence, constraints like geometric restrictions on pivots, have to be addressed after finding feasible solutions for the task."

### 2018-07-04 idetc2018_journal.tex
minor typos

@@
 First, We cluster the database using hierarchical clustering algorithm.
-Then, we find representative data point in each cluster called cluster center and form their set.
+Then, we find representative data point in each cluster called cluster centers and form their set.
 This set of cluster centers represent a diverse group of linkages.

### 2018-07-28 idetc2018_journal.tex
Professor's change

@@
 \begin{abstract}
-The past forty years of research in mechanism synthesis has witnessed an unprecedented volume of work in formulating and solving planar four-bar linkage synthesis problems.
-However, finding practical and useful mechanisms for the motion synthesis problem has proven to be elusive, as a large majority of mechanisms turn out to be defective with respect to their assembly modes.
-Most methods formulate the problem as a discrete precision position problem, which inherently ignores the continuity information in the input, resulting in linkages with branch-, circuit- and order-defects.
+Synthesizing defect-free planar four-bar mechanism for the motion generation problem has proven to be a difficult problem.
+These defects can be one or more of branch-, circuit-, and order-defects, which render synthesized mechanisms useless to practitioners.
+Such defects arise from the artificial constraints of formulating the problem as a discrete precision position problem and the corresponding methods which ignore the continuity information in the input.
 In this paper, we bring together diverse fields of pattern recognition, machine learning, artificial neural network, and computational kinematics to present a novel approach that solves this problem both efficiently and effectively.
-At the heart of this approach lies an objective function that compares the motion as a whole thereby capturing designer's intent.
-In contrast to widely used structural error or loop-closure equation based error functions which convolute the optimization by considering shape, size, position, and orientation simultaneously, this objective function computes motion difference in a form, which is invariant to similarity transformations.
-We employ auto-encoder neural networks to create a compact and clustered database of invariant motions of known linkages.
-The query is raised in the database for nearest neighbors, which are either solutions or good initial conditions for fast local optimization techniques.
+At the heart of this approach lies an objective function which compares the motion as a whole thereby capturing designer's intent.
+In contrast to widely used structural error or loop-closure equation based error functions which convolute the optimization by considering shape, size, position, and orientation of the given task simultaneously, this objective function computes motion difference in a form, which is invariant to similarity transformations.
+We employ auto-encoder neural networks to create a compact and clustered database of invariant motions of known defect-free linkages, which serve as a good initial choice for further optimization.
 In spite of highly nonlinear parameters space, our approach discovers a wide pool of defect-free solutions very quickly.
 We show that by employing proven machine learning techniques, this work could have far-reaching consequences to creating a multitude of useful and creative conceptual design solutions for mechanism synthesis problems, which go beyond planar four-bar linkages.
+
+%The past forty years of research in mechanism synthesis has witnessed an unprecedented volume of work in formulating and solving planar four-bar linkage synthesis problems.
+%However, finding practical and useful mechanisms for the motion synthesis problem has proven to be elusive, as a large majority of mechanisms turn out to be defective with respect to their assembly modes.
+%Most methods formulate the problem as a discrete precision position problem, which inherently ignores the continuity information in the input, resulting in linkages with branch-, circuit- and order-defects.
+%In this paper, we bring together diverse fields of pattern recognition, machine learning, artificial neural network, and computational kinematics to present a novel approach that solves this problem both efficiently and effectively.
+%At the heart of this approach lies an objective function that compares the motion as a whole thereby capturing the designer's intent.
+%In contrast to widely used structural error or loop-closure equation based error functions which convolute the optimization by considering shape, size, position, and orientation simultaneously, this objective function computes motion difference in a form, which is invariant to similarity transformations.
+%We employ auto-encoder neural networks to create a compact and clustered database of invariant motions of known linkages.
+%The query is raised in the database for nearest neighbors, which are either solutions or good initial conditions for fast local optimization techniques.
+%In spite of highly nonlinear parameters space, our approach discovers a wide pool of defect-free solutions very quickly.
+%We show that by employing proven machine learning techniques, this work could have far-reaching consequences to creating a multitude of useful and creative conceptual design solutions for mechanism synthesis problems, which go beyond planar four-bar linkages.
 
@@
 \section{Introduction}
+The mechanism synthesis problem deals with computing type and dimensions of a linkage system for performing specific tasks, which are often categorized as path, motion and function generation; see McCarthy and Soh \cite{sohmccarthy}, Sandor and Erdman~\cite{Sandor}, Hunt~\cite{Hunt78}, Hartenberg and Denavit \cite{Hartenberg},  Suh and Radcliffe \cite{Suh78}, and Lohse \cite{lohse2013}.
+Path generation task aims to synthesize a mechanism which can guide a particular point of a rigid body (often, the coupler) along a prescribed path.
+On the other hand, the objective of the motion generation task is to synthesize a mechanism which can guide a rigid body along a prescribed motion.
+The prescribed path is given as a time sequence of positions, whereas the prescribed motion is given as a time sequence of positions and orientations.
+Various approaches have been proposed in the literature with aim of finding acceptable solutions for path and motion generation problem.
+This paper is concerned with calculating the dimensional parameters of defect-free planar four-bar mechanisms while providing machine designers a robust set of defect-free mechanism design solutions during the conceptual design phase, and thereby dramatically broadening the inventions design capabilities.
+
+A large majority of mechanism synthesis methods are based on the precision point approach.
+This approach is a clever approximation trick to solve the above-mentioned problems, where the task is discretized into precision points.
+These points instead of the actual task, are required to be interpolated or approximated by the designed mechanism.
+However, this representation loses critical information about the actual continuous task and can lead to mechanisms with the order, circuit and branch defects; see Chase and Mirth\cite{chasemirth} for a thorough discussion on such defects.
+Unfortunately, these defects render mechanisms useless for their intended application.
 \begin{figure}
@@
 \includegraphics[width=200pt]{figure/fig_circuit_defect.eps}
-  \caption{The mechanism synthesis problem for the prescribed motion.
-  The four-bar mechanism obtained using the precision position approach suffers from circuit defect, as no coupler circuit passes through all precision positions.}
+  \caption{The four-bar mechanism obtained using the precision position approach suffers from circuit defect, as no coupler circuit passes through all precision positions.}
 \label{circuit_defect}
 \end{figure}
+For an example, consider a motion generation problem shown in Fig.~\ref{circuit_defect}, where the objective is to synthesize a four-bar mechanism that can perform the prescribed motion going continuously from pose\footnote{We refer to a pose as an entity that combines position and orientation.} 1 to 5.
+Instead of dealing with an infinite number of poses from initial to final pose, currently this problem is simplified to design a four-bar that goes through all the five poses without any guarantee on the in-between motion.
+Burmester~\cite{Burmester86} showed that a four-bar can go through at most five precision positions and in the best case scenario, there are a limited number of solutions.
+In this case, only one solution is obtained as shown in the Fig.~\ref{circuit_defect}.
+Although it can be seen that the coupler of the four-bar passes exactly through five precision positions, it can not do so without changing the circuit.
+A circuit represents an assembly mode in which the mechanism is put together and to transition from one circuit to another, the mechanism has to be taken apart and reassembled.
+This phenomenon is called circuit defect in the linkage, which makes the linkage useless for the prescribed task.
+To deal with it, an approach proposed in the literature is to tweak precision positions in a brute-force way within some tolerance until a solution is found.
+Even if a circuit defect-free solution is found, the coupler motion in-between the precision points may go through undesired poses or in an incorrect order.
+This is an outcome of discarding the functional aspect of continuous motion and turning the problem into an interpolation problem bereft of important details.
+We present our solution to the motion generation problem shown in the Fig.~\ref{circuit_defect} later on in the Case Studies section.
 
-\begin{figure*}
-\centering
-\includegraphics[width=\textwidth]{figure/overall_approach.eps}
-  \caption{The Machine Learning approach begins by creating an invariant signature for the path and the motion data, which facilitates a compact and hierarchical clustered database and an auto-encoder Neural Network trained to elicit good, defect-free solutions or subjected to local, fast optimization.
-The results are astonishingly good, defect-free concept design solutions for input problems.}
-\label{overallMethod}
-\end{figure*}
-
-The classical mechanism synthesis problem deals with computing type and dimensions of a linkage system for performing specific tasks, which are categorized as the path, motion and function generation.
-Path generation task aims to synthesize a mechanism which can guide a point along a prescribed path.
-On the other hand, the objective of motion generation task is to synthesize a mechanism which can guide a rigid body along a prescribed motion.
-The prescribed path is a time sequence of positions, whereas the prescribed motion is a time sequence of positions and orientations.
-For an exhaustive reference, see books from McCarthy and Soh \cite{sohmccarthy}, Sandor and Erdman~\cite{Sandor}, Hunt~\cite{Hunt78}, Hartenberg and Denavit \cite{Hartenberg},  Suh and Radcliffe \cite{Suh78}, and Lohse \cite{lohse2013}.
-Various approaches have been proposed in the literature with aim of finding acceptable solutions for path and motion generation problem.
-In the majority of methods, the first step is choosing a mechanism type and then calculating the design parameters of chosen mechanism type.
-The first step is called as Type Synthesis, and the later step is called as Dimension Synthesis.
-This paper presents an approach to Dimension Synthesis of planar four-bar linkages, but the approach is general enough to be applied on any planar linkage.
-
-\subsection{Motivation}
-The majority of mechanism synthesis methods are based on the precision point approach.
-This approach is a clever approximation trick to solve the abovementioned tasks, where the task is discretized into precision points.
-These points instead of the actual task, are treated as interpolation or approximation task for mechanism synthesis.
-However, this way of formulation loses important information about the actual continuous task and can lead to solutions with the order, circuit and branch defects.
-The defect in a mechanism renders itself useless for its intended application.
-The defects in the single degree of freedom mechanisms are thoroughly discussed by Chase and Mirth\cite{chasemirth}.
-
-Let's see an example of this in a motion generation task.
-The objective is to synthesize a four-bar mechanism that can perform the prescribed motion.
-Figure~\ref{circuit_defect} shows the prescribed motion and its discretized precision positions.
-In the case of motion generation problem, a four-bar can go through at most five precision positions and it is called as classical Burmester~\cite{Burmester86} problem.
-For this type of problem, only finite solutions exist and in this case, only one solution is obtained as shown in the Fig.~\ref{circuit_defect}.
-Although it can be seen that coupler of the four-bar passes exactly through five precision positions, it can not do it without changing the circuit.
-A circuit represents an assembly mode in which the mechanism is put together.
-This phenomenon is called circuit defect in the linkage, which makes the linkage useless for the prescribed task.
-To deal with it, a naive approach is to tweak precision positions in a brute-force way within the tolerance until a solution is found.
-Even if the defect-free solution is found, the coupler motion in-between the precision points may go through undesired position and orientation.
-This happens because the method discards the functional aspect of continuous motion and turns it into a vacuous interpolation problem.
-This tells us that just being a defect-free linkage with respect to the precision positions is not enough to qualify as a useful mechanism.
-
-Thus, we present a perceptive way of synthesizing defect free linkages for motion and path generation problems.
-%As a guiding direction to advance state of the art, we propose following criteria for an effective mechanism synthesis method,
+%As a guiding direction to advance state of the art, we propose the following criteria for an effective mechanism synthesis method,
 %  \item \textbf{Data Driven}: The method should evolve by learning from its previous experiences, including providing quicker solutions for problems similar to previously solved problems.
 %\end{enumerate}
-To capture the complete prescribed task, we represent it as a continuous parametric curve.
-The objective is to find a linkage, that has a coupler motion or path compatible with the task.
-We developed the compatibility measure in a way that is invariant to similarity transformations.
-Next step is to conduct a search in the space of linkage parameters to find linkages with coupler motions compatible with the prescribed task.
-Although global search methods can be applied for finding solutions, we employ an efficiently clustered database and Powell's local search method to come up with a variety of different solutions.
-The motivation behind using clustered database is rooted in the broader objective of machine design.
-Mechanism synthesis is a part of the conceptual design phase, which is one of the earliest stages of product design cycle of a machine.
-Thus, the synthesis method should be prolific in terms of concept generation to 1) realize the potential of attainable design possibilities, and 2) have the agility to adapt a design to evolving requirements.
-The method only deals with the coupler curves and is indifferent to the linkage type.
-Thus, it is readily scalable to any type of planar linkage.
-In section~\ref{subsec_motiongen}, we present the obtained solutions for the prescribed motion presented in the Fig.~\ref{circuit_defect}.
 
-\subsection{Literature Survey and Overview}
 % Global search methods
-Instead of brute-force search within tolerance regions, some approaches apply separate constraints to take care of the defects and form an optimization problem of Non-Differentiable objective function.
-It can be solved by metaheuristic algorithms like Differential-evolution(DE), Particle Swarm Optimization (PSO), Cuckoo Search (CS).
+Instead of brute-force search within tolerance regions, some approaches apply separate constraints and form an optimization problem of non-differentiable objective function.
+These methods employ metaheuristic algorithms like Differential-evolution (DE), Particle Swarm Optimization (PSO), Cuckoo Search (CS).
 Cabrera et al.\cite{Cabrera2002} used Genetic Algorithm as the tool for optimization in mechanism synthesis.
@@
 Bulatovic\cite{Bulatovic2013} used Cuckoo Search for solving the problem of optimum synthesis of a six-bar double dwell linkage.
-The above methods can produce many defect-free solutions and are scalable to any type of linkages.
+%The above methods can produce many defect-free solutions and are scalable to any type of linkages.
 However, these methods tend to be slow and inefficient as they start from scratch for every instance with no guarantee of converging to an acceptable solution.
@@
 In the case of motion generation, Li et al.\cite{li2016} have developed a Fourier descriptor-based approach for approximate motion generation.
-Bu$\acute{s}$kiewicz et al.\cite{Buskiewicz2009} used curvature of the coupler curve for path synthesis using Genetic Algorithms.
+Bu$\acute{s}$kiewicz et al.\cite{Buskiewicz2009} used the curvature of the coupler curve for path synthesis using Genetic Algorithms.
 Khan et al.\cite{khan2015} presented on approach where an artificial neural network is used for mapping between Fourier coefficients corresponding to a coupler path and corresponding linkage parameters.
@@
 Instead of the global search, an alternative approach is to start from a good initial guess based on an atlas and use local search methods.
-We adopt this approach and combine with our novel formulation to generate a diverse set of concept solutions.
+We adopt this approach and combine with our novel formulation to generate a diverse set of conceptual design solutions.
 McGarva\cite{mcgarva1994} took the earliest approach towards creating a library for coupler trajectories based on the harmonic analysis.
@@
 Chu et al.\cite{chu2010} presented an atlas-based method for synthesizing spatial four-bar linkages for function generation problems, where orientation data is stored in terms of Fourier descriptors.
-
+\begin{figure*}
+\centering
+\includegraphics[width=\textwidth]{figure/overall_approach.eps}
+  \caption{The Machine Learning approach begins by creating an invariant signature for the path and the motion data, which facilitates a compact and hierarchical clustered database and an auto-encoder Neural Network trained to elicit good, defect-free solutions or subjected to local, fast optimization.
+The results are defect-free conceptual design solutions for input problems.}
+\label{overallMethod}
+\end{figure*}
 The above methods generate data based on uniform sampling in the linkage parameter space.
-Given highly nonlinear mapping between linkage parameters and coupler trajectory, this way of sampling leads to a nonuniform sampling of trajectory space, which causes under-representation of possible motions.
+Given the highly nonlinear mapping between linkage parameters and coupler trajectory, this way of sampling leads to a nonuniform sampling of trajectory space, which causes under-representation of possible motions.
 We address this issue by employing log-normal distribution in the linkage parameter space to generate the data samples.
-Then, we perform compact clustering of the data using machine learning techniques.
+Then, we perform a compact clustering of the data using machine learning techniques.
 A hierarchy is created in the database by means of clustering, where the top level comprises of data points called cluster centers, which are representative of the cluster points in lower levels.
@@
 
+In this paper, we represent the given task as a parametric continuous function of poses or path-points.
+The objective is to find a linkage which has a coupler motion or path compatible with the given task.
+We develop a compatibility measure invariant to similarity transformations so that position, scaling, and orientation of the given path or motion do not convolute the optimization.
+Next step is to conduct a search in the space of linkage parameters to find linkages with coupler motions compatible with the prescribed task.
+Although global search methods can be applied for finding solutions, we employ an efficiently clustered database and Powell's local search method to come up with a variety of different solutions.
+The motivation behind using a clustered database is rooted in the broader objectives of machine design.
+Mechanism synthesis is a critical part of the conceptual design phase, which requires synthesis method to be prolific in terms of concept generation to 1) realize the potential of attainable design possibilities, and 2) have the agility to adapt a design to evolving requirements.
+Our method only deals with the coupler curves and is not dependent on the linkage type.
+Thus, it is readily scalable to any type of planar linkage.
+
 The synthesis routine starts by creating a continuous parametric representation of a prescribed path or motion.
-we employ pattern recognition and computational shape analysis to create an invariant signature for the prescribed path and motion.
-A query representing invariant signature \footnote{path or motion signature} of the prescribed path or motion is raised for $k$ nearest neighbors among cluster centers in the database.
+We employ pattern recognition and computational shape analysis to create an invariant signature for the prescribed path and motion.
+A query representing an invariant signature of the prescribed path or motion is raised for $k$ nearest neighbors among cluster centers in the database.
 These $k$ neighbors, if needed, are subjected to fine-tuning by local optimization to obtain a set of defect-free solutions.
@@
 
-The original contributions in the paper are as follows:
-1) a perceptive problem formulation for path and motion generation, that solves the issues associated with precision point approach,
+The original contributions of the paper are in 1) creating a perceptive problem formulation for path and motion generation, which solves the issues associated with the precision point approach,
 %The formulation is based on a measure of dissimilarity between two planar motions or paths, which is invariant to similarity transforms.
-2) we exploit the nonlinear nature of the relationship between the linkage parameters and coupler motions to create a sensitive, wide-ranging, compact, and efficient database with hierarchical clustering, and 3) an algorithm for partial matching of motions and paths which significantly improves the synthesis.
+2) exploiting the nonlinear nature of the relationship between the linkage parameters and coupler motions to create a sensitive, wide-ranging, compact, and efficient database with hierarchical clustering, and 3) developing a novel algorithm for partial matching of motions and paths which significantly improves the synthesis.
 
-%In this paper, we 1) employ pattern recognition and computational shape analysis to create a similarity transform-independent signature for coupler path and motion, 2) exploit the nonlinear nature of relationship between the linkage parameters and coupler motions to create a sensitive, wide-ranging, compact, and efficient database with hierarchical clustering, and 3) enable dimensionality reduction using Auto-encoder Neural Networks.
+%In this paper, we 1) employ pattern recognition and computational shape analysis to create a similarity Transform-independent signature for coupler path and motion, 2) exploit the nonlinear nature of relationship between the linkage parameters and coupler motions to create a sensitive, wide-ranging, compact, and efficient database with hierarchical clustering, and 3) enable dimensionality reduction using Auto-encoder Neural Networks.
 
@@
 Signatures for path and motion are termed as path signature and motion signature, respectively.
-For calculating path signature, we use formulations developed by Cui et.al\cite{cui2009}.
+For calculating the path signature, we use the formulation developed by Cui et.al\cite{cui2009}.
 
-Consider a motion given in parametric form as, $x:x(t), y:y(t), \theta:\theta(t)$.
-Where $\theta(t)$ is the change in orientation along the path with respect to initial orientation.
+Consider a motion given in parametric form as, $x:x(t), y:y(t), \theta:\theta(t)$, where $\theta(t)$ is the change in orientation along the path with respect to initial orientation.
 It should be noted that $\theta(t)$ is a continuous curve with domain ($-\infty$, $\infty$) in contrast to conventional domain i.e. [$-\pi$, $\pi$].
@@
 As an example, the parametric motion could be a B-spline motion as shown in Fig~\ref{bsplineFitting}.
-We compute $\kappa(t)$ and $K(t)$ along the direction of $t$, using Eq.~\req{curvatureEq} and Eq.~\req{kInt} respectively.
-Figure~\ref{curvatureK} shows computed curvature and its unsigned integral of the coupler path shown in Fig.~\ref{bsplineFitting}.
+We compute $\kappa(t)$ and $K(t)$ along the direction of $t$ using Eq.~\req{curvatureEq} and Eq.~\req{kInt}, respectively.
+Figure~\ref{curvatureK} shows computed curvature and its unsigned integral for the coupler path shown in the Fig.~\ref{bsplineFitting}.
 It can be seen that the curvature is small at the start, increases as the curve bends along the path and drops once again as the path straightens out.
-It is obvious that curvature plot will reverse if the direction of parameterizations reverses, while the integral is a monotonically increasing function.
+It is obvious that the curvature plot will reverse if the direction of parameterizations reverses, while the integral is a monotonically increasing function.
 
@@
 \includegraphics[width=240pt]{figure/fig_bspline.eps}
-  \caption{a) The path of the input motion along with direction of parametrization. b) Motion components $x(t), y(t), \theta(t)$ are plotted against parameter t.}
+  \caption{a) The path of the input motion along with direction of parametrization, b) motion components $x(t), y(t), \theta(t)$ are plotted against parameter t.}
 \label{bsplineFitting}
@@
 We note that there is a one-to-one mapping between $t$ and $K$.
-Although it seems natural to use dual-quaternions for representing motion and finding its signature,
-it couples orientation with the path in a way, such that the signatures formed no longer remain invariant to similarity transformation.
+Although it may seem natural to use planar quaternions~\cite{McCarthy90, Bottema} for representing motion and finding its signature, it couples orientation with the path in such a way that the signatures formed no longer remain invariant to similarity transformation.
 
 These signatures are invariant under similarity transformations; for proof see\cite{cui2009}.
-We know that curvature changes inversely to scale of the curve, so when it is integrated along the scaled curve, the scale factor cancels itself out.
+We know that curvature changes inversely to the scale of the curve, so when it is integrated along the scaled curve, the scale factor cancels itself out.
 Reflection operation produces flipped path signature, but motion signature remains invariant.
-Figure~\ref{signature} shows path and motion signature obtained for the motion depicted in Fig.~\ref{bsplineFitting}.
-It is important to note, that the signature depends on the direction of parameter $t$.
-The procedure of signature calculation presented in this section is given in Algorithm ~\ref{alg_signature}.
+Figure~\ref{signature} shows the path and motion signature obtained for the motion depicted in Fig.~\ref{bsplineFitting}.
+It is important to note that the signature depends on the direction of parameter $t$.
+The procedure of signature calculation presented in this section is given in the Algorithm ~\ref{alg_signature}.
 
@@
 In this section, we formulate functions that evaluate the similarity between two trajectories based on their signatures.
-These distance functions can be used as error metric, which can be minimized using optimization methods.
+These distance functions can be used as an error metric, which can be minimized using optimization methods.
 
@@
 
-Let us consider two coupler paths; namely \emph{Part} and \emph{Whole} as shown in~\ref{wholePart}.
+Let us consider two coupler paths; namely \emph{Part} and \emph{Whole} as shown in Fig.~\ref{wholePart}.
 Let $p$ and $W$ be their signatures respectively, where $W$ completely contains $p$ as shown in Fig.~\ref{pathSignature}.
@@
   \item $p$ and $W$ are expressed in terms of arrays and $W$ must contain more points than $p$.
-  \item $p$ is slid with offset index $j$ along $W$.
-  \item For each offset $j$, we compute normalized cross-correlation\cite{lewis1995fast} function given by,
+  \item $p$ is slided with offset index $j$ along $W$.
+  \item For each offset $j$, we compute normalized cross-correlation function~\cite{lewis1995fast}  given by,
 \end{enumerate}
@@
 Here, $p$ acts as a template that tries to find the best match against $W$ while sliding over it along $j$.
-Domain of $Cn(j, p, W)$ is [0, 1], where 1 represents the complete embedment\footnote{\emph{Part} is identical to a portion of \emph{Whole}.} of $p$ inside $W$.
+Domain of $Cn(j, p, W)$ is [0, 1], where 1 represents the complete embedment of $p$ inside $W$, i.e., \emph{Part} is identical to a portion of \emph{Whole}.
 
-The maximum score of the matching $Cn_{max}(p, W)$ represents similarity of the template in $W$, and offset index $j$ at which maximum occurs is the start point for matching.
+The maximum score of the matching $Cn_{max}(p, W)$ represents similarity of the template in $W$, and offset index $j$ at which maximum occurs is the starting point for matching.
 As we know that the signature reverses with reversal of the direction of $t$, we compute the correlation along both directions and select the best matching score, offset index and the matching direction of sampling.
@@
 \includegraphics[width=240pt]{figure/fig_path_signatures.eps}
-  \caption{Path Signatures of part $p$ and whole $W$ from Fig.~\ref{wholePart}.
+  \caption{Path Signatures of part $p$ and whole $W$ from the Fig.~\ref{wholePart}.
 The array index $i$ corresponds to the index location for the array of the $K$.
@@
 where $E(j, p, W)$ is the dissimilarity value when template $p$ is matched to $W$ at $j^{th}$ index. Here $p$ tries to find the best match against $W$ while sliding over it.
-Similar to path signature, motion signature is dependent on the direction of $t$. Thus, we compute the dissimilarity for both directions and choose whichever is the least i.e. $E_{min}(p, W)$.
+Similar to path signature, motion signature is dependent on the direction of $t$. Thus, we compute the dissimilarity for both directions and choose whichever is the least, i.e., $E_{min}(p, W)$.
 Figure~\ref{mcc} depicts dissimilarity function over the sliding domain $j$.
@@
 \includegraphics[width=240pt]{figure/fig_mcc.eps}
-  \caption{Dissimilarity function of two motion signatures along both directions. It can be seen that exact match is found at $j=0$, where the template is fully embedded inside the other motion.}
+  \caption{Dissimilarity function of two motion signatures along both directions. It can be seen that the exact match is found at $j=0$, where the template is fully embedded inside the other motion.}
 \label{mcc}
@@
 \subsection{Objective Function for Synthesis}
-The functions in Eq.~\req{nccEq} and ~\req{mccEq} presented in the sections \ref{sec_ncc}, \ref{sec_mcc} can be used as the error measure for path and motion synthesis of any planar linkage, where the objective is to find a linkage that produces a motion whose part or whole corresponds to the target motion (or path).
-Thus we can formulate the path synthesis problem as,
-
+The functions in Eq.~\req{nccEq} and ~\req{mccEq} presented in the sections \ref{sec_ncc} and \ref{sec_mcc} can be used as the error measure for path and motion synthesis of any planar linkage, where the objective is to find a linkage that produces a motion whose part or whole corresponds to the target motion (or path).
+Thus, we can formulate the path synthesis problem as,
 \begin{equation}\label{objectiveFunPath}
@@
 This optimization problem can be solved using search methods which do not require gradient computation.
-We can employ global optimization methods such as differential evolution at the start, and local optimization methods link Powell's method towards the end for faster convergence\cite{ullah1997}.
+We can employ global optimization methods such as differential evolution at the start, and local optimization approach, such as Powell's method towards the end for faster convergence\cite{ullah1997}.
 
-Considering highly nonlinear nature of the problem, finding a good initial guess proves to be daunting.
-Also, as we mentioned in the motivation, it is important to generate a diverse set of solutions.
-This requires a diverse and large number of good initial guesses.
+Considering the highly nonlinear nature of the problem, finding a good initial guess proves to be daunting.
+In addition, generating a large set of solutions requires a diverse and large number of good initial guesses.
 Thus, we exploit machine learning techniques to create a database for finding many good initial guesses or the solution itself.
-Section~\ref{sec_db_ae} presents the details on the approach.
+Section~\ref{sec_db_ae} presents the details of this approach.
 
@@
 
-To illustrate this via example, we perform sensitivity analysis in the vicinity of a singularity as follows:
+To illustrate this via an example, we perform sensitivity analysis in the vicinity of a singularity as follows:
 A four-bar with link ratios ($l_1:0.55$, $l_2:1$, $l_3:1.5$, $l_4:1$, $l_5:1$) is subjected to gradual change in parameters $l_1$ and $l_3$ by the amount (-0.2, 0.2) in steps of 0.01.
 The link ratios are chosen such that, small changes in some parameters lead to the topological change in the coupler curve.
-Error function between motions of new and initial four-bar are calculated using Eq.~\req{objectiveFunMotion} .
-Figure~\ref{saCouplerCurves} shows coupler motion of some of the four-bars while Fig.~\ref{saMotionSignatures} depicts their motion signatures.
+Error function between motions of new and initial four-bar are calculated using Eq.~\req{objectiveFunMotion}.
+Figure~\ref{saCouplerCurves} shows coupler motion of some of the four-bars, while Fig.~\ref{saMotionSignatures} depicts their motion signatures.
 Please note that these two figures show the effect of changing only one parameter $l_1$.
@@
 Having an invariant representation facilitating partial matching greatly reduces data required to sample all possible types of shapes of coupler motion.
-We have built a database of planar four-bar linkages with revolute joints as an example, but the approach is same for any planar motion generating mechanism.
-We generate this database comprising of $40,000$ linkages while taking following aspects into consideration.
+We have built a database of planar four-bar linkages with revolute joints as an example, but the approach is the same for any planar motion generating mechanism.
+We generate this database comprising of $40,000$ linkages while taking following aspects into consideration:
 \begin{enumerate}
@@
 We use machine learning techniques such as clustering and data-compression using auto-encoder neural networks to come up with good initial guesses for local optimization.
-First, We cluster the database using hierarchical clustering algorithm.
-Then, we find representative data point in each cluster called cluster centers and form their set.
+First, We cluster the database using a hierarchical clustering algorithm.
+Then, we find a representative data point in each cluster called cluster centers and form their set.
 This set of cluster centers represent a diverse group of linkages.
@@
 \subsection{Dimensionality Reduction using Auto-Encoders}
-Each data point in the database consists of discrete signature, which is kept to be of 100 float digits.
+Each data point in the database consists of a discrete signature, which is kept to be of 100 float digits.
 In order to have efficient query operations, we perform hierarchical Clustering; a method that summarizes and creates a hierarchy in the database.
@@
 Figure~\ref{autoEncoder} shows a Neural Network architecture similar to the one we designed for the task.
-Our architecture consists of 100 neurons in input and output layer, while five hidden layers have (80, 50, 10, 50, 80) neurons respectively.
+Our architecture consists of 100 neurons in the input and output layer, while the five hidden layers have (80, 50, 10, 50, 80) neurons respectively.
 Each neuron in the hidden layer is activated by Rectified Linear Unit (\emph{ReLU}) activation function.
@@
 The distance metric used for clustering is the Euclidean distance in the latent space.
-Although the more accurate distance metric is distance function discussed in sec.~\ref{sec_distanceMetric}, it is very expensive to calculate it for the entire database.
+Although the more accurate distance metric is the distance function discussed in the section~\ref{sec_distanceMetric}, it is very expensive to calculate it for the entire database.
 Signatures with ${O}(m)$ points take ${O}(m\log{}m)$ time for each comparison and there are ${O}(N^2)$ number of comparisons to be made for the database of $N$ points.
 
-Now, when the user raises a query, we use the distance function from sec.~\ref{sec_distanceMetric} for finding $k$ nearest neighbors among $1500$ cluster centers.
+Now, when the user raises a query, we use the distance function from the section~\ref{sec_distanceMetric} for finding $k$ nearest neighbors among $1500$ cluster centers.
 If a cluster center is not sufficiently close, we descend into its corresponding cluster to find the closest data point.
@@
 Next step is to compute actual parameters according to position, scale, and orientation of the path.
-It is done by comparing analogous points found by offset index $j$ in Eq.~\ref{nccEq}.
-Figure ~\ref{ex1_solns} shows first eight four-bar mechanisms corresponding to nearest signatures to path signature of input.
+It is done by comparing analogous points found by the offset index $j$ in Eq.~\ref{nccEq}.
+Figure ~\ref{ex1_solns} shows the first eight four-bar mechanisms corresponding to nearest signatures to path signature of input.
 It can be clearly seen that these linkages generate highly accurate paths for the sit to stand activity.
@@
 Now we employ the approach presented in this paper.
-The first step is to calculate motion signature of the task motion using steps mentioned in Algorithm ~\ref{alg_signature}.
+The first step is to calculate the motion signature of the task motion using steps mentioned in Algorithm ~\ref{alg_signature}.
 For that, we follow the steps given in section~\ref{sec_sign} to obtain the motion signature depicted in Fig.~\ref{queryResult}.
@@
 Table~\ref{ex2_knnLinkageData} presents the linkage parameters corresponding to the nearest neighbors along with their distance score from the task.
-Coupler motions of these linkages have a part, which matches with the shape of input motion query.
+Coupler motions of these linkages have a part, which matches with the shape of the input motion query.
 Actual scaling and orientation of the linkage can be found out easily by comparing analogous points, which are given by the offset index $j$ that corresponds to minimum distance$(E_{min})$ in Eq.~\req{mccEq}.
@@
 Although Fig.~\ref{ex2_solns} shows that $5^{th}$ and $7^{th}$ solution may slightly interfere with the ground, it can be rectified by lifting the mechanism slightly up or making small changes in coupler dimensions.
-In light of these results, we can say that this approach produces a large variety of solutions, which otherwise would be very hard to find using precision point approach.
+In light of these results, we can say that this approach produces a large variety of solutions, which otherwise would be very hard to find using the precision point approach.
 
@@
 The approach is highly data-efficient due to similarity invariant representation and partial matching.
-Sensitivity analysis indicates that complexity of the objective function is well behaved at the singular locations.
-The hierarchically clustered database provides efficient query search.
+Sensitivity analysis indicates that the complexity of the objective function is well behaved at the singular locations.
+The hierarchically clustered database provides an efficient query search.
 Finally, the effectiveness of the presented approach is showcased by two case studies.
@@
 Although the partial matching metric is more accurate, it is expensive in terms of computation cost.
-Thus, we use Euclidean metric in the latent space of compressed data for hierarchical clustering of the database.
+Thus, we use the Euclidean metric in the latent space of compressed data for the hierarchical clustering of the database.
 The problem formulation is invariant with respect to translation, orientation, and scaling.
@@
 \begin{acknowledgment}
-This work has been financially supported by National Science Foundation under a research grant to Stony Brook University (A.
+This work has been financially supported by The National Science Foundation under a research grant to Stony Brook University (A.
 Purwar and Q.J.

### 2018-07-31 rebuttal/rebuttal.tex
prof's corrections

@@
 \maketitle
-We are grateful to all of the reviewers, who took out their valuable time to review our paper. This work would be incomplete without the reviewers' inputs.
-The reviewers' comments are given in \emph{italicized}, whereas our answers are in normal text.
+We are grateful to all of the reviewers for their comments and questions and believe that the new version of the paper would resolve all the outstanding issues.
+The reviewers' comments are formatted \emph{emphasized}, whereas our replies are in Roman.
 
@@
 
-Thank you for pointing out an important point.
 We have rewritten the introduction section to clearly explain motivation and overview of the approach.
 The motivation subsection clearly explains significance of the gaps in current practices.
-We summarize the motivation as follows,
-
+In summary, the stakeholders are machine designers who have to generate useful mechanism design concepts during the conceptual design phase.
 The classical mechanism synthesis problem deals with computing type and dimensions of a linkage system for performing specific tasks, which are categorized as the path, motion and function generation.
@@
 \centering
-\includegraphics[width=200pt]{fig_circuit_defect.eps}
+\includegraphics[width=200pt]{fig_circuit_defect-eps-converted-to.pdf}
   \caption{The mechanism synthesis problem for the prescribed motion.
@@
 Figure~\ref{circuit_defect} shows the prescribed motion and its discretized precision positions.
-In the case of motion generation problem, a four-bar can go through at most five precision positions and it is called as classical Burmester~\cite{Burmester86} problem.
+In the case of motion generation problem, a four-bar can go through at most five precision positions~\cite{Burmester86}.
 For this type of problem, only finite solutions exist and in this case, only one solution is obtained as shown in the Fig.~\ref{circuit_defect}.
-Although it can be seen that coupler of the four-bar passes exactly through five precision positions, it can not do it without changing the circuit.
+Although it can be seen that coupler of the four-bar passes exactly through five precision positions, it can not do so without changing the circuit.
 A circuit represents an assembly mode in which the mechanism is put together.
 This phenomenon is called circuit defect in the linkage, which makes the linkage useless for the prescribed task.
-Even if the defect-free solution is found, the coupler motion in-between the precision points may go through undesired position and orientation.
-This happens because the method discards the functional aspect of continuous motion and turns it into a vacuous interpolation problem.
-This tells us that just being a defect-free linkage with respect to the precision positions is not enough to qualify as a useful mechanism.
 
@@
 The importance of diverse concept generation is mentioned in motivation subsection as follows,
-``The synthesis method should be prolific in terms of concept generation to 1) realize the potential of attainable design possibilities, and 2) have the agility to adapt a design to evolving requirements."
+``The synthesis method should be prolific in terms of concept generation to 1) realize the potential of attainable design possibilities, and 2) have the agility to adapt a design to evolving requirements." Our method only deals with the coupler curves and is not dependent on the linkage type.
+Thus, it is readily scalable to any type of planar linkage.
 \\
@@
 
-Thanks, we have added recent citations reporting work in the area of mechanism synthesis and machine learning applications to mechanisms.
+We have added recent citations reporting work in the area of mechanism synthesis and machine learning applications to mechanisms.
 \\
@@
 Thank you for your comments.
-We have added the example shown in the Fig.~\ref{circuit_defect} to the motivation section, which clearly explains the limitations of current practices.
+We have added the example shown in the Fig.~\ref{circuit_defect} to the Introduction section, which clearly explains the limitations of current practices.
 We have used the same example in the example section to clearly juxtapose our results against results of precision point approach.
@@
 
-We have expanded the reason for employing machine learning techniques in the subsection titled `Dimensionality Reduction using Auto-Encoders' as follows,
+We have expanded the reason for employing machine learning techniques in the subsection titled `Dimensionality Reduction using Auto-Encoders' as follows:
 
@@
 When a query is raised in the database, the first step is to search for neighbors in the set of cluster centers.
-This often yields a diverse set of neighbors and is used as a set of initial guesses for local optimization.
-"
-\\
+This often yields a diverse set of neighbors and is used as a set of initial guesses for local optimization."\\
 
@@
 
-Thank you for mentioning that.
-We have fixed it.
-\\
+Thank you for catching that. We have fixed it.\\
 
-  \item \emph{
-The values used in the sensitivity analysis are not justified. How did the authors choose the values?
+  \item \emph{The values used in the sensitivity analysis are not justified. How did the authors choose the values?
 }
 
-Thank you for the comment. We have added following line,
-``The link ratios are chosen such that, small changes in some parameters lead to a topological change in the coupler curve."
-\\
+Due to the complex relationship between parameter space and generated motion, small changes in linkage parameters can produce large and discontinuous structural changes in the generated motions.
+For example, a small change in crank length of a  planar four-bar can open a previously closed coupler path.
+Most of the methods based on Fourier descriptors cannot capture the continuity at such singular locations, which adversely affect the optimization process.
+In contrast to this behavior, the signatures derived in our paper have a smooth transition at these singular locations due to shape similarity between closed and just opened curve or motion.
+The link ratios are chosen such that, small changes in some parameters lead to the topological change in the coupler curve.\\
 
@@
 
-We have employed already proven techniques such as b-spline interpolation, hierarchical clustering, data compression using auto-encoders, Powell's local search.
+We have employed  proven techniques such as B-spline interpolation, hierarchical clustering, data compression using auto-encoders, and Powell's local search.
 We have formulated the signatures of coupler path and motion, based on proven 2D curve matching technique by Cui et al.\cite{cui2009}.
 We have presented the validation of the partial matching algorithms using examples in section 4.
-Finally, we present two case studies, where we obtain the diverse set of useful linkage solutions for path and motion generation problem.
+Finally, we present two case studies, where we obtain a diverse set of useful linkage solutions for path and motion generation problem.
 \\
@@
 \begin{itemize}
-  \item \emph{
+  \item[] \emph{
 $1$. Please provide brief descriptions (possibly with examples) of circuit and branch defects that
@@
 
-  \item \emph{
+  \item[] \emph{
   $2$. In Figure 2b, why is the range of parameter $t$ for $\theta(t)$ is only 0-50, rather than 0-100?
@@
 
-  \item \emph{
+  \item[] \emph{
 $3.$ In Algorithm 2, Line 8, should it be $\theta(tmp)$ instead of $\kappa(tmp)$ ?\\
@@
 
-  \item \emph{
+  \item[] \emph{
 $5.$ In Figure 15, $X$ and $\tilde{X}$ mismatch the input and output vectors shown in the diagram.
@@
 
-Figure 15 shows $X$ as the input and $\tilde{X}$ as the output of auto-encoder network, which matches with the description.
-The query regarding the mismatch is not clear to us.
-Could you please elaborate on the query?
+What was Figure 15 before is now the Figure 16.
+This figure shows $X$ as the input and $\tilde{X}$ as the output of auto-encoder network, which dimensionally match with each other.
+In between layers can have vectors of lower dimensions.
 \\
 
-  \item \emph{
+  \item[] \emph{
 $7.$ In section 5.1, it is argued that Euclidean distance is used as the distance metric in latent space for
@@
 Thanks for the feedback. We have made changes in the text to clarify which metric is used at what point.
-In section 5.1, we added following lines,
+In section 5.1, we have added following:
 
@@
 
-  \item \emph{
+  \item[] \emph{
 $8.$ It is unclear how local optimization is performed after finding the nearest cluster centers. Is the
@@
 
-  \item \emph{
+  \item[] \emph{
 $9.$ Please comment on how this approach can be extended to handle process specific constraints?

### 2018-07-31 idetc2018_journal.tex
prof's corrections

@@
 \begin{abstract}
-Synthesizing defect-free planar four-bar mechanism for the motion generation problem has proven to be a difficult problem.
-These defects can be one or more of branch-, circuit-, and order-defects, which render synthesized mechanisms useless to practitioners.
-Such defects arise from the artificial constraints of formulating the problem as a discrete precision position problem and the corresponding methods which ignore the continuity information in the input.
+Synthesizing  circuit-, branch-, or order- defects-free planar four-bar mechanism for the motion generation problem has proven to be a difficult problem.
+These defects render synthesized mechanisms useless to machine designers.
+Such defects arise from the artificial constraints of formulating the problem as a discrete precision position problem and limitations of the methods which ignore the continuity information in the input.
 In this paper, we bring together diverse fields of pattern recognition, machine learning, artificial neural network, and computational kinematics to present a novel approach that solves this problem both efficiently and effectively.
@@
 The prescribed path is given as a time sequence of positions, whereas the prescribed motion is given as a time sequence of positions and orientations.
-Various approaches have been proposed in the literature with aim of finding acceptable solutions for path and motion generation problem.
-This paper is concerned with calculating the dimensional parameters of defect-free planar four-bar mechanisms while providing machine designers a robust set of defect-free mechanism design solutions during the conceptual design phase, and thereby dramatically broadening the inventions design capabilities.
+Various approaches have been proposed in the literature aiming to find acceptable solutions for path and motion generation problem.
+This paper is concerned with calculating the dimensional parameters of planar four-bar mechanisms while providing machine designers a robust set of defect-free solutions during the conceptual design phase, and thereby dramatically broadening the inventions design capabilities.
 
-A large majority of mechanism synthesis methods are based on the precision point approach.
-This approach is a clever approximation trick to solve the above-mentioned problems, where the task is discretized into precision points.
-These points instead of the actual task, are required to be interpolated or approximated by the designed mechanism.
+A large majority of mechanism synthesis methods are based on the precision position approach.
+This approach is a clever approximation trick to solve the above-mentioned problems, where the task is discretized into precision positions.
+These positions instead of the actual task, are required to be interpolated or approximated by the designed mechanism.
 However, this representation loses critical information about the actual continuous task and can lead to mechanisms with the order, circuit and branch defects; see Chase and Mirth\cite{chasemirth} for a thorough discussion on such defects.
@@
 \end{figure}
-For an example, consider a motion generation problem shown in Fig.~\ref{circuit_defect}, where the objective is to synthesize a four-bar mechanism that can perform the prescribed motion going continuously from pose\footnote{We refer to a pose as an entity that combines position and orientation.} 1 to 5.
-Instead of dealing with an infinite number of poses from initial to final pose, currently this problem is simplified to design a four-bar that goes through all the five poses without any guarantee on the in-between motion.
-Burmester~\cite{Burmester86} showed that a four-bar can go through at most five precision positions and in the best case scenario, there are a limited number of solutions.
+For an example, consider a motion generation problem shown in Fig.~\ref{circuit_defect}, where the objective is to synthesize a four-bar mechanism that can perform the prescribed motion going continuously from position 1 to 5.
+Instead of dealing with an infinite number of positions from initial to final one, currently this problem is simplified to design a four-bar that goes through all the five positions without any guarantee on the in-between motion.
+Burmester~\cite{Burmester86} showed that a four-bar can go through at most five precision positions and even in the best case scenario, there are a limited number of solutions.
 In this case, only one solution is obtained as shown in the Fig.~\ref{circuit_defect}.
@@
 This is an outcome of discarding the functional aspect of continuous motion and turning the problem into an interpolation problem bereft of important details.
-We present our solution to the motion generation problem shown in the Fig.~\ref{circuit_defect} later on in the Case Studies section.
 
@@
 These methods employ metaheuristic algorithms like Differential-evolution (DE), Particle Swarm Optimization (PSO), Cuckoo Search (CS).
-Cabrera et al.\cite{Cabrera2002} used Genetic Algorithm as the tool for optimization in mechanism synthesis.
+Cabrera et al.\cite{Cabrera2002} used Genetic Algorithm for optimization in mechanism synthesis.
 Sardashti et al.\cite{sardashti2013} used PSO towards the defect-free synthesis of four-bar linkage with joint clearance for path generation problem.
@@
 
-The original contributions of the paper are in 1) creating a perceptive problem formulation for path and motion generation, which solves the issues associated with the precision point approach,
+The original contributions of the paper are in 1) creating a perceptive problem formulation for path and motion generation, which solves the issues associated with the precision position approach,
 %The formulation is based on a measure of dissimilarity between two planar motions or paths, which is invariant to similarity transforms.
@@
 This network takes 5-dimensional input in the input layer.
-At each encoder layer, the input is compressed into a vector of lesser dimensions, lowest at the bottleneck layer.}
+At each encoder layer, the input is compressed into a vector of lower dimensions, the lowest at the bottleneck layer.}
 \label{autoEncoder}
@@
 \clearpage
-\listoftables
-\listoffigures
+%\listoftables
+%\listoffigures
 
